%\documentclass[oneside,reqno,12pt]{amsart}





\documentclass[b5paper,draft,openbib,12pt]{memoir} 
%\documentclass[b5paper,openbib,12pt]{memoir} 


 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{bbm}
\usepackage{graphicx}
\usepackage{slashed}
\usepackage{eurosym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathabx}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[mathscr]{eucal}
\usepackage{cancel}


%commutative diagram
\usepackage{amsmath,amscd}
%picture
\usepackage{wrapfig}

\usepackage[unicode=true, pdfusetitle, bookmarks=true,
  bookmarksnumbered=false, bookmarksopen=false, breaklinks=true, 
  pdfborder={0 0 0}, backref=false, colorlinks=true, linkcolor=blue,
  citecolor=blue, urlcolor=blue]{hyperref}
\hypersetup{final}
%needed to have hyperlinks in draft mode


% \numberwithin{equation}{section}
\allowdisplaybreaks[1]

\newtheorem{Def}{Definition}
\newtheorem{axiom}[Def]{Axiom}
\newtheorem{Conj}[Def]{Conjecture}
\newtheorem{Thm}[Def]{Theorem}
\newtheorem{Prp}[Def]{Proposition}
\newtheorem{Lemma}[Def]{Lemma}
\newtheorem{Remark}[Def]{Remark}
\newtheorem{Corollary}[Def]{Corollary}
\newtheorem{Example}[Def]{Example}
\newtheorem{Assumption}[Def]{Assumption}


\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\dotCup}{\mathop{\dot{\bigcup}}}
\DeclareMathOperator{\dotcup}{\mathop{\dot{\cup}}}
\DeclareMathOperator{\ag}{ag}
\DeclareMathOperator{\AG}{AG}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\ev}{ev}
\DeclareMathOperator{\odd}{odd}

\newcommand{\id}{{\mathbbm 1}}
\newcommand{\equaltext}[1]{\ensuremath{\stackrel{\text{#1}}{=}}}
\newcommand{\letext}[1]{\ensuremath{\stackrel{\text{#1}}{\le}}}
\newcommand{\Conv}{\mathop{\scalebox{1.7}{\raisebox{-0.2ex}{\(\ast\)}}}}
\newcommand{\CONV}{\mathop{\scalebox{3.0}{\raisebox{-0.2ex}{\(\ast\)}}}}

% Annotations
\usepackage[colorinlistoftodos,shadow,textsize=scriptsize,textwidth=2.5cm]{todonotes}
\newcommand{\noch}[1]{ \todo[color=blue!20]{Todo: #1} }
\newcommand{\black}{ \color{black} }


\renewcommand\chapterheadstart{
\vspace *{\beforechapskip}
\hrulefill
\vskip 0pt
}

\renewcommand\afterchaptertitle{%
\vskip 0pt
\hrulefill
\par \nobreak  \vskip  \afterchapskip  } 


\setsecnumdepth{all}


%all divisions are numbered in the text body

\parindent 0cm

\begin{document}



\frontmatter
%
%\noindent
%\begin{center}
%    \textsc{ \small{Description of the dissertation project of Markus Nöth,
%        Ludwig-Maximilians University of Munich} \\
%        \smallskip
%\large{ Electron-Positron Pair Creation in External Fields} \\
%\small{Rigorous Control of the Scattering-Matrix Expansion}}
%    \vskip.3cm
%    \small
% supervisor:    D.-A.\ Deckert (LMU)
% \vskip0.4cm
\title{Electron-Positron Pair Creation in External~Fields}
%\subtitle{\footnotesize{Rigorous Control of the Scattering-Matrix Expansion}}
\author{M. Nöth}
\maketitle

 \begin{abstract}
 In this project we investigate the phenomenon of creation of matter-antimatter
pairs of particles, more precisely electron-positron pairs, out of the vacuum
subject to strong external electromagnetic fields. 
Although this phenomenon was predicted already in 1929 and was
observed in many experiments, its rigorous
mathematical description still lies
at the frontier of human understanding of nature. 
Dirac introduced the heuristic description of the vacuum of quantum electrodynamics (QED) as a homogeneous sea of particles. Although the picture of pair creation as lifting a particle out of the Dirac sea, leaving a hole in the sea, is very
explanatory the mathematical formulation of the time evolution of the Dirac sea
faces many mathematical challenges.
A straightforward interaction of sea particles and the radiation field is ill-defined and physically important
quantities such as the total charge current density are badly divergent due to the
infinitely many occupied states in the sea. 
Nevertheless, in the last century physicists and mathematicians
 have developed strong methods called
``perturbative renormalisation theory'' that allow at least to treat the
scattering regime perturbatively. 
Non-perturbative methods have to be developed in order to give an adequate theoretical description of upcoming next-generation experiments allowing a study of the time evolution.
Our endeavour focuses on the so-called \emph{external
field model of QED} in which one neglects the interaction between the sea
particles and only allows an interaction with a prescribed electromagnetic field.
It is the goal of this project to develop the necessary non-perturbative
methods in this model to give a rigorous construction of the scattering
and the time evolution operator. 
\\
\smallskip
\noindent \textbf{Keywords:} Second Quantised Dirac Equation, non-perturbative QED, external-field QED, Scattering Operator
 \end{abstract}


%\vskip.5cm
%\thispagestyle{empty}


\tableofcontents

\newpage



\mainmatter

\chapter{Introduction}

%\show\afterchaptertitle
\noch{Historische Einleitung durch Anfänge relativistischer Quantenphysik, Strahlungskatastrophe (unbounded below). No potentials resultat Lukas}



\chapter[Direct Interaction in Relativistic Quantum Mechanics][Direct Interaction]{Direct Interaction in Relativistic Quantum Mechanics}
As we have seen in the last chapter, having interaction mediated by potentials in a Dirac equation does not seem to be a viable option.
One alternative approach to this problem is to reformulate Diracs equation as an integral equation and to introduce interaction
afterwards. For the benefit of the unfamiliar reader, we will first follow the heuristic derivation of this type of equation
 in \cite{lienert2018direct}, then briefly review the mathematical results that had been established in the past and finally 
 discuss new results for which the author is at least partially to blame.

\section{Overview}
\subsection{Derivation}
\noch{Check whether copying from \cite{lienert2018direct} like this is fine.}
\newcommand{\free}{{0}}
\newcommand{\ret}{{\textup ret}}
\newcommand{\adv}{{\textup adv}}
\newcommand{\sym}{{\textup sym}}
\newcommand{\vx}{{\vec{x}} }
\newcommand{\vy}{{\vec{y}} }

We now follow the heuristic derivation of \cite{lienert2018direct} 
for an equation for a multi-time wave function for two particles  
that expresses direct interaction along light-like configurations. 
This type of equation will then keep us occupied for the rest of this chapter. 
The derivatin is organised as follows: We start out reformulating Diracs equation
for a single particle 
as an integral equation. The reformulated version is then extended to  two particles
in an Poincaré invariant manner. Extending the equation is conveniently done in 
the framework of multi-time wavefunctions.


Diracs equation for one particle subject to a potential \(V\) takes the form
\begin{equation}
	i \partial_t \phi(t,\vx) = \big( H^\free + V(t,\vx) \big) \phi(t,\vx),
	\label{eq:singlepartschroed}
\end{equation}
here \(\phi\) denotes the wavefunction in question, \(\vx\in\mathbb{R}^3, t\in\mathbb{R}\)
and \(H^\free\) is the Hamiltonian associated with a free Dirac particle.
We denote by \(S^\ret\) the retarded Green's function of the non interacting Dirac equation,
that is \(S^\ret\) satisfies
\begin{align}\label{eq:schroedgreensfn}
  \big( i \partial_t - H^\free \big) S^\ret &= \delta^4,\\
  S^\ret(t,\vx) &= 0 \quad \text{for }\, t< t_0.
\end{align}
Then inverting the differential operator \(i\partial_t -H^\free\) in  \eqref{eq:singlepartschroed}
results in 
\begin{equation}
	\phi(t,\vx) = \phi^\free(t,\vx) + \int_{t_0}^\infty \! dt' \int d^3 \vx' \, S^\ret(t-t',\vx-\vx') V(t',\vx') \phi(t',\vx'),
	\label{eq:singlepartint}
\end{equation}
where $\phi^\free$ 
is the solution of the non interacting equation subject to the 
initial condition \(\phi^\free(t_0)=\phi_0\). 
Equations \eqref{eq:singlepartint} and \eqref{eq:singlepartschroed} subject to 
\(\phi(t_0)=\phi_0\) yield equivalent 
descriptions, as can be verified directly: An action of \(i\partial_t -H^\free\) on 
\eqref{eq:singlepartint} shows that a solution thereof also solves \eqref{eq:singlepartschroed}.
Also the initial condition is fulfilled, as the integral term vanishes for \(t=t_0\).
Conversely equation \eqref{eq:singlepartschroed} can be considered a free Dirac equation 
involving an inhomogeneous term of the form \(V \phi\), whose solutions are known to be
of the form \eqref{eq:singlepartint}.
Executing the analogous procedure for the two particle Dirac equation

\begin{equation}
	i \partial_t \phi(t,\vx_1,\vx_2) = \big(H_1^\free + H_2^\free + V(t,\vx_1,\vx_2)\big) \phi(t,\vx_1,\vx_2),
	\label{eq:twopartschroed}
\end{equation}
subject to the initial condition  \(\phi(t_0)=\phi_0\), 
results in the integral equation
\begin{align}
	\phi(t,\vx_1,\vx_2) = \phi^\free&(t,\vx_1,\vx_2) + \int_{t_0}^\infty \! dt' \! \int d^3 \vx_1'\,  d^3 \vx_2'\, S_1^\ret(t-t',\vx_1-\vx_1') \nonumber\\
	\times&S_2^\ret(t-t',\vx_2-\vx_2') V(t',\vx_1',\vx_2') \phi(t',\vx_1',\vx_2'),
	\label{eq:twopartschroedint}
\end{align}
where 
$\phi^\free(t)$ is a solution to the free Dirac equation for two particles subject
to \(\phi^\free (t_0)=\phi_0\) and \(S_k^\ret\) is the retarded Green's function
of the free Dirac equation of particle number \(k\). Here it is crucial to notice that
The Green's function of the free two particle Dirac equation factorises into a product 
of two Green's functions of the Dirac equation for one particle.

Since equation \eqref{eq:twopartschroedint} contains only one temporal variable, but six spatial ones,
it is not obvious how it might be considered a relativistic equation at all. So we will 
the step from one to two particles, but before we do so let us first rewrite equation 
\eqref{eq:singlepartint} in a more suggestive way:
\begin{equation}
	\psi(x) = \psi^\free(x) + \int d^4 x' \, S^\ret(x-x') V(x') \psi(x'),
	\label{eq:singlepartintspacetime}
\end{equation}
where non bold letters denote elements of Minkowski spacetime and we replaced \(\phi\)
by \(\psi\) in order to make a visible switch to relativistic notation. 
Furthermore we replaced the lower bound in the temporal integral domain by \(-\infty\)
in order to render the total domain of integral Poincaré invariant.

Equation \eqref{eq:singlepartintspacetime} immediately inspres us to write down the
following generalisation
\begin{align}\label{eq:twopartintgeneral}
  \psi(x_1,x_2) = &\psi^\free(x_1,x_2) \\\nonumber
  &+ \int d^4 x_1'\, d^4 x_2' \, S^\ret_1(x_1-x_1') S^\ret_2(x_2-x_2') K(x_1',x_2') \psi(x_1',x_2').
\end{align}
we integrate over all of \(\mathbb{R}^8\) and \(\psi^\free\) a solution of the free 
Dirac equation both in \(x_1\) and \(x_2\) and their respective spinor indices:
\begin{align}
  D_1  \psi^\free(x_1,x_2) = 0,\\
  D_2  \psi^\free(x_1,x_2) = 0,
	\label{eq:freemultitime}
\end{align}
For the object \(K\), called the ''interaction kernel``, the optimal choice is not yet known.
However, for \eqref{eq:twopartintgeneral} to be Poincaré invariant, it should be invariant
itself. A simple way to ensure this is to let it only depend directly 
the squared Minkowski distance \((x_1-x_2)^2\). A choice that shows some resemblence of 
Wheeler-Feynman electrodynamics is
\begin{equation}
	K(x_1,x_2) = i\, \frac{e_1e_2}{4\pi} \gamma_1^\mu \gamma_{2,\mu} \; \delta((x_1-x_2)^2).
	\label{eq:twopartkernel}
\end{equation}
In an equation incorporating \eqref{eq:twopartkernel} the interaction between the particles 
happens along light-like distances. The constant in front of \eqref{eq:twopartkernel}
is fixed by the non-relativistic limit, recovering an equation very much like the Breit equation,
see \cite[section 3.6]{lienertfirst}.

Summarising this results in the equation
\begin{align}\label{eq:twopartint}
  \psi&(x_1,x_2) = \psi^\free(x_1,x_2)+i\, \frac{e_1e_2}{4\pi} \int d^4 x_1' \, d^4 x_2' \\\nonumber
  & \times S^\ret_1(x_1-x_1') S^\ret_2(x_2-x_2') \, \gamma_1^\mu \gamma_{2,\mu}\delta((x_1'-x_2')^2) \psi(x_1',x_2').
\end{align}


Despite the fact that the motivation for \eqref{eq:twopartint} holds for Dirac particles, 
it is also conceivable to replace \(\psi\), \(S^\ret\) and all the constant factor by 
quantities related to the Klein Gordon equation and arrive at 

\begin{align}\label{eq:KGtwopartint}
  \psi&(x_1,x_2) = \psi^\free(x_1,x_2)+\lambda \int d^4 x_1' \, d^4 x_2' \\\nonumber
  & \times G^\ret_1(x_1-x_1') G^\ret_2(x_2-x_2') \,\delta((x_1'-x_2')^2) \psi(x_1',x_2'),
\end{align}
where \(\psi\) and \(\psi\free\) are no longer spinor valued, \(\psi^\free\) is a
solution to the free Klein Gordone equation in both \(x_1\) and \(x_2\),
\begin{align}
  (\Box_{x_1} + m_1^2)\psi=0\\
  (\Box_{x_2} + m_2^2)\psi=0
\end{align}
and \(G^\ret\) is the retarded Green's function of the Klein Gordon equation.

In fact,  most of the rigorous results about equations of a similar 
type as the ones motivated in this chapter are about the Klein 
Gordon version \eqref{eq:KGtwopartint}.


\subsection{Previous Results on Directly Interacting Particles}
In this chapter we summarise the most important existence results on equations of the type of 
\eqref{eq:twopartintgeneral}. Because this line of work is still fairely young,
it can still readily be summarised. The results are taken from \cite{lienertfirst} and 
\cite{lienertcurved}. The theorems are about slightly different versions of equations
of the type of \eqref{eq:KGtwopartint}. I tried to contain the necessary notation to within each
of the theorems. I only cited the theorems that are about a four dimensional spacetime, 
there are also results about three and two dimensional spacetime, the interested reader 
is refered to \cite{lienert2018direct,lienertcurved}. The versions of 
equation \eqref{eq:KGtwopartint} in the theorems are considerably modified:

\begin{itemize}
\item The spacetime of equation \eqref{eq:KGtwopartint} is \(\mathbb{R}^4\), Minkowski spacetime, whilst 
the spacetime of all the theorems in flat spacetime is 
\(\mathbb{R}^+\times\mathbb{R}^3=:\frac{1}{2}\mathbb{M}\). 
That is, there is a beginning in time. This modification has technical reasons. However, as current 
cosmological models of our universe do have a beginning in time this modification does not necessarily
mean that the equation can no longer describe certain aspects of physics. As these cosmological models 
have nonzero curature the authors of \cite{lienertcurved} 
have shown existence of solutions of versions of equation \eqref{eq:KGtwopartint}
on Friedmann-Lemaître-Robertson-Walker (FLRW) spacetime. In section \ref{sec:direct dirac} and 
\ref{sec:KG lightcones} \noch{really also in the second paper?} we will also employ this 
simplification and show existence on FLRW spacetime. This is not an attempt to treat 
general curved spacetimes, it is done as an act of consistency. We introduce a beginning in time 
and try to justify this by cosmological arguments and hence we treat a spacetime commonly used
in cosmology.
\item The interaction kernel \(K\) which we motivated to be proportional to \(\delta((x_1-x_2)^2)\)
is replaced by various less singular objects. This modification is purely technical and we do not 
justify it. The previous results approach the singular \(K\) introduced in the last section to different
degrees. In section \ref{sec:direct dirac} where we treat Dirac particles 
we will use a rather soft interaction kernel. The new result about Klein Gordon particles in 
section \ref{sec:KG lightcones} employs the fully singular \(\delta((x_1-x_2)^2)\) kernel. 
\end{itemize}

%\begin{Thm}[Thm 3.1 of \cite{lienertfirst}]
%Let \(T>0\), \(M,N\in\mathbb{N}\), consider 
%the Banach space \(\mathcal{B}=L^\infty ([0,T]^N,L^2(\mathbb{R}^M))\).
%Let \(\mathcal{L}:[0,T]^{2N}\rightarrow L^2(\mathbb{R}^{2M})\) such that 
%\begin{equation*}
%\sup_{t,t'\in[0,T]^{N}}\|\mathcal{L}(t,t')\|^2<\infty,
%\end{equation*}
%then for any \(f_0\in\mathcal{B}\) the equation
%\begin{equation*}
%f(t,x)=f_0(t,x)+ \int_0^t dt' \int dx' L(t,t',x,x') f(t',x')
%\end{equation*}
%has a unique solution \(f\in\mathcal{B}\).
%\end{Thm}

%\begin{Thm}[Thm 3.2 \((d=1)\) of \cite{lienertfirst}]
%Let \(T>0, \lambda\in\mathbb{C}, m_1,m_2\ge 0\), every
%\begin{equation*}
%\psi^\free \in \mathcal{B}_1=L^\infty ([0,T]^2,L^2(\mathbb{R}^2)),
%\end{equation*}
%and every essentially bounded \(K:\mathbb{R}^4\rightarrow \mathbb{C}\), the integral equation 
%\begin{align*}
%\psi(t_1,z_1,t_2,z_2)=\psi^\free(t_1,z_1,t_2,z_2)+\frac{\lambda}{4}\int_0^{t_1}dt_1'\int_0^{t_2}dt_2'\int dz_1'dz_2'\\
% \times H(t_1-t_1'-|z_1-z_1'|) J_0(m_1\sqrt{(t_1-t_1')^2-|z_1-z_1'|^2})\\
% \times H(t_2-t_2'-|z_2-z_2'|) J_0(m_2\sqrt{(t_2-t_2')^2-|z_2-z_2'|^2})\\
%  \times K(t_1',z_1',t_2',z_2')\psi(t_1',z_1',t_2',z_2')
%\end{align*}
%has a unique solution \(\psi \in \mathcal{B}_1\).
%\end{Thm}

%\begin{Thm}[Thm 3.3 \((d=2)\) of \cite{lienertfirst}]
%Let \(T>0, \lambda\in\mathbb{C}, m_1,m_2\ge 0\), for every essentially bounded \(K:\mathbb{R}^6\rightarrow\mathbb{C}\)
%and every \(\psi^\free \in \mathcal{B}_2=L^\infty([0,T]^2,L^2(\mathbb{R}^4))\) the equation
%\begin{align*}
%&\psi(t_1,\vx_1,t_2,\vx_2)=\psi^\free(t_1,\vx_1,t_2,\vx_2)+\frac{\lambda}{(2\pi)^2}\int_0^{t_1}dt_1'\int_0^{t_2}dt_2'\\
%&\times\int d^2\vx_1'd^2\vx_2' H(t_1-t_1'-|\vx_1-\vx_1'|)\frac{\cos(m_1\sqrt{(t_1-t_1')^2-|\vx_1-\vx_1'|^2})}{\sqrt{(t_1-t_1')^2-|\vx_1-\vx_1'|^2}}\\
%&\quad \times H(t_2-t_2'-|\vx_2-\vx_2'|)\frac{\cos(m_2\sqrt{(t_2-t_2')^2-|\vx_2-\vx_2'|^2})}{\sqrt{(t_2-t_2')^2-|\vx_2-\vx_2'|^2}} \\
%&\quad \quad\quad \quad \times K(t_1',\vx_1',t_2',\vx_2')\psi(t_1',\vx_1',t_2',\vx_2')
%\end{align*}
%has a unique solution \(\psi \in \mathcal{B}_2\).
%\end{Thm}

\begin{Thm}[Thm 3.4 \((d=3)\) of \cite{lienertfirst}]
Let \(T>0, \lambda\in\mathbb{C}\), for every bounded \(K:\mathbb{R}^8\rightarrow\mathbb{C}\) and every
\(\psi^\free \in\mathcal{B}_3=L^\infty([0,T]^2,L^2(\mathbb{R}^6))\)
the equation 

\begin{align*}
&\psi(t_1,\vx_1,t_2,\vx_2)=\psi^\free(t_1,\vx_1,t_2,\vx_2)+\frac{\lambda}{(4\pi)^2}\int d\vx_1' d\vx_2'\\
&\times \frac{H(t_1-|\vx_1-\vx_1'|)}{|\vx_1-\vx_1'|}\frac{H(t_2-|\vx_2-\vx_2'|)}{|\vx_2-\vx_2'|}K(t_1-|\vx_1-\vx_1'|,\vx_1',t_2-|\vx_2-\vx_2'|,\vx_2')\\
&\quad\quad\quad\quad \times\psi(t_1-|\vx_1-\vx_1'|,\vx_1',t_2-|\vx_2-\vx_2'|,\vx_2')
\end{align*}
has a unique solution \(\psi\in\mathcal{B}_3\).
\end{Thm}

\begin{Thm}[Thm 3.5 of \cite{lienertfirst}]
  Let \(T>0, \lambda\in\mathbb{C}\), for every bounded \(f:\mathbb{R}^8\rightarrow \mathbb{C}\) and every \(\psi^\free \in \mathcal{B}_3\) the equation
\begin{align*}
&\psi(t_1,\vx_1,t_2,\vx_2)=\psi^\free(t_1,\vx_1,t_2,\vx_2) + \frac{\lambda}{(4\pi)^2}\int d^3\vx_1'd^3\vx_2'\\
& \times \frac{H(t_1-|\vx_1-\vx_1'|)}{|\vx_1-\vx_1'|} \frac{H(t_2-|\vx_2-\vx_2'|)}{|\vx_2-\vx_2'|} \frac{f(t_1-|\vx_1-\vx_1'|,\vx_1',t_2-|\vx_2-\vx_2'|,\vx_2')}{|\vx_1'-\vx_1|}\\
&\quad \quad \quad \times \psi(t_1-|\vx_1-\vx_1'|,\vx_1',t_2-|\vx_2-\vx_2'|,\vx_2'),
\end{align*}
has a unique solution \(\psi\in\mathcal{B}_3\).
\end{Thm}


The next results will be about FLRW spacetime. We have to introduce some notation before we can 
present them. Here we cite \cite[sec 3.2]{selfDirac}. 
\noch{entscheide ob man hier vielleicht Matt+mein KG paper zitieren kann, dann muss man nicht umformulieren.}




\section{Directly Interacting Dirac Particles}\label{sec:direct dirac}

\section{KG-Particles Interacting Directly Along Lightcones}\label{sec:KG lightcones}


\chapter[Quantum Field Theoretic Approach to Interactions][Interaction in QFT]{Quantum Field Theoretic Approach to Interactions} \label{sec:QFT}

\noch{quick introduction into Hadamard stuff and Dirk \& Franz stuff, erwähne Ruijsnaars stuff}

\todo{rewrite!}
In order to be able to state our main conjecture \eqref{main_result} precisely
I will need to introduce the one-particle dynamics for electrons and their
scattering operator, see section \ref{sec:one-particle} below, and then move on
to the second quantised dynamics and its corresponding scattering operator  in
section \ref{sec:second quant}. Second quantization is the canonical
method of turning a one-particle theory into one of an arbitrary and
possibly changing number of particles. The informal
series expansion of the one-particle scattering operator \(U\) is derived 
from Dirac's equation of motion for the electron. In section
 \ref{sec:well-def} the convergence of this
expansion is shown. The informal expansion of the second quantized
scattering operator $S$ is then derived from $U$ by second quantisation in
section \ref{sec:second quant}. At this point I have gathered enough tools to present the main conjecture \ref{main_result} in section \ref{sec:main result}. 
After the main conjecture is known, I present several of my own results in sections \ref{sec: odd orders}, \ref{sec: first order} and \ref{sec: second order} about the first order, the second order and all other odd orders. 
These results give an intuition on how to control the convergence of the informal expansion of the scattering operator \(S\).

\section{The Relationship Between Hadamard States, the Fermionic Projector, and Admissible Polarisation Classes}
\todo{insert QFT communications paper, once ready}
\todo{necessary: more thorough introduction to Franz and Dirk stuff for handling the geometry part}


\section{Analyticity of the One Particle Scattering Operator}

In this section we analyse the construction of the one particle 
scattering operator \(S_A\)
carried out in \cite{ivp0} and answer the question whether
operators like
\begin{equation}
P^+ \partial_B S_{A}^* S_{A+B}P^-
\end{equation}
are Hilbert-Schmidt operators. This will turn out to be important 
for the geometric construction carried out in 
chapter \ref{chapter geometery}. 

Since this section is heavily inspired from \cite{ivp0}, we need
to introduce some notation from this paper. 
\begin{Def}
We define the set \(\mathcal{V}\) of four potentials
\begin{equation}
\mathcal{V}:= C_c^\infty(\mathbb{R}^4,\mathbb{R}^4).
\end{equation}
Let \(A\in\mathcal{V}\), we define the the integral operator
\(Q^A:\mathcal{H}\righttoleftarrow\) by giving its integral kernel, which 
is also denoted by \(Q^A\):
\begin{align}
\mathbb{R}^3\times\mathbb{R}^3\ni (p,q)\mapsto Q^A(p,q)
:=\frac{Z^A_{+-}(p,q)-Z^A_{-+}(p,q)}{i(E(p)+E(q))}\\
\text{with }Z^A_{\pm\mp}(p,q):=P_\pm (p)Z^A(p-q)P_\mp (q),\\
Z^A=-i e\gamma^0 \gamma^\alpha \hat{A}_\alpha,\\
\hat{A}_\mu(t):\mathcal{H} \righttoleftarrow, \hat{A}_\mu(t)\psi:= \hat{A}_\mu(t) \ast \psi,\\
\hat{A}_\mu := \frac{1}{(2\pi)^{3/2}}\int_{\mathbb{R}^3} A_\mu (x)e^{-i p x} d^3x,\\ 
\text{and } E(p):=\sqrt{m^2+|p|^2}.
\end{align}

We introduce the standard polarisation for the free Dirac equation\todo{think of some more intuitive notation for the projector.}
\begin{align}
P^-:=1_{\mathrm{spec}(H^0)<0}, \quad P^+=1-P^-.
\end{align}
\end{Def}



\begin{Lemma}
For general \(A,F\in\mathcal{V}\) we have the well known equations for
the one-particle time evolution operators

\begin{align}
U^A(t_1,t_0)=U^0(t_1,t_0) + \int_{t_0}^{t_1}dt U^0(t_1,t) Z^A(t) U^{A}(t,t_0)\\
U^{A+F}(t_1,t_0)=U^A(t_1,t_0) + \int_{t_0}^{t_1}dt U^A(t_1,t) Z^F(t) U^{A+F}(t,t_0).
\end{align}
\end{Lemma}
\begin{proof}
\dots
\end{proof}

\begin{Thm}[Analyticity of S]\todo{think about 
  generalisation to higher derivatives}
Let \(n\in\mathbb{N}\),  \(A,H_{k}\in\mathcal{V}\) for 
\(k\le n\), pick \(t_1\) 
after \(\supp A\cup \bigcup_{k\le n}\supp H_k\) and \(t_0\)
before \(\supp A\cup\bigcup_{k\le n}\supp H_k\) then 
\begin{align}\label{derivative U}
\partial_{H_1} U^{A+H_1}(t_1,t_0)=\int_{t_0}^{t_1}dt~ U^A(t_1,t)Z^{H_1}(t) U^{A}(t,t_0)
\end{align}
holds with respect to the topology induced by the
norm
\begin{equation}
T:\mathcal{H}\righttoleftarrow \|T\|_{\mathrm{op}+I_2}=\|T\|+\|P^+ T P^-\|_{I_2}+\|P^- T P^+\|_{I_2},
\end{equation}
where \(\|\cdot\|\) is the operator norm and \(\|\cdot\|_{I_2}\) is the 
Hilbert-Schmidt norm.
Additionally the derivatives 
\begin{equation}
\partial_{H_1}\dots \partial_{H_k}U^{A+\sum_{b=1}^k F_b}(t_1,t_0)
\end{equation}
all exist with respect to the topology just mentioned.
Furthermore let \(T_1\in I_2(\mathcal{F})\) then the following formulas hold:\todo{how well does cyclicity of the trace hold for operators?}
\begin{align}\notag
\partial_{H_1} \tr(T_1 P^+ U^{A}(t_0,t_1)U^{A+H_1}(t_1,t_0)P^-)\\\label{pull derivative into trace}
= \tr(T_1 P^+ U^{A}(t_0,t_1)\partial_{H_1} U^{A+H_1}(t_1,t_0)P^- )\\\notag\vspace{2cm}
\partial_{H_1} \tr(T_1 P^+ U^{A}(t_0,t_1)U^{A+H_1}(t_1,t_0)P^+)\\
= \tr(T_1 P^- U^{A}(t_0,t_1)\partial_{H_1} U^{A+H_1}(t_1,t_0)P^+ ).
\end{align}
\end{Thm}
\begin{proof}
Following \cite{ivp0} we will throughout this proof make use of the 
following shorthand notation. For operator valued maps 
\(T_1,T_2:\mathbb{R}^2\to (\mathcal{H}\righttoleftarrow) \) we define 
for \(t_1,t_0\in\mathbb{R}\)
\begin{equation}
T_1T_2 = \int_{t_0}^{t_1}dt~ T_1(t_1,t)T_2(t,t_0),
\end{equation}
as a map of the same type as \(T_1\) and \(T_2\)
whenever this is well defined. Furthermore for operator valued functions
\(C_1,C_2:\mathbb{R}\to (\mathcal{H}\righttoleftarrow)\) we define
\begin{align}
T_1C_1=T_1(t_1,t_0)C_1(t_0)\\
C_1 T_1=C(t_1)T_1(t_1,t_0)\\
C_1C_2=C_1(t_1),
\end{align}
as maps of the same type as \(T_1, T_1\) and \(C_1\) 
respectively.
Pick\(n\in\mathbb{N}\), \(A,H_b\in\mathcal{V}\) for \(b\le k\) 
and \(t_1,t_0\) as in the theorem. 
Furhtermore we introduce the integral operator 
\({Q'}^A:\mathcal{H}\righttoleftarrow\) by it's kernel
\begin{equation}
\mathbb{R}\times\mathbb{R}^3\times\mathbb{R}^3
\ni(t,p,q)\mapsto {Q'}^A(t,p,q)=\partial_t Q^A(t,p,q),
\end{equation}
where the time dependence is due to the time dependence of the 
four-potential \(A\).
The following notion of even and odd part of 
an arbitrary bounded linear operator 
\(T:\mathcal{F}\righttoleftarrow\) on 
Fock space will come in handy:
\begin{equation}
T_{\mathrm{odd}}:=P^+TP^- + P^-TP^+\\
T_{\mathrm{ev}}:=P^+TP^+ + P^-TP^-.
\end{equation}

We abbreviate
\begin{equation}
H:=\sum_{b=1}^k H_b, \quad B:=A+H
\end{equation}
Because of the choice of \(t_1,t_0\) we have
\begin{equation}\label{def R}
R^{A+H}(t_1,t_0):=[(1-Q^{A+H})U^{A+H}(1+Q^{A+H})](t_1,t_0)=U^{A+H}(t_1,t_0),
\end{equation}
because \(A+H=0\) both at \(t_1\) and \(t_0\).

So it suffices to study the family of operators \(R\). 
From the analysis carried out in \cite{ivp0} we know that 
\(R^B\) for \(B\in\mathcal{V}\) is the limit in the sense of the 
operator norm of the sequence
\begin{align}
R^B_{0}:=0, \quad R^B_{n+1}:=U^0 F^B R^B_{n}+ U^0 + G^B,
\end{align}
where \(F\) and \(G\) are given By

\begin{align}
F^B:= (-{Q'}^B+Z^B_{\mathrm{ev}}-Q^BZ^B)(1+Q^B),\\
G^B:=- U^0(1-Q^BQ^B) + U^0(-{Q'}^B\\
+Z_{\mathrm{ev}}-Q^B Z^B)Q^B Q^B U^B (1+Q^B).
\end{align}

\begin{Lemma}
We are going to prove that for \(n\in\mathbb{N}\) and 
\begin{align}
  R^{A}_n&\xrightarrow[n\rightarrow \infty]{\|\cdot\|_{\mathrm{op}+I_2}}R^A\\
  \partial_F R^{A+F}_n&\xrightarrow[n\rightarrow \infty]{\|\cdot\|_{\mathrm{op}+I_2}} \partial_FR^{A+F}
\end{align}
holds.
\end{Lemma}

\begin{proof}
First we introduce the auxiliary norms for operators \(T\) 
and \(W\) depending on one and two 
scalar variables respectively.

\begin{align}
  \|T \|_{\mathrm{op}+I_2,\gamma}
  &:=\sup_{t\in[t_1,t_0]}e^{-\gamma (t-t_0)} \left(\|T(t)\|
  +\| T_{\odd}(t)\|_{I_2}\right)\\
  \|T \|_{\mathrm{op},\gamma}&:=\sup_{t\in[t_1,t_0]}e^{-\gamma (t-t_0)} \|T(t)\|\\
  \|W \|_{\mathrm{op},\infty}&:=\sup_{t,t'\in[t_1,t_0]} \|W(t,t')\|\\
  \|T \|_{I_2 ,\gamma}&:=\sup_{t\in[t_1,t_0]}e^{-\gamma (t-t_0)} \| T(t)\|_{I_2},\\
  \|W \|_{I_2 ,\infty}&:=\sup_{t,t'\in[t_1,t_0]} \| W(t,t')\|_{I_2},
\end{align}
for some \(\gamma\ge 0 \).

From the analysis of \cite{ivp0} follows that the 
recursive equation \cite[(3.42)]{ivp0}

\begin{align}
R^B_{n}=U^0F^B_{\ev}R^B_{n-1}+U^0F^B_{\odd} U^0F^B R^B_{n-2}\\
+U^0 F^B_{\odd} +U^0F^B_{\odd} U^0 + U^0 +G^B
\end{align}
is fulfilled by the same sequence of operators for \(n\ge 2\).
Hence we have for \(n\ge 2\):
\begin{align}\notag
  R^B-R^B_{n}=U^0F^B_{\ev}(R^B-R^B_{n-1})\\
  +U^0F^B_{\odd} U^0F^B (R^B-R^B_{n-2}).
\end{align}
Abbreviating \(U^0F^B_{\ev}=:a,U^0F^B_{\odd}U^0 F^B:=b\), we obtain
\begin{align}\notag
  R^B-R^B_{n}=a(R^B-R^B_{n-1})\\\label{R recurisve}
  +b (R^B-R^B_{n-2}).
\end{align}
Furthermore, we introduce the notation for \(k\in\mathbb{N}\)
\begin{align}
\forall k \in \mathbb{N} [k]&:=\{l\in\mathbb{R}\mid l\le k\}\\
\forall u\subseteq [k]:\partial_{u}&:=\prod_{k\in u}\partial_{H_k},\\
R^B-R^B_n&:=\Delta^n,
\end{align}
where the product of derivatives is to be understood as the 
mixed derivative with respect to all the factors.
Now we estimate for some set \(u\subset [k]\)

\begin{align}
\|\partial_u \Delta^n_{\odd} \|_{I_2}
\le\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)}
\left\| \sum_{w\subseteq u} (\partial_{u\backslash w}a ~
\partial_w \Delta^{n-1}_{\odd})(t,t_0)\right\|_{I_2}\\
+\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)}
\left\|P^+ \sum_{w\subseteq u} (\partial_{u\backslash w}b ~
\partial_w \Delta^{n-2})(t,t_0) P^-\right\|_{I_2}\\
+\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)}
\left\|P^- \sum_{w\subseteq u} (\partial_{u\backslash w}b ~
\partial_w \Delta^{n-2})(t,t_0) P^+\right\|_{I_2}\\
\le 
\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)} \sum_{w\subseteq u} 
\| \partial_{u\backslash w}(a ~
\partial_w \Delta^{n-1}_{\odd})(t,t_0)\|_{I_2}\\
+2\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)} \sum_{w\subseteq u} 
\|  (\partial_{u\backslash w}b ~
\partial_w \Delta^{n-2})(t,t_0) \|_{I_2}\\
\le
\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)} \sum_{w\subseteq u} 
\int_{t_0}^{t}dt' 
\| \partial_{u\backslash w}a(t,t') ~
\partial_w \Delta^{n-1}_{\odd}(t',t_0)\|_{I_2}\\
+2 \sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)}\sum_{w\subseteq u} 
t_{t_0}^{t}dt'  
\|  \partial_{u\backslash w}b(t,t') ~
\partial_w \Delta^{n-2}(t',t_0) \|_{I_2}\\
\le
\sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)} \sum_{w\subseteq u} 
\int_{t_0}^{t}dt' 
\| \partial_{u\backslash w}a\|_{\mathrm{op},\infty}
\|\partial_w \Delta^{n-1}_{\odd}(t',t_0)\|_{I_2}\\
+2 \sup_{t\in[t_0,t_1]} e^{-\gamma(t-t_0)}\sum_{w\subseteq u} 
\int_{t_0}^{t}dt'  
\|  \partial_{u\backslash w}b(t,t')\|_{I_2}
\|\partial_w \Delta^{n-2}(t',t_0) \|_{\mathrm{op}}\\
\le
\sup_{t\in[t_0,t_1]} e^{-\gamma t} \sum_{w\subseteq u} 
\int_{t_0}^{t}dt' e^{\gamma t'}
\| \partial_{u\backslash w}a\|_{\mathrm{op},\infty}
\|\partial_w \Delta^{n-1}_{\odd}(\cdot,t_0)\|_{I_2,\gamma}\\
+2 \sup_{t\in[t_0,t_1]} e^{-\gamma t}\sum_{w\subseteq u} 
\int_{t_0}^{t}dt'  e^{\gamma t'}
\|  \partial_{u\backslash w}b\|_{I_2,\infty}
\|\partial_w \Delta^{n-2}(t',t_0) \|_{\mathrm{op},\gamma}\\
\le
\frac{1}{\gamma} \sum_{w\subseteq u} 
\| \partial_{u\backslash w}a\|_{\mathrm{op},\infty}
\|\partial_w \Delta^{n-1}_{\odd}(\cdot,t_0)\|_{I_2,\gamma}\\
+\frac{2}{\gamma} \sup_{t\in[t_0,t_1]}\sum_{w\subseteq u} 
\|  \partial_{u\backslash w}b\|_{I_2,\infty}
\|\partial_w \Delta^{n-2}(t',t_0) \|_{\mathrm{op},\gamma}\\
\end{align}




, this 
can be brought into the vectorised form:
\begin{align}\label{T iterated}
\binom{R^B-R^B_{n}}{R^B-R^B_{n-1}}
=\begin{pmatrix} a &b \\ 1 & 0 \end{pmatrix}
  \binom{R^B-R^B_{n-1}}{R^B-R^B_{n-2}},
\end{align}
which by induction yields
\begin{align}
  \binom{R^B-R^B_{n}}{R^B-R^B_{n-1}}
  =\begin{pmatrix}a &b \\ 1 & 0 \end{pmatrix}^{n-1}
    \binom{R^B-R^B_{1}}{R^B}.
\end{align}
Taking the derivative of \eqref{R recurisve} we find
\begin{align}\notag
  \partial_H (R^{A+F}-R^{A+H}_{n})
  =U^0F^A_{\ev}\partial_H(R^{A+H}-R^{A+H}_{n-1})\\\notag
  +U^0F^A_{\odd} U^0F^A \partial_H(R^{A+H}-R^{A+H}_{n-2})
  +\partial_H U^0F^{A+H}_{\ev}(R^{A}-R^{A}_{n-1})\\\label{R dot recurisve}
  +\partial_H U^0F^{A+H}_{\odd} U^0F^{A+H} (R^{A}-R^{A}_{n-2}).
\end{align}
Using the furher abbreviations 
\begin{align}
c:=\partial_H U^0F^{A+H}_{\ev}\\
d:=\partial_H U^0F^{A+H}_{\odd} U^0F^{A+H}\\
T_n:= R^{A}-R^{A}_{n}\\
\dot{T}_n:= \partial_H (R^{A+H}-R^{A+H}_{n}),
\end{align}
we vectorise the recursive equation and arrive at 
\begin{align}
\begin{pmatrix}\dot{T}_n\\\dot{T}_{n-1}\end{pmatrix}
= \begin{pmatrix} a & b \\  1 & 0\end{pmatrix}
\begin{pmatrix}\dot{T}_{n-1}\\\dot{T}_{n-2}\end{pmatrix}
+\begin{pmatrix} c & 0 \\  0 & d\end{pmatrix}
\begin{pmatrix}T_{n-1}\\ T_{n-2}\end{pmatrix}.
\end{align}
This yields by induction
\begin{align}
\begin{pmatrix}\dot{T}_n\\\dot{T}_{n-1}\end{pmatrix}
&= \begin{pmatrix} a & b \\  1 & 0\end{pmatrix}^{n-1}
\begin{pmatrix}\dot{T}_{1}\\\dot{T}_{0}\end{pmatrix}\\
&+\sum_{k=0}^{n-2}\begin{pmatrix} a & b \\  1 & 0\end{pmatrix}^{k}
\begin{pmatrix} c & 0 \\  0 & d\end{pmatrix}
\begin{pmatrix}T_{n-1-k}\\ T_{n-2-k}\end{pmatrix}.
\end{align}
Inserting \eqref{T iterated} then gives
\begin{align}
\begin{pmatrix}\dot{T}_n\\\dot{T}_{n-1}\end{pmatrix}
&= \begin{pmatrix} a & b \\  1 & 0\end{pmatrix}^{n-1}
\begin{pmatrix}\dot{T}_{1}\\\dot{T}_{0}\end{pmatrix}\\
&+\sum_{k=0}^{n-2}\begin{pmatrix} a & b \\  1 & 0\end{pmatrix}^{k}
\begin{pmatrix} c & 0 \\  0 & d\end{pmatrix}
\begin{pmatrix} a & b \\  1 & 0\end{pmatrix}^{n-2-k}
\begin{pmatrix}T_{1}\\ T_{0}\end{pmatrix}.
\end{align}

\end{proof}


\end{proof}









\section{Geometric Construction of the Phase}\label{chapter geometery}
Next we introduce the set of four potentials we work with, as well as the argument of a complex number and an 
invertible bounded operator. For complex numbers the convention we chose here differs slightly from the standard in the literature,
which is why we also use a slightly non standard name for this function.
\begin{Def}[ polar decomposition and spectral projections]
We denote by \(\mathcal{H}=L^2(\mathbb{R}^3,\mathbb{C})\).
For \(X:\mathcal{H}\rightarrow \mathcal{H}\) bounded
\begin{equation}
\AG(X):=X |X|^{-1}.
\end{equation}
Furthermore, we define for any complex number \(z\in \mathbb{C}\backslash \{0\}\)
\begin{equation}
\ag(z):=\frac{z}{|z|} .
\end{equation}
In abuse of notation we will define the expression
\begin{equation}
\partial_t \ln f(t):=\frac{\partial_t f(t)}{f(t)},
\end{equation}
for any differentiable \(f:\mathbb{R}\rightarrow \mathbb{C}\backslash \{0\} \), 
even if the expression \(\ln f(t)\) cannot be interpreted as the principle
branch of the logarithm.

We also introduce \(S^1:=\{z\in\mathbb{C}\mid |z|=1\}\).

\end{Def}





\begin{Def}[scattering operator and phases]\label{def: S bar, gamma, cA}
We define for all \(A,B\in\mathcal{V} \)
\begin{align}
S_{A,B}:=U^{A}_{\Sigma_{\mathrm{in}},\Sigma_{\mathrm{out}}}U^{B}_{\Sigma_{\mathrm{out}},\Sigma_{\mathrm{in}}},
\end{align}
\todo{vllt direkt mit \(S_A\) definieren, warte ab bis abschätzung der ableitungen geschehen ist}
where \(\Sigma_{\mathrm{out}}\) and \(\Sigma_{\mathrm{int}}\)  are Cauchy-surfaces of Minkowski spacetime such that 
\begin{align}
&\forall (x,y)\in \supp A\cup\supp B\times \Sigma_{\mathrm{in}}: (x-y)^2 \ge 0\Rightarrow x^0>y^0,\\
&\forall (x,y)\in \supp A\cup\supp B\times \Sigma_{\mathrm{out}}: (x-y)^2 \ge 0\Rightarrow x^0<y^0
\end{align}
holds.
Let 
\begin{align}
\mathrm{dm}:=\{(A,B)\in\mathcal{V}^2\mid P^- S_{A,B}P^-\text{ and }\\
 P^- S_{B,A}P^-:\mathcal{H}^- \righttoleftarrow  \text{ are invertible}\},
\end{align}
we define
\begin{equation}\label{dom s bar}
\dom\overline{S}:=\{(A,B)\in \mathrm{dm}\mid  \overline{A~B}\times\overline{A~B} \subseteq \mathrm{dm} \},
\end{equation}
where \(\overline{A~B}\) is the line segment connecting \(A\) and \(B\) in \(\mathcal{V}\).
Furthermore, we choose for all \(A,B\in \dom \overline{S}\) the lift
\begin{align}
\overline{S}_{A,B}=\mathcal{R}_{\AG((P^- S_{A,B}P^-)^{-1})} \mathcal{L}_{S_{A,B}}.
\end{align}

For \((A,B),(B,C), (C,A)\in\dom\overline{S}\), we define 
 the complex numbers 
\begin{align}\label{def: gamma}
\gamma_{A,B,C}&:=\ag(\det_{\mathcal{H}^-} (P^- S_{A,B} P^- S_{B,C} P^- S_{C,A}P^-)),\\
\Gamma_{A,B,C}&:=\ag(\gamma_{A,B,C}).
\end{align}
We will see in lemma \ref{gamma attri} that \(\gamma_{A,B,C}\neq 0\) and
\( P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}-1\) is traceclass, so that \(\Gamma_{A,B,C}\) is well-defined.
Lastly we introduce the partial derivative in the direction of any four-potential \(F\) by
\begin{equation}
\partial_F T(F):=\partial_{\varepsilon}T(\varepsilon F)|_{\varepsilon =0}
\end{equation}
and for  \(A,B,C\in\mathcal{V}\) the function
\begin{equation}
c_A(F,G):=-i \partial_F \partial_G  \Im \tr [P^- S_{A,A+F} P^+ S_{A,A+G} P^-] .
\end{equation}
\end{Def}

\begin{Lemma}[properties of \(\dom\overline{S}\)]\label{lem properties of dom s bar}
The set \(\dom \overline{S}\) has the following properties:
\begin{enumerate}
\item contains the diagonal: \(\{(A,A)\mid A\in\mathcal{V}\}\subseteq \dom\overline{S}\).
\item openness: \(\forall n \in \mathbb{N}: \left\{s\in\mathbb{R}^{2n}\mid \left(\sum_{k=1}^n s_k A_k,\sum_{k=n+1}^{2n} s_{k} A_{k} \right)\in \dom\overline{S}\right\}\) is an open subset of \(\mathbb{R}^{2n}\) for all \(A_1,\dots A_{2n}\in\mathcal{V}\).
\item symmetry:  \((A,A')\in\dom\overline{S}\iff (A',A)\in\dom\overline{S}\)
\item star-shaped: \((A,t A)\in \dom\overline{S}\Rightarrow \forall s\in \overline{1~~t} : (A,s A)\in\dom\overline{S}\)
\item well defined-ness of \(\overline{S}\): \(\dom\overline{S}\subseteq \{A,B\in\mathcal{V}\mid P^- S_{A,B} P^-:\mathcal{H}^- \righttoleftarrow \text{is invertible} \}\).
\end{enumerate}
We will only prove openness, as the other properties follow directly from the definition \eqref{dom s bar}. So pick \(n\in\mathbb{N}\), 
\(A_i\in\mathcal{V}\) for \(i\in \mathbb{N}, i\le 2 n\) and \(s\in\mathbb{R}^{2n}\)
such that \(\left(\sum_{k=1}^n s_k A_k,\sum_{k=n+1}^{2n} s_{k} A_{k} \right)\in\dom\overline{S}\). 
We have to find a neighbourhood \(U\subseteq \mathbb{R}^{2n}\) of \(s\) such that 
\(\{ \left(\sum_{k=1}^n s_k' A_k,\sum_{k=n+1}^{2n} s_{k}' A_{k} \right) \mid s'\in U\}\subseteq \dom\overline{S}\) holds. 
In doing so we have to ensure that the square

\begin{align}
  \overline{\sum_{k=1}^n s_k A_k~~~\sum_{k=n+1}^{2n} s_{k} A_{k} }^2
\end{align}
stays a subsets of \(\mathrm{dm}\) for all \(s'\in U\). Now pick a metric \(d\) on \(\mathbb{R}^n\) and define 
\begin{align}\nonumber
&r:=\inf \left\{d(s,s')\mid \overline{\sum_{k=1}^n s_k' A_k~~\sum_{k=n+1}^{2n} s_k' A_k }^2 ~~\cap \mathrm{dm}^c\neq \emptyset \right\}.
\end{align}
It cannot be the case that \(r=0\), because the metric is continuous, the square compact in \(\mathbb{R}^{2n}\) 
and the set of invertible bounded operators (defining \(\mathrm{dm}\)) is open in the topology generated by the operator norm.
 \todo{reicht das, oder soll ich das ausführlicher schreiben?}
If \(r=\infty\) then \(U=\mathbb{R}^{2n}\) will suffice. If \(r\in\mathbb{R}^+\) then \(U=B_r(s,t)\) the open ball of radius \(r\) around \(s\) works.
\end{Lemma}

\subsection{Main Result of Construction}


\begin{Def}[causal splitting]
We define a causal splitting as a function 
\begin{align}
&c^+:\mathcal{V}^3\rightarrow \mathbb{C}, \\
&(A,F,G)\mapsto c_A^+(F,G),
\end{align}
such that \(c^+\) restricted to any finite dimensional subspace is smooth in the 
first argument and linear in the second and third argument.
Furthermore \(c^+\) should satisfy
\begin{align}\label{c+ 1}
c_A(F,G)=c_A^+(F,G)-c_A^+(G,F),\\\label{c+ 2}
\partial_H c^+_{A+H}(F,G)=\partial_G c^+_{A+G}(F,H),\\\label{c+ 3}
\forall F \prec G: c_A^+(F,G)=0.
\end{align}
\end{Def}

\begin{Def}[current]
Given a lift \(\hat{S}_{A,B}\) of the one-particle scattering operator \(S_{A,B}\) for which the derivative in the following expression exists,
 we define the associated current by Bogolyubov's formula:
\begin{equation}
j_A^{\hat{S}}(F):=i\partial_F \left\langle \Omega, \hat{S}_{A,A+F} \Omega\right\rangle.
\end{equation}
\end{Def}

\begin{Thm}[existence of causal lift]\label{thm: geometry}
Given a causal splitting \(c^+\), there is a second quantised scattering operator \(\tilde{S}\), lift of the one-particle scattering operator \(S\)
with the following properties
\begin{align}
&\forall A,B,C\in \mathcal{V}:\tilde{S}_{A,B}\tilde{S}_{B,C}=\tilde{S}_{A,C}\\
&\forall F\prec G: \tilde{S}_{A,A+F}=\tilde{S}_{A+G,A+F+G}
\end{align}
and the associated current satisfies
\begin{equation}
\partial_G j_{A+G}^{\tilde{S}}(F)=\left\{\begin{matrix} -2i c_A(F,G)  &\text{ for } G\prec F\\ 0 &\text{  otherwise.}  \end{matrix} \right.
\end{equation}
\end{Thm}

\subsection{Proofs}


Since the phase of a lift relative to any other lift is fixed by a single matrix element, we may use the vacuum expectation values to characterise the
phase of a lift. The function \(c\) captures the dependence of this object on variation of the external fields, the connection between vacuum expectation
values and \(c\) becomes clearer with the next lemma.

\begin{Lemma}[properties of \(\Gamma\)]\label{gamma attri}
The function \(\Gamma\) has the following properties for all  \(A,B,C,D\in\mathcal{V}\) such that the expressions occurring in each equation are well defined:
\begin{align}\label{gamma attri0}
&\gamma_{A,B,C}\neq 0\\\notag
&\Gamma_{A,B,C}=\det_{\mathcal{H}^-}(P^--P^-S_{A,C}P^+S_{C,A}P^- \\\label{gamma attri1}
&\hspace{5cm}- P^- S_{A,B} P^+ S_{B,C} P^- S_{C,A} P^-)\\\label{gamma attri2}
&\Gamma_{A,B,C}^{-1}=\ag(\langle \Omega, \overline{S}_{A,B} \overline{S}_{B,C} \overline{S}_{C,A}\Omega\rangle )\\\label{gamma attri3}
&\Gamma_{A,B,C}=\Gamma_{B,C,A}=\frac{1}{\Gamma_{B,A,C}}\\\label{gamma attri4}
&\Gamma_{A,A,B}=1\\\label{gamma attri5}
&\Gamma_{A,B,C}\Gamma_{B,A,D}\Gamma_{A,C,D}\Gamma_{C,B,D}=1 \\\label{gamma attri6}
&\Gamma_{A,B,C}=\Gamma_{D,B,C}\Gamma_{A,D,C}\Gamma_{A,B,D} \\\label{gamma attri7}
&\overline{S}_{A,C}=\Gamma_{A,B,C}\overline{S}_{A,B}\overline{S}_{B,C}\\\label{gamma attri8}
&c_A(B,C)=\partial_B \partial_C \ln \Gamma_{A,A+B,A+C}.
\end{align}
\end{Lemma}
\begin{proof}
Pick  \(A,B,C\in\mathcal{V}\) such that \(\|1-S_{X,Y}\|<1\) for \(X,Y\in\{A,B,C\}\). 
By definition \(\gamma\) is
\begin{equation}
\gamma_{A,B,C}=\det_{\mathcal{H}^-}(P^- S_{A,B} P^- S_{B,C} P^- S_{C,A} P^-).
\end{equation}
The operator whose determinant we take in the last line is a product
\begin{equation}
P^- S_{A,B} P^- S_{B,C} P^- S_{C,A} P^-=P^- S_{A,B}P^-~~ P^- S_{B,C}P^-~~ P^- S_{C,A} P^-.
\end{equation}
The three factors appearing in this product are all invertible, hence the product is also invertible as operators of type \(\mathcal{H}^-\rightarrow \mathcal{H}^-\)
 because of the conditions of \(\{A,B,C\}\) imply that \(\|P^--P^-S_{X,Y}P^-\|<1\) which means that the Von Neumann series of the inverse converges, 
therefore if the determinant exists we have \(\gamma_{A,B,C}\neq 0\).
To see that it does exist, we reformulate
\begin{align}
&\gamma_{A,B,C}=\det_{\mathcal{H}^-}(P^- S_{A,B} P^- S_{B,C} P^- S_{C,A} P^-)\\
&=\det_{\mathcal{H}^-}(P^-S_{A,C}P^-S_{C,A}P^- - P^- S_{A,B} P^+ S_{B,C} P^- S_{C,A} P^-)\\\label{eq: gamma proof of first attri}
&=\det_{\mathcal{H}^-}(P^--P^-S_{A,C}P^+S_{C,A}P^- - P^- S_{A,B} P^+ S_{B,C} P^- S_{C,A} P^-),
\end{align}
now we know by a classic result of Ruisnaars \cite{ruisnaar&ivp0} that \(P^+S_{X,Y}P^-\) is a Hilbert-Schmidt operator for our setting,
hence \(\gamma\) and also \(\Gamma\) are well defined.

 Equation 
\eqref{eq: gamma proof of first attri} also proves \eqref{gamma attri1}. Next we show \eqref{gamma attri2}. 
Borrowing notation from \cite[section 2]{ivp0} to identify \(\Omega=\bigwedge \Phi\) with the injection \(\Phi: \mathcal{H}^-\hookrightarrow\mathcal{H}\)
and \(\bigwedge\) is used to construct the infinite wedge spaces that are the perspective of Fock space introduced in \cite{ivp0}. 
We begin by reformulating the right hand side of  \eqref{gamma attri2}
\begin{align}
 &\langle \Omega, \overline{S}_{A,B} \overline{S}_{B,C} \overline{S}_{C,A}\Omega\rangle \\\notag
&=\langle \bigwedge \Phi, \bigwedge \left(S_{A,B}S_{B,C}S_{C,A}\Phi \AG(P^-S_{C,A} P^-)^{-1}\right.\\\notag
&\hspace{3cm}\left. \AG(P^-S_{B,C} P^-)^{-1} \AG(P^-S_{A,B} P^-)^{-1}  \right)\rangle \\
&=\langle \bigwedge \Phi, \bigwedge \left(\Phi \AG(P^-S_{C,A} P^-)^{-1}\right.\\\notag
&\hspace{3cm}\times\left. \AG(P^-S_{B,C} P^-)^{-1} \AG(P^-S_{A,B} P^-)^{-1}  \right)\rangle \\
&=\det_{\mathcal{H}^-}\left( (\Phi)^*  \left[\Phi \AG(P^- S_{C,A} P^-)^{-1} \AG(P^-S_{B,C} P^-)^{-1}\right.\right.\\\notag
&\hspace{6cm}\times\left.\left. \AG(P^-S_{A,B} P^-)^{-1} \right] \right)\\
&=\det_{\mathcal{H}^-}  \left()\AG(P^- S_{C,A} P^-)^{-1} \AG(P^- S_{B,C} P^-)^{-1}\right.\\ \notag
&\hspace{6cm}\left.\times\AG(P^-S_{A,B} P^-)^{-1}\right)  \\\label{eq:1/arg}
&=\frac{1}{\det_{\mathcal{H}^-}  \AG(P^- S_{A,B} P^-) \AG(P^- S_{B,C} P^-) \AG(P^-S_{C,A} P^-) }.
\end{align}
We first note that \(\det_{\mathcal{H}^-}|P^- S_{X,Y}P^-|\in\mathbb{R}^+\) for \(X,Y\in \{A,B,C\}\). This is well defined because 
\begin{align}
&\langle \Omega, \overline{S}_{X,Y}\Omega\rangle
=\langle \bigwedge \Phi, \bigwedge(S_{X,Y}\Phi \AG(P^- S_{X,Y}P^-)^{-1})\rangle\\
&=\det_{\mathcal{H}^-} \left( \Phi^* S_{X,Y}\Phi \AG(P^- S_{X,Y}P^-)^{-1}\right)\\
&=\det_{\mathcal{H}^-} \left( P^- S_{X,Y} P^- \AG(P^- S_{X,Y}P^-)^{-1}\right)\\
&=\det_{\mathcal{H}^-} \left(\AG(P^- S_{X,Y}P^-)^{-1} P^- S_{X,Y} P^- \right)\\
&=\det_{\mathcal{H}^-} \left(\AG(P^- S_{X,Y}P^-)^{-1} \AG(P^- S_{X,Y}P^-) |P^- S_{X,Y} P^-| \right)\\
&=\det_{\mathcal{H}^-} |P^- S_{X,Y}P^-|
\end{align}
holds. Moreover this determinant does not vanish, since the\\ \(P^- S_{X,Y}P^-\) is invertible. Also clearly the eigenvalues are positive
since \(|P^- S_{X,Y}P^-|\) is an absolute value. We continue with the result of \eqref{eq:1/arg}. Thus, we find
\begin{align}\label{eq: arg representation}
&\langle \Omega, \overline{S}_{A,B} \overline{S}_{B,C} \overline{S}_{C,A}\Omega\rangle^{-1}\\
&=\det_{\mathcal{H}^-}\left(  \AG(P^- S_{A,B} P^-) \AG(P^- S_{B,C} P^-) \AG(P^-S_{C,A} P^-)  \right)\\\notag
&=\det_{\mathcal{H}^-}\left(  \AG(P^- S_{A,B} P^-) \AG(P^- S_{B,C} P^-) P^-S_{C,A} P^-\right.\\
&\hspace{7.5cm}\times\left. |P^-S_{C,A} P^-|^{-1}  \right)\\\notag
&=\det_{\mathcal{H}^-}\left(  \AG(P^- S_{A,B} P^-) \AG(P^- S_{B,C} P^-) P^-S_{C,A} P^-  \right)\\
&\hspace{7cm}\times \det_{\mathcal{H}^-}|P^-S_{C,A} P^-|^{-1} \\\notag
&=\det_{\mathcal{H}^-}\left( P^-S_{C,A} P^- \AG(P^- S_{A,B} P^-) \AG(P^- S_{B,C} P^-)  \right)\\
&\hspace{7cm}\times \det_{\mathcal{H}^-}|P^-S_{C,A} P^-|^{-1} \\\notag
&=\frac{\det_{\mathcal{H}^-}\left(P^- S_{A,B} P^- P^- S_{B,C} P^- P^-S_{C,A} P^-  \right)}
{\det_{\mathcal{H}^-}|P^- S_{A,B} P^-| \cdot \det_{\mathcal{H}^-}|P^-S_{B,C} P^-|}\\
&\hspace{7cm}\times\frac{1}{\det_{\mathcal{H}^-}|P^-S_{C,A} P^-|}.
\end{align}
Now since the denominator of this fraction is real we can use \eqref{gamma attri1} to identity
\begin{equation}
\ag(\langle \Omega, \overline{S}_{A,B} \overline{S}_{B,C} \overline{S}_{C,A}\Omega\rangle)=\Gamma_{A,B,C}^{-1},
\end{equation}
which proves \eqref{gamma attri2}.

For the first equality in \eqref{gamma attri3} we use \(\det X (1+Y) X^{-1}=\det (1+Y)\) for any \(Y\) trace-class and 
 \(X\) bounded and invertible. So we can cyclicly permute the factors \(P^- S_{X,Y}P^-\) in the determinant and find
\begin{align*}
&\Gamma_{A,B,C}=\ag(\det_{\mathcal{H}^-} P^- S_{A,B}P^-S_{B,C}P^-S_{C,A}P^- )\\
&\quad=\ag(\det_{\mathcal{H}^-} P^-S_{C,A}P^- S_{A,B}P^-S_{B,C}P^- )
=\Gamma_{C,A,B}.
\end{align*}
For the second equality of \eqref{gamma attri3} we use \eqref{gamma attri1}
to represent both \(\Gamma_{A,B,C}\) and \(\Gamma_{B,A,C}\). Using this and the manipulations of the determinant 
we already employed, we arrive at
\begin{align}
&\Gamma_{A,B,C}\Gamma_{B,A,C}\\
&=\ag(\det_{\mathcal{H}^-} (P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}P^-))\\
&\quad\times\ag(\det_{\mathcal{H}^-} (P^-S_{B,A}P^-S_{A,C}P^-S_{C,B}P^-))\\
&=\ag(\det_{\mathcal{H}^-} (P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}P^-))\\
&\quad\times(\ag(\det_{\mathcal{H}^-} (P^-S_{B,C}P^-S_{C,A}P^-S_{A,B}P^-)))^*\\
&=\ag(\det_{\mathcal{H}^-} (P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}P^-))\\
&\quad\times(\ag(\det_{\mathcal{H}^-} (P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}P^-)))^*\\
&=|\ag(\det_{\mathcal{H}^-} (P^-S_{A,B}P^-S_{B,C}P^-S_{C,A}P^-))|^2=1,
\end{align}
which proves \eqref{gamma attri3}. 

Next, using \eqref{def: gamma} inserting twice the same argument yields
\begin{equation}
\gamma_{A,A,C}=\det_{\mathcal{H}^-} P^-S_{A,C}P^-S_{C,A}P^-
=\det_{\mathcal{H}^-} (P^- S_{C,A} P^-)^*P^-S_{C,A}P^-\in \mathbb{R}^+,
\end{equation}
hence \eqref{gamma attri4} follows.


For proving \eqref{gamma attri5} we will use the definition of \(\Gamma\) directly and repeatedly use that we can cyclicly permute operator groups of the form
\(P^- S_{X,Y}P^-\) for \(X,Y\in \{A,B,C,D\}\) in the determinant, i.e.
\begin{equation}\label{tetraeder 1}
\det P^- S_{X,Y}P^- O = \det O P^- S_{X,Y}P^-.\tag{\(\circlearrowleft\)}
\end{equation}
This is possible, because \(P^- S_{X,Y}P^-\) is bounded and invertible. Furthermore we will use that 
\begin{equation}\label{tetraeder 2}
\det O_1 O_2 = \det O_1 \det O_2\tag{\(\leftrightarrow\)}
\end{equation}
holds whenever 
both \(O_1\) and \(O_2\) have a determinant. Moreover for any  \((P^- S_{X,Y}P^-)^*P^- S_{X,Y}P^-\) is the modulus squared of an invertible operator and hence
its determinant is positive which means that 
\begin{equation}\label{tetraeder 3}
\ag \det (P^- S_{X,Y}P^-)^*P^- S_{X,Y}P^-=1.\tag{\(\ag\!|\,\, |\)}
\end{equation}
These three rules will be repeatedly used. We calculate
\begin{align}
&\Gamma_{A,B,C}\Gamma_{B,A,D}\Gamma_{A,C,D}\Gamma_{C,B,D}\\\notag
&=\ag \det_{\mathcal{H}^-}P^- S_{A,B}P^- S_{B,C}P^- S_{C,A}P^- \\
&\hspace{1,5cm}\times\ag \det_{\mathcal{H}^-}P^- S_{B,A}P^- S_{A,D}P^- S_{D,B}P^-~~ \Gamma_{A,C,D}\Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 1}}{=}
\ag \det_{\mathcal{H}^-}P^-S_{A,D}P^- S_{D,B}P^- S_{B,A}P^- \\
&\hspace{1.5cm}\times \ag \det_{\mathcal{H}^-}P^- S_{A,B}P^- S_{B,C}P^- S_{C,A}P^- ~~  \Gamma_{A,C,D}\Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 2}}{=}
\ag \det_{\mathcal{H}^-}\big(P^-S_{A,D}P^- S_{D,B} \big[P^- S_{B,A} P^- S_{A,B}P^-\big]\\
&\hspace{5cm}\times S_{B,C}P^- S_{C,A}P^-\big) ~ \Gamma_{A,C,D}\Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 1}}{=}
\ag \det_{\mathcal{H}^-}P^-S_{B,C}P^- S_{C,A}P^-S_{A,D}P^- S_{D,B} \big[P^- S_{B,A} P^- S_{A,B}P^-\big]  \\
&\hspace{8cm}\times \Gamma_{A,C,D}\Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 2}}{=}
\ag \det_{\mathcal{H}^-}P^-S_{B,C}P^- S_{C,A}P^-S_{A,D}P^- S_{D,B}P^-\\
&  \hspace{4cm}\times\ag \det_{\mathcal{H}^-} P^- S_{B,A} P^- S_{A,B}P^-  ~~ \Gamma_{A,C,D}\Gamma_{C,B,D}\\
&\overset{\eqref{tetraeder 3}}{=}
\ag \det_{\mathcal{H}^-}P^-S_{B,C}P^- S_{C,A}P^-S_{A,D}P^- S_{D,B}P^-   ~~ \Gamma_{A,C,D}\Gamma_{C,B,D}\\
&\overset{\eqref{tetraeder 1}}{=}
\ag \det_{\mathcal{H}^-}P^-S_{A,D}P^- S_{D,B}P^-S_{B,C}P^- S_{C,A}P^-   ~~ \Gamma_{A,C,D} \Gamma_{C,B,D}\\\notag
&=\ag \det_{\mathcal{H}^-}P^- S_{A,C}P^- S_{C,D}P^- S_{D,A}P^-\\
&\hspace{1.5cm}\times\ag \det_{\mathcal{H}^-}P^-S_{A,D}P^- S_{D,B}P^-S_{B,C}P^- S_{C,A}P^-   ~~ \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 2}}{=}
\ag \det_{\mathcal{H}^-}\big(P^- S_{A,C}P^- S_{C,D}P^-\big[ P^- S_{D,A}P^-P^-S_{A,D}P^- \big]\\
&\hspace{4cm}\times  S_{D,B}P^-S_{B,C}P^- S_{C,A}P^-\big)   ~~ \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 1}}{=}
\ag \det_{\mathcal{H}^-}\big(P^- S_{D,B}P^-S_{B,C}P^- S_{C,A}P^- S_{A,C}P^- S_{C,D}P^-\\
&\hspace{4cm}\times\big[P^- S_{D,A}P^-P^-S_{A,D}P^- \big]\big)    ~~ \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 2}}{=}
\ag \det_{\mathcal{H}^-}P^- S_{D,B}P^-S_{B,C}P^- S_{C,A}P^- S_{A,C}P^- S_{C,D}P^- \\
&\hspace{4cm}\times\ag \det_{\mathcal{H}^-} P^-S_{D,A}P^-P^-S_{A,D}P^-    ~~ \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 3}}{=}
\ag \det_{\mathcal{H}^-}\big(P^- S_{D,B}P^-S_{B,C}P^-\big[P^- S_{C,A}P^- S_{A,C}P^-\big]\\
&\hspace{7cm}\times P^- S_{C,D}P^-\big)     \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 1}}{=}
\ag \det_{\mathcal{H}^-}P^- S_{C,D}P^- S_{D,B}P^-S_{B,C}P^- \big[P^- S_{C,A}P^- S_{A,C}P^-\big]\\     
&\hspace{9cm}\times \Gamma_{C,B,D}\\\notag
&\overset{\eqref{tetraeder 2}}{=}
\ag \det_{\mathcal{H}^-}P^- S_{C,D}P^- S_{D,B}P^-S_{B,C}P^-\\
&\hspace{4cm}\times \ag \det P^- S_{C,A}P^- S_{A,C}P^-     ~~ \Gamma_{C,B,D}\\
&\overset{\eqref{tetraeder 3}}{=}
\ag \det_{\mathcal{H}^-}P^- S_{C,D}P^- S_{D,B}P^-S_{B,C}P^-  ~~ \Gamma_{C,B,D}\\\notag
&=
\ag \det_{\mathcal{H}^-}P^- S_{C,D}P^- S_{D,B}P^-S_{B,C}P^- \\
&\hspace{4cm}\times \ag \det_{\mathcal{H}^-} P^- S_{C,B}P^- S_{B,D}P^- S_{D,C}P^- \\
&=
|\ag \det_{\mathcal{H}^-}P^- S_{C,D}P^- S_{D,B}P^-S_{B,C}P^-|^2=1. 
\end{align}

Equation \eqref{gamma attri6} is a direct consequence of \eqref{gamma attri5} and \eqref{gamma attri3}.

For \eqref{gamma attri7} we realise that according to \cite{ivp0} that two lifts can only differ by a phase,
that is
\begin{equation}
\overline{S}_{A,C}=\alpha \overline{S}_{A,B} \overline{S}_{B,C}
\end{equation}
for some \(\alpha\in \mathbb{C}, |\alpha|=1\). 

In order to identify \(\alpha\) we recognise that \(\overline{S}_{X,Y}=\overline{S}_{Y,X}^{-1}\) for four potentials \(X,Y\) 
and find
\begin{equation}
1 \alpha^{-1}= \overline{S}_{A,B} \overline{S}_{B,C}\overline{S}_{C,A}.
\end{equation}
Now we take the vacuum expectation value on both sides of this equation and use \eqref{gamma attri2} to find
\begin{equation}
\alpha^{-1}=\langle\Omega,\overline{S}_{A,B} \overline{S}_{B,C}\overline{S}_{C,A}\Omega\rangle = \Gamma_{A,B,C}^{-1}.
\end{equation}

Finally we prove \eqref{gamma attri8}. We start from the right hand side of this equation 
and work our way towards the left hand side of it. In the following calculation we will repeatedly make use of the fact that 
\((P^-S_{A,A+B}P^-S_{A+B,A}P^- )\) is the absolute value squared of an invertible operator and has a determinant, which is therefore positive. 
For the marked equality we will use that for a differentiable function \(z:\mathbb{R}\rightarrow \mathbb{C}\) at points \(t\) where \(z(t)\in\mathbb{R}^+\)
holds, we have
\begin{align}\notag
(z/|z|)'(t)=\frac{z'}{|z|}(t)+\frac{-z}{|z|^2}\frac{z'z^*+ {z^*}'z}{2|z|}(t) =\frac{z'}{2|z|}(t)-\frac{z^2{z^*}'}{2 |z|^3}(t)\\
=i (\Im (z'))/z(t).
\end{align}
Furthermore, we will use the following  expressions for the derivative of the determinant which holds for all functions 
\(M:\mathbb{R}\rightarrow (\mathcal{H}\rightarrow \mathcal{H})\) such that \(M(t)-1\) is traceclass and \(M\) is invertible 
for all \(t\in\mathbb{R}\)
\begin{align}\label{diff det}
\partial_\varepsilon \det M(\varepsilon)|_{\varepsilon=0}=\det M(0) \tr (M^{-1}(0)\partial_\varepsilon M(\varepsilon)|_{\varepsilon}),
\end{align}
likewise we need the following expression for the derivative of \(M^{-1}\) for 
\(M:\mathbb{R}\rightarrow (\mathcal{H}\rightarrow \mathcal{H})\) such that \(M(t)\) is invertible and bounded for every \(t\in\mathbb{R}\)
\begin{equation}
\partial_{\varepsilon}M^{-1}(\varepsilon)|_{\varepsilon=0}=-M^{-1}(0) \partial_{\varepsilon}M(\varepsilon)|_{\varepsilon=0}M^{-1}(0).
\end{equation}
We compute
\begin{align}
\partial_B \partial_C \ln \Gamma_{A,A+B,A+C}\\
\overset{\eqref{gamma attri1}}{=} 
\partial_B \partial_C \ln \ag(\det_{\mathcal{H}^-} (P^-S_{A,A+B}P^-S_{A+B,A+C}P^- S_{A+C,A}P^-))\\
=\partial_B \frac{\partial_C\ag(\det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A+C}P^- S_{A+C,A}P^-))}{\ag(\det_{\mathcal{H}^-} (P^-S_{A,A+B}P^-S_{A+B,A}P^- ))}\\
=\partial_B \partial_C\ag(\det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A+C}P^- S_{A+C,A}P^-))\\
\overset{*}{=}
i\partial_B \frac{\Im \partial_C \det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A+C}P^- S_{A+C,A}P^-)}{\det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A}P^-)}\\\notag
=i\partial_B \Big[\frac{\det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A}P^-)}{\det_{\mathcal{H}^-}(P^-S_{A,A+B}P^-S_{A+B,A}P^-)}\\\notag
\times \Im  \tr ((P^-S_{A,A+B}P^-S_{A+B,A}P^-)^{-1}\\
\times\partial_C P^-S_{A,A+B}P^-S_{A+B,A+C}P^- S_{A+C,A}P^-)\Big]\label{eq ca 1}
\end{align}
The fraction in front of the trace equals \(1\). As a next step we replace the second but last projector \(P^-=1-P^+\), the resulting first summand vanishes,
because the dependence on \(C\) cancels. This results in 
\begin{align}\notag
&\eqref{eq ca 1}=-i\partial_B \Im \tr((P^-S_{A,A+B}P^-S_{A+B,A}P^-)^{-1}\\
&\hspace{3cm}\times\partial_C P^-S_{A,A+B}P^-S_{A+B,A+C}P^+ S_{A+C,A}P^-).\label{eq ca 2}
\end{align}
Now, because \(P^+P^-=0\) only one summand of the product rule survives:
\begin{align}\notag
&\eqref{eq ca 2}=-i\partial_B \Im \tr((P^-S_{A,A+B}P^-S_{A+B,A}P^-)^{-1}\\
&\hspace{3cm}\times\partial_C P^-S_{A,A+B}P^-S_{A+B,A}P^+ S_{A+C,A}P^-).\label{eq ca 3}
\end{align}
Next we use 
\((M N )^{-1}= N^{-1} M^{-1}\) for invertible operators \(M\) and \(N\) for the first factor in the trace and cancel as much as possible of
the second factor:
\begin{align}\notag
\eqref{eq ca 3}=-i\partial_B \Im \tr((P^-S_{A+B,A}P^-)^{-1}  P^-S_{A+B,A}\\
\times P^+ \partial_C S_{A+C,A}P^-)\\\notag
=-i \Im \tr(\partial_B[(P^-S_{A+B,A}P^-)^{-1}  P^-S_{A+B,A}\\
\times P^+ \partial_C S_{A+C,A}P^-])\\
=-i \Im \tr(\partial_B  P^-S_{A+B,A}P^+ \partial_C S_{A+C,A}P^-)\\
=-i \Im \tr(\partial_B  P^-S_{A,A+B}P^+ \partial_C S_{A,A+C}P^-)\\
=-i \partial_B\partial_C\Im \tr(  P^-S_{A,A+B}P^+  S_{A,A+C}P^-)
\end{align}
which proves the claim.

\end{proof}



In order to construct the lift announced in theorem \ref{thm: geometry}, we first construct a reference lift \(\hat{S}\), that is well defined on all of \(\mathcal{V}\). 
Afterwards we will study the dependence of the relative phase between 
this global lift \(\hat{S}_{0,A}\) and a local lift given by \(\hat{S}_{0,B}\overline{S}_{B,A}\) for \(B-A\) small. 
By exploiting properties of this phase and the causal splitting \(c^+\) we will construct a global lift that has the desired properties.

Since \(\mathcal{V}\) is star shaped, we may reach any four-potential \(A\) from \(0\) through the straight line
\(\{t A\mid t \in [0,1]\}\). 

\begin{Def}[ratio of lifts]\label{def:ratio}
For any  \(A,B\in\mathcal{V}\) and any two lifts \(S_{A,B}', S_{A,B}''\) of the one particle scattering operator \(S_{A,B}\)
we define the ratio
\begin{equation}
\frac{S_{A,B}'}{S_{A,B}''}\in S^1
\end{equation}
to be the unique complex number \(z\in S^1\) such that 
\begin{equation}
z ~S_{A,B}'' = S_{A,B}'
\end{equation}
holds.
\end{Def}

\begin{Thm}[existence of global lift]\label{thm: ex s hat}
  There is a unique map \(\hat{S}_{0,\cdot}:\mathcal{V}\to U(\mathcal{F})\) 
    which maps  \(A\in\mathcal{V}\) to a lift of \(S_{0,A}\) and solves the 
    differential equation
  \begin{equation}\label{diff s hat}
A,B\in\mathcal{V}\text{ linearly dependent}\Rightarrow \partial_B \frac{\hat{S}_{0,A+B}}{\hat{S}_{0,A}\overline{S}_{A,A+B}}=0,
\end{equation}
subject to the initial condition \(\hat{S}_{0,0}=1\).
\end{Thm}

The proof of theorem \ref{thm: ex s hat} is divided into two lemmas due to its length. We will introduce the integral flow \(\phi_A\) associated 
with the differential equation \eqref{diff s hat} for some \(A\in\mathcal{V}\). We will then study the properties of \(\phi_A\)
in the two lemmas and finally construct \(\hat{S}_{0,A}=1 \phi_A(0,1)\). In the first lemma we will establish the existence of a 
local solution. The solution will be constructed along the line \(\overline{0 ~~ A}\). In the second lemma we patch local solutions together
to a global one.



\begin{Lemma}[\(\phi\) local existence and uniqueness]\label{lem phi local}
There is a unique \(\phi_A:\{(t,s)\in\mathbb{R}^2\mid (t A, s A)\in \dom\overline{S}\} \rightarrow U(\mathcal{F})\) for every \(A\in\mathcal{V}\)
satisfying
\begin{align}\label{phi prop1}
\forall (t,s)\in \dom \phi_A: \phi_A(t,s) \text{ is a lift of } S_{tA, sA}\\\label{phi prop2}
\forall (t,s),(s,l),(l,t)\in \dom\phi_A: \phi_A(t,s)\phi_A(s,l)=\phi_A(t,l)\\\label{phi prop3}
\forall t\in\mathbb{R}: \phi_A(t,t)=1\\\label{phi prop4}
\forall s\in\mathbb{R}: \partial_{t} \left.\frac{\phi_A(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}=0.
\end{align}
\end{Lemma}
\begin{proof}
We first define the phase
\begin{align}\label{def local z}
z:\{(A,B)\in\dom\overline{S}\mid A, B \text{ linearly dependent}\} \rightarrow S^1
\end{align}
by the differential equation
\begin{equation}
\frac{d}{d x} \ln z(t A, x A) = - \left.\left( \frac{d}{dy} \ln \Gamma_{tA,x A, yA}\right)\right|_{y=x}
\end{equation}
and the initial condition 
\begin{equation}\label{z initial}
z(A,A)=1
\end{equation}
 for any \(A\in \mathcal{V}\). The phase \(z\) takes the form
\begin{equation}\label{z solution}
z(tA,xA)=\exp\left(-\int_{t}^x dx' \left.\left( \frac{d}{dx'} \ln \Gamma_{tA,y A, x' A}\right)\right|_{y=x'}\right).
\end{equation}
Please note that both differential equation and initial condition are invariant under rescaling of the potential \(A\), so \(z\) is well defined. 
We will now construct a local solution to \eqref{diff s hat} and define \(\phi_A\) using this solution.
Pick \(A\in \mathcal{V}\) the expression
\begin{equation}\label{loc s hat}
\hat{S}_{0,s A} = \hat{S}_{0, A} \overline{S}_{ A, s A} z( A, s A)
\end{equation}
solves \eqref{diff s hat} locally. Local here means that \(s\) is close enough to \(1\) such that \(( A, s A)\in\dom\overline{S}\).
Calculating the argument of the derivative of \eqref{diff s hat} we find:
\begin{align}
0= \frac{\hat{S}_{0,(s+\varepsilon) A}}{\hat{S}_{0,s A}\overline{S}_{s A, (s+\varepsilon)A}}
= \frac{\hat{S}_{0,A} \overline{S}_{A, (s+\varepsilon)A} z(A, (s+\varepsilon)A)}
{\hat{S}_{0, A} \overline{S}_{ A, s A} \overline{S}_{s A,(s+\varepsilon)}z( A, s A)}\\
\overset{\eqref{gamma attri6}}{=}
 \frac{\hat{S}_{0,A}\overline{S}_{ A, s A} \overline{S}_{s A,(s+\varepsilon)} \Gamma_{A, sA, (s+\varepsilon)A} z(A, (s+\varepsilon)A)}
{\hat{S}_{0, A} \overline{S}_{t A, s A} \overline{S}_{s A,(s+\varepsilon)}z( A, s A)}\\
= \frac{\Gamma_{tA,sA,(s+\varepsilon)A}z(tA, (s+\varepsilon)A)}{z( A, sA)}
\end{align}
Now we take the derivative with respect to \(\varepsilon\) at \(\varepsilon=0\), 
cancel the factor that does not depend on \(\varepsilon\) and relabel \(s=x\) to obtain
\begin{align}
0=\left.\left(\frac{d}{dy}(\Gamma_{ A, x A, y A} ~z( A, y A))\right)\right|_{y=x}\\
\iff \frac{d}{dx}\ln z(tA, xA)=\left.\left(-\frac{d}{dy}\ln \Gamma_{t A, xA, yA}\right)\right|_{y=x},
\end{align}
which is exactly the defining differential equation of \(z\). The initial condition of \(z\) equation \eqref{z initial} 
is necessary to match the initial condition in \eqref{loc s hat} for \(s=1\).
The connection to \(\phi\) from the statement of the lemma can now be made.
We define 
\begin{equation}\label{def phi}
\phi_A(t,s):=z(t A, s A) \overline{S}_{t A, s A},
\end{equation}
for \((tA,sA)\in\dom\overline{S}\). Since \(\overline{S}\) is a lift of \(S\), we see that
 \eqref{phi prop1} holds. Equation \eqref{phi prop3} follows from \eqref{z initial} and 
 \(\overline{S}_{tA, tA}=1\) for general \(t\in\mathbb{R}\).
 Equation \eqref{phi prop4} follows by plugging in 
\eqref{def phi} and using the differential equation for \(z\) \eqref{z initial}:
\begin{align}
\partial_s \left.\frac{\phi_A(t,s)}{\overline{S}_{t A,sA}}\right|_{s=t}
=\partial_s \left.\frac{z(tA,sA)\overline{S}_{t A, sA}}{\overline{S}_{t A, s A}}\right|_{s=t}\\
=\partial_t \left.z(tA, sA)\right|_{t=s}=0.
\end{align}


It remains to see that \eqref{phi prop2}, i.e. that 

\begin{align}\label{consistency phi}
\phi_A(t,s)\phi_A(s,l)=\phi_A(t,l)
\end{align}
holds for \((tA,sA),(sA,lA),(tA,lA)\in\dom\overline{S}\). 
In order to do so we plug in the definition \eqref{def phi} of \(\phi_A\) and obtain
\begin{align}
\phi_A(t,s)\phi_A(s,l)=\phi_A(t,l)\\
\iff z(tA,sA) z(sA,lA)\overline{S}_{tA,sA}\overline{S}_{sA,lA}=z(tA,lA)\overline{S}_{tA,lA}\\
\iff z(tA,sA) z(sA,lA)\overline{S}_{tA,sA}\overline{S}_{sA,lA}\\
=z(tA,lA)\overline{S}_{tA,s A} \overline{S}_{sA,lA}\Gamma_{tA,sA,lA}\\
\iff z(tA,sA) z(sA,lA)z(tA,lA)^{-1}=\Gamma_{tA,sA,lA}.
\end{align}
In order to check the validity of the last equality we plug in the 
ntegral formula \eqref{z solution} for \(z\), we also abbreviate 
\(\frac{d}{d x}=\partial_x\)

\begin{align}
z(tA,sA) z(sA,lA)z(tA,lA)^{-1}\\
=e^{-\int_t^s d x' \left.(\partial_{x'} \ln \Gamma_{tA,yA,x'A} )\right|_{y=x'} -\int_s^l d x' \left.(\partial_{x'} \ln \Gamma_{sA,yA,x'A} )\right|_{y=x'} }\\
\times e^{   +\int_t^l d x' \left.(\partial_{x'} \ln \Gamma_{tA,yA,x'A} )\right|_{y=x'}  }\\
=e^{-\int_l^s d x' \left.(\partial_{x'} \ln \Gamma_{tA,yA,x'A} )\right|_{y=x'}  -\int_s^l d x' \left.(\partial_{x'} \ln \Gamma_{sA,yA,x'A} )\right|_{y=x'} }\\
\overset{\eqref{gamma attri6}}{=}
e^{-\int_l^s d x' \left.(\partial_{x'} \ln \Gamma_{sA,yA,x'A} )\right|_{y=x'} 
-\int_l^s d x' \left.(\partial_{x'} \ln \Gamma_{tA,sA,x'A} )\right|_{y=x'}}\\ 
\times e^{-\int_l^s d x' \left.(\partial_{x'} \ln \Gamma_{tA,yA,sA} )\right|_{y=x'} 
 -\int_s^l d x' \left.(\partial_{x'} \ln \Gamma_{sA,yA,x'A} )\right|_{y=x'} }\\
 =e^{-\int_l^s d x' \left.(\partial_{x'} \ln \Gamma_{tA,sA,x'A} )\right|_{y=x'}}\\
  =e^{-\int_l^s d x'\partial_{x'} \ln \Gamma_{tA,sA,x'A} }\\
  \overset{\eqref{gamma attri4}}{=}\Gamma_{t A, s A, l A},
\end{align}
which proves the validity of the consistency relation 
\eqref{consistency phi}.

In order to prove uniqueness we pick \(A\in \mathcal{V}\) 
and assume there is \(\phi'\) also defined on \(\dom \phi_A\) 
and satisfies \eqref{phi prop1}-\eqref{phi prop4}. Then we may 
use \eqref{phi prop1} to conclude that for any \((t,s)\in\dom\phi_A\) 
there is
\(\gamma(t,s)\in S^1\) such that
\begin{equation}
\phi_A(t,s)=\phi'(t,s) \gamma(t,s)
\end{equation}
holds true. Picking \(l\) such that \((t,s),(s,l),(t,l)\in \dom\phi_A\) and  using \eqref{phi prop2} we find

\begin{align}
\phi'(t,s) \gamma(t,s)=\phi_A(t,s)=\phi_A(t,l)\phi_A(l,s)\\
=\gamma(t,l)\phi'(t,l) \gamma(l,s)\phi'(l,s)=\gamma(t,l) \gamma(l,s)\phi'(t,s) ,
\end{align}
hence we have
\begin{equation}
 \gamma(t,s)=\gamma(t,l) \gamma(l,s).
\end{equation}
From property \eqref{phi prop3} we find
\begin{equation}
\gamma(t,t)=1,
\end{equation}
for any \(t\).
Using equation \eqref{phi prop4} we conclude that 

\begin{align}
0=\partial_t \left.\frac{\phi'(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}
=\partial_t \left.\frac{\phi_A(s,t) \gamma(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}\\
=\partial_t \left.\gamma(s,t) \frac{\phi_A(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}
=\partial_t \left.\gamma(s,t)\right|_{t=s} + \partial_t  \left.\frac{\phi_A(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}\\
=\partial_t \left.\gamma(s,t)\right|_{t=s}.
\end{align}
Finally we find for general \((s,t)\in \dom\phi_A\):
\begin{equation}
\partial_x \gamma(s,x)|_{x=t}=\partial_x ( \gamma(s,t) \gamma(t,x))|_{x=t}=\gamma(s,t) \partial_x \gamma(t,x)|_{x=t}=0.
\end{equation}
So \(\gamma(t,s)=1\) everywhere. We conclude \(\phi_A=\phi'\).

\end{proof}



\begin{Lemma}[\(\phi\) global existence and uniqueness]\label{lem: phi global}
For any \(A\in\mathcal{V}\) the map \(\phi_A\) constructed in 
lemma \ref{lem phi local} 
can  be uniquely extended to all of \(\mathbb{R}^2\)
keeping its defining properties 
\begin{align}\label{global phi prop1}
\forall (t,s)\in \mathbb{R}^2: \phi_A(t,s) \text{ is a lift of } S_{tA, sA}\\\label{global phi prop2}
\forall (t,s),(s,l),(l,t)\in \mathbb{R}^2: \phi_A(t,s)\phi_A(s,l)=\phi_A(t,l)\\\label{global phi prop3}
\forall t\in\mathbb{R}: \phi_A(t,t)=1\\\label{global phi prop4}
\forall s\in\mathbb{R}: \partial_{t} \left.\frac{\phi_A(s,t)}{\overline{S}_{sA,tA}}\right|_{t=s}=0.
\end{align}
\end{Lemma}
\begin{proof}
Pick \(A\in\mathcal{V}\). For \(x\in\mathbb{R}\) we define the set
\begin{equation}\label{def U x}
U_x:=\{y\in\mathbb{R}\mid (x A, y A)\in \dom\overline{S}\},
\end{equation}
which according to properties 2 and 4 of lemma 
\ref{lem properties of dom s bar} is an open interval and
fulfills that \(\bigcup_{x\in\mathbb{R}} U_x\times U_x\) is an open 
neighbourhood of the diagonal \(\{(x,x)\mid x \in\mathbb{R}\}\).
Therefore \(\phi_A\) is defined for arguments that are
close enough to each other. Since 
properties \eqref{global phi prop4} and \eqref{global phi prop3} 
only concern the behavior of \(\phi_A\) at the diagonal any
extension fulfils them. 

We pick a sequence \((x_k)_{k\in\mathbb{N}}\subset \mathbb{R}\) such
that 
\begin{equation}
\bigcup_{k\in\mathbb{N}_0} U_{x_k} = \mathbb{R}
\end{equation}
holds and 
\begin{equation}
  \forall n \in \mathbb{N}_0: \bigcup_{k=0}^n U_{x_k}=:\dom_n
\end{equation}
is an open interval. Please note that such a sequence always exists. 
We are going to prove that for any \(n\in\mathbb{R}_0\) 
There is a function \(\psi_n:\dom_n\times\dom_n\to U(\mathcal{F})\), 
which satisfies the conditions
\begin{align}\label{induction psi1}
\forall (t,s)\in \dom_n\times \dom_n: \psi_n(t,s) \text{ is a lift of } S_{tA, sA}\\\label{induction psi2}
\forall s,k,l\in\dom_n: \psi_n(k,s)\psi_n(s,l)=\psi_n(k,l)\\\label{induction psi3}
\forall x,y\in\dom_n: (xA, yA)\in\dom\overline{S}\Rightarrow  \psi_n(x,y)=\phi_A(x,y)
\end{align}
and is the unique function to do so, i.e. 
any other function fulfilling properties 
\eqref{induction psi1}-\eqref{induction psi3} possibly being defined
on a larger domain coincides with \(\psi_n\) on \(\dom_n\times\dom_n\).

We start with \(\psi_0=\phi_A\)  
restricted to \(U_{x_0} \times U_{x_0}\).
This function is a restriction of \(\phi_A\) and because of 
lemma \ref{lem phi local} it 
fulfils all of the required properties directly. 
 
For the induction step we 
define \(\psi_{n+1}\) on the domain 
\(\dom_{n+1}\times \dom_{n+1}\) by
 \begin{equation}\label{def psi induction}
 \psi_{n+1}(x,y):=\left\{\begin{matrix}
 \psi_n(x,y) \quad &\text{for }x,y\in \dom_n\\
 \phi_A(x,y) \quad &\text{for } x,y\in U_{x_{n+1}}\\
 \psi_n(x,t)\phi_A(t,y)\quad &\text{for } x\in \dom_n, y\in U_{x_{n+1}}\\
 \phi_A(x,t)\psi_n(t,y)\quad &\text{for } y\in \dom_n, x\in U_{x_{n+1}}.
 \end{matrix} \right.
 \end{equation} 
In order to complete the induction step we have to show that 
\(\psi_{n+1}\) is well defined and fulfils properties
\eqref{induction psi1}-\eqref{induction psi3} 
with \(n\) replaced by \(n+1\) and is the unique function 
to do so.
  
To see that \(\psi_{n+1}\) is well defined we have to check 
that the cases in the definition agree when they overlap. 
\begin{enumerate}
  \item If we have \(x,y \in \dom_n\cap U_{x_{n+1}}\) all four cases overlap; however, the 
  alternative definitions all equal \(\phi_A(x,y)\):
\begin{align}\nonumber
  \psi_n(x,y)\overset{\eqref{induction psi3}}{=}\phi_A(x,y)\overset{\eqref{consistency phi}}{=}\phi_A(x,t) \phi_A(t,y)
  \\
\overset{\eqref{induction psi3}}{=}\left\{\begin{matrix}\psi_A(x,t) \phi_n(t,y)\\ \phi_A(x,t) \psi_n(t,y).\end{matrix}\right.
  \end{align}
  \item Furthermore, if we have \(x\in \dom_n\), \(y\in \dom_n\cap U_{x_{n+1}}\) case one 
  and three overlap. Here both calternatives are equal to
  \(\psi_n(x,y)\), since \(x,y\in \dom_n\) and we obtain:
  \begin{equation}
  \psi_n(x,y)\overset{\eqref{induction psi2}}{=}\psi_n(x,t)\psi_n(t,y)\overset{\eqref{induction psi3}}{=}\psi_n(x,t)\phi_A(t,y).
  \end{equation}
  \item Additionally, if \(y\in \dom_n\), \(x\in \dom_n\cap U_{x_{n+1}}\) case one and four overlap. 
  Here they are equal to
  \(\psi_n(x,y)\), since \(x,y\in \dom_n\) a quick calculation yields:
  \begin{equation}
  \psi_n(x,y)\overset{\eqref{induction psi2}}{=}\psi_n(x,t)\psi_n(t,y)\overset{\eqref{induction psi3}}{=}\psi_A(x,t)\psi_n(t,y).
  \end{equation}
  \item Moreover, if we have \(y\in U_{x_{n+1}}\), \(x\in \dom_n\cap U_z\) 
  case two and three overlap. Here both candidate definitions are equal to
  \(\phi_A(x,y)\), since \(x,t\in U_z\) we arrive at:
  \begin{equation}
  \phi_A(x,y)\overset{\eqref{consistency phi}}{=}\phi_A(x,t)\phi_A(t,y)\overset{\eqref{induction psi3}}{=}\psi_n(x,t)\phi_A(t,y).
  \end{equation}
  \item Also, if we have \(x\in U_{x_{n+1}}\), \(y\in \dom_n\cap U_{x_{n+1}}\) 
  case two and four overlap. In this case both alternatives are equal to
  \(\phi_A(x,y)\), since \(y,t\in U_{x_{n+1}}\) we get:
    \begin{equation}
  \phi_A(x,y)\overset{\eqref{consistency phi}}{=}\phi_A(x,t)\phi_A(t,y)\overset{\eqref{induction psi3}}{=}\phi_A(x,t)\psi_n(t,y).
  \end{equation}
  \end{enumerate}
We proceed to show the induction claim, 
starting with \(\eqref{induction psi1}_{n+1}\). By the induction 
hypothesis we know that \(\psi_n(x,y)\) as well as 
\(\phi_A(x,y)\) are lifts of \(S_{xA,yA}\) for any \((x,y)\) in their 
domain of definition. Therefore we have for \(x,y\in \dom_n \cup U_{x_{n+1}}\)
 \begin{equation}\tag{\ref{def psi induction}}
 \psi_{n+1}(x,y)=\left\{\begin{matrix}
 \psi_n(x,y) \quad &\text{for }x,y\in \dom_n,\\
 \phi_A(x,y) \quad &\text{for } x,y\in U_{x_{n+1}},\\
 \psi_n(x,t)\phi_A(t,y)\quad &\text{for } x\in \dom_n, y\in U_{x_{n+1}},\\
 \phi_A(x,t)\psi_n(t,y)\quad &\text{for } y\in \dom_n, x\in U_{x_{n+1}},
 \end{matrix} \right.
 \end{equation} 
where each of the lines is a lift of \(S_{xA,y A}\) whenever the expression is defined.


Equation \(\eqref{induction psi2}_{n+1}\) we will again show in a case 
by case manner depending on the \(s,k\) and \(l\):
\begin{enumerate}
\item \(s,k,l\in \dom_{n}\): 
\(\eqref{induction psi2}_{n+1}\) follows directly from the induction hypothesis;
\item  \(s,k\in \dom_{n}\) and \(l\in U_{x_{n+1}}\):
\begin{align}\nonumber
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\psi_n(s,k)\psi_n(k,t)\phi_A(t,l)\\
\overset{\eqref{induction psi2}}{=} \psi_n(s,t)\phi_A(t,l)=\psi_{n+1}(s,l),
\end{align}
\item \(s,l\in \dom_n\) and  \(k\in U_{x_{n+1}}\): 
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\psi_{n}(s,t)\phi_A(t,k)\phi_A(t,k)\psi_n(t,l)\\
\overset{\eqref{phi prop3},\eqref{phi prop2}}{=}\psi_{n}(s,t)\psi_n(t,l)\overset{\eqref{induction psi2}}{=}\psi_n(s,l)=\psi_{n+1}(s,l),
\end{align*}
\item  \(s\in \dom_n\) and  \(k,l\in U_{x_{n+1}}\):
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\psi_n(s,t)\phi_A(t,k)\phi_A(k,l)\\
\overset{\eqref{phi prop2}}{=}\psi_n(s,t)\phi_A(t,l)
=\psi_{n+1}(s,l),
\end{align*}
\item \(k,l\in \dom_n\) and  \(s\in U_{x_{n+1}}\): 
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\phi_A(s,t)\psi_n(t,k)\psi_n(k,l)\\
\overset{\eqref{induction psi2}}{=}\phi_A(s,t)\psi_n(t,l)=\psi_{n+1}(s,l),
\end{align*}
\item  \(k\in \dom_n\) and  \(s,l\in U_{x_{n+1}}\):
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\phi_A(s,t)\psi_n(t,k)\psi_n(k,t)\phi_A(t,l)\\
\overset{\eqref{induction psi2}}{=}\phi_A(s,t)\psi(t,t)\phi_A(t,l)
\overset{\eqref{induction psi3},\eqref{phi prop3}}{=}\phi_A(s,t)\phi_A(t,l)\\
\overset{\eqref{phi prop2}}{=} \phi_A(s,l)=\psi_{n+1}(s,l),
\end{align*}
\item \(l\in \dom_n\) and  \(s,k\in U_{x_{n+1}}\):
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\phi_A(s,k)\phi_A(k,t)\psi_n(t,l)\\
\overset{\eqref{phi prop2}}{=}\phi_A(s,t)\psi_n(t,l)=\psi_{n+1}(s,l),
\end{align*}
\item and if \(s,k,l\in U_z\): 
\begin{align*}
\psi_{n+1}(s,k)\psi_{n+1}(k,l)=\phi_A(s,k)\phi_A(k,l)\\
\overset{\eqref{phi prop2}}{=}\phi_A(s,l)=\psi_{n+1}(s,l).
\end{align*}
\end{enumerate}

To see \(\eqref{induction psi3}_{n+1}\), i.e. that  \(\psi_{n+1}\) is 
coincides with \(\phi_A\) where both functions are defined pick 
\(x,y\in \dom_{n+1}\) such that \((xA,yA)\in\dom\overline{S})\).
Recall the definition of \(\psi_{n+1}\)

\begin{equation}\tag{\ref{def psi induction}}
  \psi_{n+1}(x,y)=\left\{\begin{matrix}
  \psi_n(x,y) \quad &\text{for }x,y\in \dom_n,\\
  \phi_A(x,y) \quad &\text{for } x,y\in U_{x_{n+1}},\\
  \psi_n(x,t)\phi_A(t,y)\quad &\text{for } x\in \dom_n, y\in U_{x_{n+1}},\\
  \phi_A(x,t)\psi_n(t,y)\quad &\text{for } y\in \dom_n, x\in U_{x_{n+1}},
  \end{matrix} \right.
\end{equation} 

Therefore if \(x,y\in\dom_{n+1}\) we may use the induction hypothesis directly
and if \(x,y\in U_{x_{n+1}}\) we also arrived a the claim we want to prove.
Excluding these cases, we are left with rows number three and four of this
definition with the restriction
\begin{enumerate}
  \item[3.] \(x\in \dom_n\backslash~ U_{x_{n+1}}, y\in U_{x_{n+1}}\backslash~ \dom_n \) and
  \item[4.] \(y\in \dom_n\backslash~ U_{x_{n+1}}, x\in U_{x_{n+1}}\backslash~ \dom_n \),
\end{enumerate}
respectively.
Because \(t\) appearing in the definition of \(\psi_{n+1}\) satisfies
\(t\in \dom_n\cap U_{x_{n+1}}\), we have in both cases \(t\in \overline{x~y}\).
By using property 4 of lemma \ref{lem properties of dom s bar} we infer 
from \((xA,yA)\in \dom\overline{S}\) that in both cases
 \((xA, t A),(tA, y A)\in \dom \overline{S}\)
also holds. Hence we may apply the induction hypothesis 
\(\eqref{induction psi3}_{n}\).

Now only uniqueness is left to show. So let \(\tilde{\psi}\) defined 
at least on\(\dom_{n+1}\times\dom_{n+1}\) fulfil 
 \begin{align}\label{uniqueness0}
  \forall (t,s)\in \dom_n\times \dom_n: \tilde{\psi}(t,s) \text{ is a lift of } S_{tA, sA}\\\label{uniqueness psi1}
\forall s,k,l\in\mathbb{R}: \tilde{\psi}(k,s)\tilde{\psi}(s,l)=\tilde{\psi}(k,l),\\\label{uniqueness psi2}
\forall (x,y)\in\dom_n: (xA, yA)\in\dom\overline{S}\Rightarrow  \tilde{\psi}(x,y)=\phi_A(x,y).
\end{align}
Now pick \(x,y \in (\dom_n\cup U_z)\). Let without loss of generality \(y>x\). 
Pick for each \(z \in [x,y]\) an open set \(U_z \subseteq \dom\overline{S}\) then 
\begin{equation}
 \bigcup_{z\in [x,y]} U_z \supseteq [x,y]
\end{equation}
is an open cover of \([x,y]\). Since \([x,y]\) is compact there is a finite selection of \(z_i\in [x,y], 1\le i\le n\in\mathbb{N}\) such that
also 
\begin{equation}
 \bigcup_{i=1}^n U_{z_i}\supseteq [x,y]
\end{equation}
is an open cover of \([x,y]\). Without loss of generality let \(z_1=x, z_n=y\). We next reduce \(\tilde{\psi}(x,y)\) to the following product
\begin{equation}
\tilde{\psi}(x,y)=\prod_{i=1}^{n=1}\tilde{\psi}(z_i,z_{i+1})=\prod_{i=1}^{n=1}\phi_A(z_i,z_{i+1}),
\end{equation}
by repeated application of equation 
\eqref{uniqueness psi1} and application of \eqref{uniqueness psi2}. 
By the very same procedure we can reduce \(\psi_{n+1}(x,y)\) to the same 
product, proving \(\psi_{n+1}(x,y)=\tilde{\psi}(x,y)\). This ends the 
induction. 

Now we have established an extension \(\psi_n\) of \(\phi_A\)
fulfilling properties \eqref{induction psi1}-\eqref{induction psi3}
and coinciding with any other function on its domain 
\(\dom_n\) that also satisfies 
these properties. The domain is of the form
\begin{equation}
\bigcup_{k=0}^n U_{x_k}
\end{equation}
with \(x_k\) such that \(\bigcup_{k=0}^l U_{x_k}\) is connected for all 
\(l\). This also yields a global unique extension of \(\phi_A\) because
we can pick points \((x_n)_{n\in\mathbb{N}}\) such that 
\(\bigcup_{k=0}^n U_{x_k}\) is connected for all \(n\) and
\begin{equation}
  \mathbb{R}= \bigcup_{n\in\mathbb{N}} U_{x_n}
\end{equation}
holds.

\end{proof}

Lemma \ref{lem: phi global} enables us to define a global lift.
\begin{Def}[global lift]\label{de: s hat}
For any \(A\in\mathcal{V}\) we define 
\begin{equation}
\hat{S}_{0,A}:=\phi_A(1,0).
\end{equation}
\end{Def}
using lemma  \ref{lem: phi global} we are now in a position
to prove theorem \ref{thm: ex s hat}.
\begin{proof}[proof of theorem \ref{thm: ex s hat}]
The operator \(\hat{S}\) fulfils the claimed differential 
equation \eqref{diff s hat} due to the global 
multiplication property 
\eqref{global phi prop2} and the differential 
equation \eqref{global phi prop4}.
Its uniqueness is inherited from the 
uniqueness of \(\phi_A\) for \(A\in\mathcal{V}\)
from lemma \ref{lem: phi global}.
\end{proof}


%\begin{rmk}
%The lift \(\hat{S}_{0,A}\) can also be calculated differently: pick \(N\in\mathbb{N}\) and a series \((\delta_k)_{k\in\mathbb{N}}\subset \mathbb{R}^+\)
% such that \(\|\mathds{1}-S_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_k A}\|<1\)  holds true for all \(k\) and \(\sum_{k=1}^{N}\delta_k=1\). 
%Then 

%\textcolor{red}{is there some kind of direct correspondence between \(\|1-S_{0,\delta_n A}\|\) and \(\|1-S_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_k A}\|\)??}
%\begin{equation}
%P^-S_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_k A}P^-
%\end{equation}
%is invertible. Now, 
%\begin{equation}\label{hat finite spacing}
%\hat{S}_{0,A}=\prod_{n=0}^{N} \overline{S}_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_kA}.
%\end{equation}
%Before proving this claim, we notice the following property of \(\overline{S}\): For any  \(A\in\mathcal{V}\) and \(\alpha, \beta, \gamma>0\)
% such that all factors exist the following identity holds
%\begin{align}
%\overline{S}_{\alpha A, \gamma A} = \overline{S}_{\alpha A, \beta A} \overline{S}_{\beta A, \gamma A}.
%\end{align}
%This property is by \eqref{gamma attri6} equivalent to 
%\begin{equation}\label{gamma equal 1}
%\Gamma_{\alpha A, \beta A, \gamma A}=1.
%\end{equation}
%This claim can be reduced to the one where \(\alpha=1\) by the following renaming scheme
%\begin{align}
%\alpha A&=: \tilde{A}\\
%\beta/\alpha &=: \tilde{\beta}\\
%\gamma/\alpha&=:\tilde{\gamma}.
%\end{align}
%In fact, the claim holds, as
%the following calculation shows:
%\begin{align}
%\ln &\Gamma_{A,\beta A, \gamma A} = \int_1^\beta d \beta' \partial_{\beta'}\ln \Gamma_{A,\beta' A, \gamma A} 
%+ \overbrace{\ln \Gamma_{A,A,\gamma A}}^{\overset{\eqref{gamma attri4}}{=}0}\\
%&= \int_1^\beta d\beta' \left(\int_1^\gamma d\gamma' \partial_{\gamma'}\partial_{\beta'} \ln \Gamma_{A,\beta' A, \gamma' A} 
%+ \partial_{\beta'} \overbrace{\ln \Gamma_{A,\beta' A, A}}^{\overset{\eqref{gamma attri4}}{=}0} \right)\\
%&=\int_1^\beta d\beta' \int_1^\gamma d\gamma' c_A((\beta'-1) A, (\gamma'-1) A)\\
%&=\int_1^\beta d\beta' \int_1^\gamma d\gamma'  (\beta'-1) (\gamma'-1) \overbrace{c_A( A,  A) }^{\overset{\eqref{gamma attri3},\eqref{gamma attri8}}{=}0}=0,
%\end{align}
%where we have used various properties of lemma \ref{gamma attri}.
%
%\textcolor{blue}{generalisation:}
%claim: for all \(A,B\in \mathcal{A}\) and all \(\alpha,\beta\in\mathbb{R}\), \(|\alpha|,|\beta|\) small enough, such that the expression appearing is well defined
%\begin{equation}
%\Gamma_{A,A+\alpha B, A+ \beta B} =1.
%\end{equation}
%proof:
%\begin{align}
%\ln \Gamma_{A,A+\alpha B, A+ \beta B} = \overbrace{\ln \Gamma_{A,A+\alpha B, A}}^{=0}+ \int_0^{\beta} d\beta' \partial_{\beta'} \ln \Gamma_{A,A+\alpha B, A+ \beta' B}\\
%=\int_0^{\beta} d\beta' \partial_{\beta'} \left(\overbrace{\ln \Gamma_{A,A, A+ \beta' B}}^{=0}+ \int_0^{\alpha}d\alpha' \partial_{\alpha'} \ln \Gamma_{A,A+\alpha' B, A+ \beta' B}\right)\\
%=\int_0^{\beta} d\beta'  \int_0^{\alpha}d\alpha' \partial_{\beta'} \partial_{\alpha'} \ln \Gamma_{A,A+\alpha' B, A+ \beta' B}\\
%=\int_0^{\beta} d\beta'  \int_0^{\alpha}d\alpha' c_A(\alpha' B, \beta' B) 
%=\int_0^{\beta} d\beta'  \int_0^{\alpha}d\alpha' \alpha' \beta' \overbrace{ c_A( B,  B)}^{=0}.
%\end{align}


%Because of \eqref{gamma equal 1} we see that \eqref{hat finite spacing} is actually independent of the choice of sequence \((\delta_k)_{k}\).
%The right side of equation \eqref{hat finite spacing} satisfies the initial condition of the ordinary differential equation, so we only need to check the differential equation itself.
%Next we reformulate the ordinary differential equation \eqref{diff s hat}, pick \(B=t A\) then we have
%\begin{equation}
%0=\partial_B \frac{\hat{S}_{0,A+B}}{\hat{S}_{0,A}\overline{S}_{A,A+B}}
%=\partial_\varepsilon \frac{\hat{S}_{0,A(1+\varepsilon t)}}{\hat{S}_{0,A}\overline{S}_{A,A(1+\varepsilon t)}}
%=t\partial_\varepsilon \frac{\hat{S}_{0,A(1+\varepsilon)}}{\hat{S}_{0,A}\overline{S}_{A,A(1+\varepsilon)}}
%\end{equation}


%What is more, we can pick \((\delta_k)_k\) such that \(\sum_{k=1}^N \delta_k=1\) and \(\delta_{N+1}=\varepsilon\) then we have

%\begin{align}
%\hat{S}_{0,A(1+\varepsilon)}=\prod_{n=0}^{N+1} \overline{S}_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_kA}
%=\prod_{n=0}^{N} \overline{S}_{\sum_{k=1}^{n-1}\delta_k A,\sum_{k=1}^{n}\delta_kA}~ \overline{S}_{A,A(1+\varepsilon)}\\
%=\hat{S}_{0,A}\overline{S}_{A,A+B},
%\end{align}

%or in other words

%\begin{equation}
%\frac{\hat{S}_{0,A+B}}{\hat{S}_{0,A}\overline{S}_{A,A+B}}=1.
%\end{equation}
%If \(A=0\) holds, we see directly that 

%\begin{equation}
%\frac{\hat{S}_{0,B}}{\hat{S}_{0,0}\overline{S}_{0,B}}= 1,
%\end{equation}

%so in both cases the ordinary differential equation is satisfied. 
%\end{rmk}

\begin{Def}[relative phase]
Let \((A,B) \in\dom\overline{S}\), we define \(z(A,B)\in S^1\) by
\begin{equation}\label{def z}
z(A,B):=\frac{\hat{S}_{0,B}}{\hat{S}_{0,A}\overline{S}_{A,B}}.
\end{equation}
Please note that for such \(A,B\) the lift \(\bar{S}_{A,B}\) 
is well defined. This means that the product in the 
denominator is a lift of \(S_{0,B}\)
and according to definition \ref{de: s hat} the 
ratio is well defined. 
\end{Def}

\begin{Remark}
The global function \(z\) defined here is an extension 
of the funtion \(z\) appearing locally 
in the 
the proof of lemma \ref{lem phi local},
cf. formula \eqref{def local z}.

Please note that \(z\) is smooth
when restricted to  \(\mathcal{W}^2\cap \dom\overline{S}\) 
for any finite dimensional subspace
 \(\mathcal{W}\subseteq \mathcal{V}\).
\end{Remark}


\begin{Lemma}[properties of the relative phase]
For all \\
\((A,F),(F,G),(G,A)\in\dom\overline{S}\), as well as 
or all \(H,K\in \mathcal{V}\), we have
\begin{align}\label{z antisym}
z(A,F)&=z(F,A)^{-1}\\\label{z gamma}
z(F,A)z(A,G)z(G,F)&=\Gamma_{F,A,G}\\\label{z c}
\partial_{H}\partial_{K}\ln  z(A+ H,A+ K)&=c_A(H,K).
\end{align}
\end{Lemma}
\begin{proof}
Pick \(A,F,G\in\mathcal{V}\) as in the lemma. We start off by analysing
\begin{align}
&\hat{S}_{0,F}\overline{S}_{F,G}\overset{\eqref{def z}}{=}z(A,F)\hat{S}_{0,A}\overline{S}_{A,F}\overline{S}_{F,G}\\\label{phase comparison}
&\overset{\eqref{gamma attri6}}{=}z(A,F) \Gamma_{A,F,G}^{-1} \hat{S}_{0,A} \overline{S}_{A,G}.
\end{align}
Exchanging  \(A\) and \(F\) in this equation yields
\begin{equation}
\hat{S}_{0,A}\overline{S}_{A,G}=z(F,A) \Gamma_{F,A,G}^{-1} \hat{S}_{0,F} \overline{S}_{F,G}.
\end{equation}
This is equivalent to
\begin{equation}
\hat{S}_{0,F} \overline{S}_{F,G}=z(F,A)^{-1} \Gamma_{F,A,G} \hat{S}_{0,A}\overline{S}_{A,G}~.
\end{equation}
Comparing the last equation with 
formula \eqref{phase comparison} 
and taking the permutation properties 
 \eqref{gamma attri3} of \(\Gamma\) into 
 account this implies that 
\begin{equation}
z(A,F)=z(F,A)^{-1}
\end{equation}
holds true. Equation \eqref{phase comparison} solved for \(\hat{S}_{0,A}\overline{S}_{A,G}\) also gives us

\begin{align}
\hat{S}_{0,G}\overset{\eqref{def z}}{=}z(A,G)\hat{S}_{0,A}\overline{S}_{A,G}\\
\overset{\eqref{phase comparison}}{=}z(A,G)z(A,F)^{-1}\Gamma_{A,F,G}\hat{S}_{0,F}\overline{S}_{F,G}.
\end{align}
The latter equation compared with 
\begin{equation}
\hat{S}_{0,G}\overset{\eqref{def z}}{=}z(F,G)\hat{S}_{0,F}\overline{S}_{F,G},
\end{equation}
yields  a direct connection between \(\Gamma\) and \(z\):
\begin{equation}
\frac{z(A,G)}{z(A,F)}\Gamma_{A,F,G}=z(F,G),
\end{equation}
which we rewrite using the antisymmetry 
\eqref{z antisym} of \(z\)  as
\begin{equation}
\Gamma_{A,F,G}=z(F,G)z(A,F)z(G,A).
\end{equation}
Finally, in this equation, we substitute 
\(F=A+\varepsilon_1 H\) as well as  
\(G=A+\varepsilon_2 K\), where 
\(\varepsilon_1,\varepsilon_2\) is small enough so that 
\(z\) and \(\Gamma\) are still well defined. Then we 
take the second logarithmic derivative to find
\begin{align}\notag
 \partial_{\varepsilon_1}\partial_{\varepsilon_2}\ln  z(A+\varepsilon_1 H,A+\varepsilon_2 K)=\partial_{\varepsilon_1}\partial_{\varepsilon_2}\ln\Gamma_{A,A+\varepsilon_1 H,A+\varepsilon_2 K}\\
 \overset{\eqref{gamma attri8}}{=}c_A(H,K). 
\end{align}

\end{proof}

So we find that \(c_A\) is the second mixed logarithmic 
derivative of \(z\). In the following we will 
characterise \(z\) more thoroughly by \(c\) and \(c^+\).
\begin{Def}[\(p\)-forms of four potentials, phase integral]
For \(p\in\mathbb{N}\), we introduce the set \(\Omega^p\) 
of \(p\)-forms 
to consist of all maps 
\(\omega: \mathcal{V}\times \mathcal{V}^{p}\rightarrow \mathbb{C}\)
such that \(\omega\) is linear and antisymmetric in its 
\(p\) last arguments and smooth in its first argument
when restricted to any finite
dimensional subspace of \(\mathcal{V}\).

Additionally, we define the \(1\)-form 
\(\chi\in \Omega^1(\mathcal{V})\) by
\begin{equation}\label{de chi}
\chi_A(B):=\partial_B\ln z(A,A+B)
\end{equation}
for all \(A,B\in\mathcal{V}\).
Furthermore, for \(p\in\mathbb{N}\) and any differential 
form \(\omega\in \Omega^p(\mathcal{V})\), 
we define its exterior derivative, 
\(d \omega\in\Omega^{p+1}(\mathcal{V})\) by
\begin{equation}
(d\omega)_A(B_1,\dots, B_{p+1}):=\sum_{k=1}^{p+1} (-1)^{k+1} \partial_{B_k}\omega_{A+B_k}(B_1,\dots , \cancel{B_k},\dots, B_{p+1}),
\end{equation}
for \(A,B_1,\dots, B_{p+1}\in\mathcal{V}\), where 
the notation \(\cancel{B_k}\) denotes that \(B_k\) is  
dropped as an argument.

\end{Def}

\begin{Lemma}[connection between \(c\) and the relative phase]\label{connection between c and the relative phase}
The differential form \(\chi\) fulfils 
\begin{equation}
(d\chi)_A(F,G)=2 c_A(F,G)
\end{equation}
for all \(A,F,G\in\mathcal{V}\).
\end{Lemma}
\begin{proof}
Pick \(A,F,G\in \mathcal{V}\), we calculate
\begin{align}\nonumber
&(d\chi)_A(F,G)=\partial_F\partial_G \ln z(A+F,A+F+G)\\
&\hspace{3cm}-\partial_F \partial_G \ln z(A+G,A+F+G)\\
&=\partial_F\partial_G (\ln  z(A,A+F+G)+\ln z(A+F,A+G))\\
 &\hspace{1cm} - \partial_F\partial_G(  \ln z(A,A+F+G)+\ln z(A+G,A+F))\\
&\overset{\eqref{z antisym}}{=} 2 \partial_F\partial_G \ln z(A+F,A+G)\overset{\eqref{z c}}{=}2 c_A(F,G).
\end{align}
\end{proof}

Now since \(d c=0\), we might use Poincaré's lemma as a method independent of \(z\) to construct a differential form \(\omega\) such that \(d\omega=c\). 
In order to execute this plan, we first need to prove Poincaré's lemma for our setting:

\begin{Lemma}[Poincaré]\label{lem poincare}
Let \(\omega\in \Omega^p(\mathcal{V})\) for \(p\in\mathbb{R}\) be closed, i.e. \(d \omega =0\). Then \(\omega\) is also exact, more precisely we have
\begin{equation}
\omega=d \int_{0}^1 \iota^*_t i_X f^* \omega dt,
\end{equation}
where \(X\), \(\iota_t\) for \(t\in\mathbb{R}\) and \(f\) are given by
 \begin{align}
 &X: \mathbb{R}\times\mathcal{V}\rightarrow \mathbb{R}\times\mathcal{V},\\
 &\hspace{2cm} (t,B)\mapsto (1,0) \\
&\forall t \in \mathbb{R}: \iota_t: \mathcal{V}\rightarrow \mathbb{R}\times\mathcal{V},\\
&\hspace{2cm} B\mapsto (t,B)\\
&f:\mathbb{R}\times \mathcal{V}\mapsto \mathcal{V},\\
&\hspace{2cm} (t,B) \mapsto t B\\
 &\forall t \in \mathbb{R}: f_t:=f(t,\cdot).
 \end{align}
\end{Lemma}
\begin{proof}
Pick some \(\omega \in \Omega^p(\mathcal{V})\).
We will first show the more general formula 
\begin{equation}\label{poincare more general}
f^*_b\omega-f^*_a \omega=d \int_{a}^b \iota_t^* i_X f^* \omega ~dt+ \int_{a}^b \iota_t^* i_X f^* d \omega dt.
\end{equation}
The lemma follows then by \(b=1, a= 0\), \(f^*_1\omega=\omega, f^*_0 \omega=0\) and \(d \omega=0\) for a closed \(\omega\). 
We begin by rewriting the right hand side of \eqref{poincare more general}:
\begin{align}\nonumber
d \int_{a}^b \iota_t^* i_X f^* \omega ~dt+ \int_{a}^b \iota_t^* i_X f^* d \omega dt\\\label{poincare 1 manipulation}
=\int_a^b (d\iota_t^* i_X f^* \omega+ \iota_t^* i_X f^* d \omega )dt.
\end{align}
Next we look at both of these terms separately. Let therefore \(p\in \mathbb{N}\), \(t, s_k\in \mathbb{R}\) and \(A,B_k\in \mathcal{V}\) for each \(p+1\ge k\in\mathbb{N}\).
First, we calculate \(d \iota^*_t i_X f^* \omega\):
\begin{align}
&(f^*\omega)_{(t,A)}((s_1,B_1),\dots, (s_p,B_p))\\\nonumber
&\hspace{3cm}=\omega_{tA}(s_1A+tB_1,\dots, s_p A+t B_p)\\[0.3cm]
&\Rightarrow (i_X f^* \omega)_{(t,A)}((s_1,B_1),\dots, (s_{p-1},B_{p-1}))\\\nonumber
&\hspace{3cm}=\omega_{tA}(A,s_1A+tB_1,\dots, s_{p-1}A + t B_{p-1}\\[0.3cm]
&\Rightarrow (\iota^*_t i_X f^* \omega)_{A}(B_1,\dots, B_{p-1})= t^{p-1} \omega_{t A}(A,B_1,\dots, B_{p-1})\\[0.3cm]\notag
&\Rightarrow (d\iota^*_t i_X f^* \omega)_{A}(B_1,\dots, B_{p}) \\
&\quad=\partial_\varepsilon |_{\varepsilon=0} \sum_{k=1}^p (-1)^{k+1} t^{p-1} \omega_{t A + \varepsilon t B_k}(A,B_1,\dots, \cancel{B_k},\dots, B_p)\\
&\quad+ \partial_\varepsilon|_{\varepsilon=0} \sum_{k=1}^p (-1)^{k+1} t^{p-1} \omega_{tA}(A+\varepsilon B_k,B_1,\dots, \cancel{B_k},\dots, B_p)\\\notag
&=\partial_{\varepsilon}|_{\varepsilon=0}\sum_{k=1}^p t^p (-1)^{k+1} \omega_{tA+\varepsilon B_k}(A,B_1,\dots, \cancel{B_k},\dots, B_p)\\\label{li derivative 1}
&\hspace{6cm}+p t^{p-1}\omega_{tA}(B_1,\dots, B_p).
\end{align}


Now, we calculate \(\iota^*_t i_X f^* d \omega\):
\begin{align}\notag
&(d\omega)_A(B_1,\cdots, B_{p+1})\\
&\hspace{2cm}=\partial_\varepsilon |_{\varepsilon=0} \sum_{k=1}^{p+1} (-1)^{k+1} \omega_{A+\varepsilon B_k}(B_1,\dots , \cancel{B_k}, \dots, B_{p+1})\\[0.3cm]
&(f^* d \omega){(t,A)}((s_1,B_1),\dots , (s_{p+1},B_{p+1}))\\\notag
&= (d\omega)_{tA}(s_1A + t B_1, \dots, s_{p+1}A+t B_{p+1})\\
&=\partial_{\varepsilon}|_{\varepsilon =0} \sum_{k=1}^{p+1}(-1)^{k+1}\\\notag
&\quad \times\omega_{tA + \varepsilon(s_kA + t B_k)}(s_1A+tB_1, \dots,  \cancel{s_k A + t B_k},\dots , s_p A  + t B_p )\\[0.4cm]
&(i_X f^* d \omega)_{(t,A)}((s_1,B_1),\dots , (s_p, B_p))\\\notag
&\quad= \partial_{\varepsilon} |_{\varepsilon =0} \omega_{(t+\varepsilon)A}(s_1A+tB_1, \dots, s_pA+t B_p)\\\notag
&+\partial_{\varepsilon}|_{\varepsilon=0} \sum_{k=1}^p (-1)^k\\\notag
&\times\omega_{tA + \varepsilon(s_k A + t B_k)} (A,s_1A+t B_1, \dots, \cancel{s_k A + t B_k},\dots, s_p A + t B_p)\\
&= t^p \partial_{\varepsilon}|_{\varepsilon=0}\omega_{(t+\varepsilon)A }(B_1,\dots, ,\cancel{B_k},\dots, B_p))\\
&\hspace{2cm}+ \sum_{k=1}^p s_k t^{p-1} (-1)^{k+1} \partial_{\varepsilon}|_{\varepsilon=0}\omega_{(t+\varepsilon)A}(A,B_1,\dots, B_p) \\
&+\partial_{\varepsilon}|_{\varepsilon=0}\sum_{k=1}^p(-1)^k t^{p-1}(\omega_{(t+s_k\varepsilon)A}(A,B_1,\dots, \cancel{B_k},\dots, B_p) \\
&\hspace{2cm} + \omega_{tA + \varepsilon t B_k}(A,B_1, \dots, \cancel{B_k},\dots, B_p))\\
&=t^p\partial_{\varepsilon}|_{\varepsilon=0} \Big(\omega_{(t+\varepsilon)A}(B_1,\dots, B_p)\\\notag
&\hspace{2cm} +\sum_{k=1}^p (-1)^k \omega_{tA+\varepsilon B_k}(A,B_1,\dots, \cancel{B_k},\dots, B_p)\Big)\\\label{li derivative 2}
&(\iota_t^* i_X f^* d \omega)_{A}(B_1,\dots ,  B_p)=t^p\partial_{\varepsilon}|_{\varepsilon=0} \Big(\omega_{(t+\varepsilon)A}(B_1,\dots, B_p)\\\notag
&\hspace{2cm}+\sum_{k=1}^p (-1)^k \omega_{tA+\varepsilon B_k}(A,B_1,\dots, \cancel{B_k},\dots, B_p)\Big)
\end{align}

Adding \eqref{li derivative 1} and \eqref{li derivative 2} we find for \eqref{poincare 1 manipulation}:

\begin{align}
\int_a^b (d\iota_t^* i_X f^* \omega+ \iota_t^* i_X f^* d \omega )dt=\\
\int_a^b  \Big( t^p\partial_{\varepsilon}|_{\varepsilon=0} \omega_{(t+\varepsilon)A}(B_1,\dots, B_p)
+p t^{p-1}\omega_{tA}(B_1,\dots, B_p)\Big) dt\\
=\int_a^b  \frac{d}{dt} (t^p \omega_{tA}(B_1,\dots, B_p))dt =\int_a^b  \frac{d}{dt} (f^*_t \omega)_{A}(B_1,\dots, B_p)dt\\
=(f^*_b\omega)_A(B_1,\dots,B_p)-(f^*_a\omega)_A(B_1,\dots,B_p).
\end{align}

\end{proof}

\begin{Def}[integral of a closed p form]
For a closed exterior form \(\omega\in\Omega^{p}(\mathcal{V})\) we define the form \(\prod [\omega]\)
\begin{equation}
\prod\![\omega]:=\int_{0}^1 \iota^*_t i_X f^* \omega dt.
\end{equation}
For \(A,B_1,\dots , B_{p-1}\in\mathcal{V}\) it takes the form 
\begin{equation}
\prod\![\omega]_A(B_1,\dots, B_p)=\int_0^1 t^{p-1} \omega_{tA}(A,B_1,\dots, B_{p-1})dt.
\end{equation}
By lemma \ref{lem poincare} we know \(d\prod [\omega]=\omega\) if \(d\omega=0\).
\end{Def}

Now we found two one forms each produces \(c\) when the exterior derivative is taken. The next lemma informs us about their relationship.

\begin{Lemma}[inversion of lemma \ref{connection between c and the relative phase}]
The following equality holds
\begin{equation}
\chi=2 \prod\![c].
\end{equation}
\end{Lemma}
\begin{proof}
We have \(d(\chi-2 \prod\![c])=0\) so by lemma \ref{lem poincare} we know that there is \(v:\mathcal{V}\rightarrow \mathbb{R}\) such that
\begin{equation}
dv=\chi-2 \prod\![c]
\end{equation}
holds. Now \eqref{diff s hat} translates into the following ODE for \(z\):
\begin{equation}
\partial_B \ln z(0,B)=0, \quad \partial_\varepsilon \ln z(A,(1+\varepsilon)A)|_{\varepsilon =0}=0
\end{equation}
for all \(A,B\in\mathcal{V}\). This means that
\begin{equation}
\chi_0(B)=0=\prod\![c]_0(B), \quad \chi_{A,A}=0=\prod\![c]_A(A)
\end{equation}
hold. This implies
\begin{equation}
\partial_\varepsilon v_{\varepsilon A}=0, \quad \partial_\varepsilon v_{A+\varepsilon A}=0,
\end{equation}
which means that \(v\) is constant.
\end{proof}


From this point on we will assume the existence of  a function \(c^+\) fulfilling \eqref{c+ 1},\eqref{c+ 2} and \eqref{c+ 3}.
Recall equation \eqref{c+ 2}: 
\begin{equation}
\forall A,F,G,H: \partial_H c_{A+H}^+(F,G)=\partial_G c^+_{A+G}(F,H).
\end{equation}

For a fixed \(F\in\mathcal{V}\), this condition can be read as \(d( c^+_{\cdot} (F,\cdot))=0\). As a consequence we can apply lemma \ref{lem poincare} to define a one form.

\begin{Def}[integral of the causal splitting]
For any \(F\in\mathcal{V}\), we define

\begin{equation}
\beta_A(F):=2 \prod\![c^+_{\cdot}(F,\cdot)]_A.
\end{equation}
\end{Def}

\begin{Lemma}[relation between the integral of the causal splitting and the phase integral]
The following two equations hold:
\begin{align}\label{beta c}
&d \beta=-2 c\\
&d(\beta +\chi)=0.
\end{align}
\end{Lemma}
\begin{proof}
We start with the exterior derivative of \(\beta\). Pick \(A,F,G\in\mathcal{V}\):
\begin{align}
d\beta_A(F,G)=\partial_F \beta_{A+F}(G)-\partial_G \beta_{A+G}(F)\\
=d\Big(\prod\![c^+_\cdot(G,\cdot)]\Big)_A(F)-d\Big(\prod\![c^+_\cdot(F,\cdot)]\Big)_A(G)\\
=2 c^+_A(G,F)-2 c_A^+(F,G)\overset{\eqref{c+ 1}}{=}-2 c_A(F,G).
\end{align}
This proves the first equality. The second equality follows directly by \(d \chi=2 c\).
\end{proof}

\begin{Def}[corrected lift]
Since \(\beta+\chi\) is closed, we may use lem \ref{lem poincare} again to define the phase
\begin{equation}\label{def alpha}
\alpha:=\prod\![\beta+\chi].
\end{equation}
Furthermore, for all \(A,B\in\mathcal{V}\) we define the corrected second quantised scattering operator 
\begin{align}
&\tilde{S}_{0,A}:=e^{-\alpha_A} \hat{S}_{0,A}\\
&\tilde{S}_{A,B}:=\tilde{S}^{-1}_{0,A}\tilde{S}_{0,B}.
\end{align}
\end{Def}

\begin{Corollary}[group structure of the corrected lift]
We have \(\tilde{S}_{A,B} \tilde{S}_{B,C}=\tilde{S}_{A,C}\) for all \(A,B,C\in\mathcal{V}\).
\end{Corollary}

\begin{Thm}[causality of the corrected lift]
The corrected second quantised scattering operator fulfils the following causality condition for all \(A,F,G\in \mathcal{V}\) such that \(F\prec G\):
\begin{equation}
\tilde{S}_{A,A+F}=\tilde{S}_{A+G,A+G+F}.
\end{equation}
\end{Thm}
\begin{proof}
Let \(A,F,G\in\mathcal{V}\) such that \(F\prec G\) We note that for the first quantised scattering operator we have
\begin{equation}
S_{A+G,A+G+F}=S_{A,A+F},
\end{equation}
so by definition of \(\overline{S}\) we also have
\begin{equation}\label{s bar causal}
\overline{S}_{A+G,A+G+F}=\overline{S}_{A,A+F}.
\end{equation}
So for any lift this equality is true up to a phase, meaning that 

\begin{equation}\label{f causal}
f(A,F,G):=\frac{\tilde{S}_{A+G,A+G+F}}{\tilde{S}_{A,A+F}}
\end{equation}
is well defined. We see immediately
\begin{equation}\label{vanish at axis}
f(A,0,G)=1=F(A,F,0).
\end{equation}

Pick \(F_1,F_2\prec G_1,G_2\). We abbreviate \(F=F_1+F_2, G=G_1+G_2\) and we calculate
\begin{align}
&f(A,F,G)=\frac{\tilde{S}_{A+G,A+F+G}}{\tilde{S}_{A,A+F}}\\
&=\frac{\tilde{S}_{A+G,A+F+G}}{\tilde{S}_{A+G_1,A+G_1+F}}\frac{\tilde{S}_{A+G_1,A+G_1+F}}{\tilde{S}_{A,A+F}}\\
&=\frac{\tilde{S}_{A+G,A+G+F_1} \tilde{S}_{A+G+F_1,A+F+G}}{\tilde{S}_{ A+G_1,A+F_1+G_1} \tilde{S}_{ A+G_1+F_1,A+G_1+F}}  \frac{\tilde{S}_{A+G_1,A+G_1+F}}{\tilde{S}_{A,A+F}}\\
&=\frac{\tilde{S}_{A+G,A+G+F_1}}{\tilde{S}_{A+G_1,A+F_1+G_1}} \frac{\tilde{S}_{A+G+F_1,A+F+G}}{\tilde{S}_{A+G_1+F_1,A+G_1+F}}  f(A,G_1,F_1+F_2)\\\notag
&=f(A+G_1,F_1,G_2)f(A+G_1+F_1,G_2,F_2)\\
&\hspace{2cm} \times f(A,G_1,F_1+F_2).
\end{align}
Taking the logarithm and differentiating we find:
\begin{equation}\label{shift to small G,F}
\partial_{F_2}\partial_{G_2}\ln f(A,F_1+F_2,G_1+G_2)=\partial_{F_2}\partial_{G_2}\ln f(A+F_1+G_1,F_2,G_2).
\end{equation}
Next we pick \(F_2=\alpha_1 F_1\) and \(G_2=\alpha_2 G_1\) for \(\alpha_1,\alpha_2\in\mathbb{R}^+\) small enough so that

 \begin{align}
 \|1-S_{A+F+G,A+F_1+G_1}\|<1\\
 \|1-S_{A+F+G,A+F_1+G}\|<1\\
 \|1-S_{A+F+G,A+F+G_1}\|<1
 \end{align} 
 hold. We abbreviate \(A'=A+G_1+F_1\), use \eqref{def z} and compute
 
 \begin{align}\notag
 &f(A',F_2,G_2)=\\\notag
 &\frac{e^{-\alpha_{A'+F_2+G_2}+\alpha_{A'+G_2}}z(A',A'+F_2+G_2)z^{-1}(A',A'+G_2)}{e^{-\alpha_{A'+F_2}+\alpha_{A'}}z(A',A'+F_2)z^{-1}(A',A')} \\
&\hspace{3cm}\times \frac{\overline{S}_{A'+G_2,A'}\overline{S}_{A',A'+F_2+G_2}}{\overline{S}_{A',A'}\overline{S}_{A',A'+F_2}}.
 \end{align}

The second factor in this product can be simplified significantly:
\begin{align}
 \frac{\overline{S}_{A'+G_2,A'}\overline{S}_{A',A'+F_2+G_2}}{\overline{S}_{A',A'}\overline{S}_{A',A'+F_2}}
 = \frac{\overline{S}_{A'+G_2,A'}\overline{S}_{A',A'+F_2+G_2}}{\overline{S}_{A',A'+F_2}}\\
 \overset{\eqref{gamma attri6}}{=}\Gamma^{-1}_{A'+G_2,A',A'+F_2+G_2}\frac{\overline{S}_{A'+G_2,A'+F_2+G_2}}{\overline{S}_{A',A'+F_2}}\\
 \overset{\eqref{s bar causal}}{=}\Gamma_{A',A'+G_2,A'+F_2+G_2}\\\notag
\overset{ \eqref{z gamma}}{=}z(A',A'+G_2)z(A'+G_2,A'+G_2+F_2)\\
 \times z(A'+F_2+G_2,A').
\end{align}
So in total we find

\begin{align}\notag
f(A',F_2,G_2)=\\
\frac{e^{-\alpha_{A'+F_2+G_2}+\alpha_{A'+G_2}}z(A',A'+F_2+G_2)z^{-1}(A',A'+G_2)}{e^{-\alpha_{A'+F_2}+\alpha_{A'}}z(A',A'+F_2)z^{-1}(A',A')}  \\\notag
\times z(A',A'+G_2)z(A'+G_2,A'+G_2+F_2)\\\notag
\times z(A'+F_2+G_2,A')\\
=\exp(-\alpha_{A'+F_2+G_2}+\alpha_{A'+G_2}+\alpha_{A'+F_2}-\alpha_{A'})\\
\times z(A'+G_2,A'+G_2+F_2)z^{-1}(A',A'+F_2).
\end{align}
Most of the factors do not depend on \(F_2\) and \(G_2\), so taking the mixed logarithmic derivative things simplify:
\begin{align}\notag
\partial_{G_2}\partial_{F_2} \ln f(A',F_2,G_2)= \\
\partial_{G_2}\partial_{F_2} ( -\alpha_{A'+F_2+G_2} + \ln z(A'+G_2,A'+G_2+F_2))\\
\overset{\eqref{def alpha}, \eqref{de chi}}{=}  \partial_{G_2} (-\beta_{A'+G_2}(F_2)-\chi_{A'+G_2}(F_2) + \chi_{A'+G_2}(F_2))\\
\overset{\eqref{beta c}}{=}2 c^+_{A'}(F_2,G_2)\overset{F_2\prec G_2, \eqref{c+ 3}}{=}0.
\end{align}
So by \eqref{shift to small G,F} we also have
\begin{align}
\partial_{F_2}\partial_{G_2}\ln f(A,F_1+F_2,G_1+G_2)=0\\
=\partial_{\alpha_1}\partial_{\alpha_2}\ln f(A,F_1(1+\alpha_1),G_1(1+\alpha_2))
\end{align}
But then we can integrate and obtain
\begin{align}
&0=\int_{-1}^0d \alpha_1 \int_{-1}^0d \alpha_2  \partial_{\alpha_1}\partial_{\alpha_2}\ln f(A,F_1(1+\alpha_1),G_1(1+\alpha_2))\\
&=\ln f(A,F_1,G_1)-\ln f(A,0,G_1)-\ln f(A,F_1,0)\\\notag 
&\hspace{3cm}+ \ln f(A,0,0)\\
&\overset{\eqref{vanish at axis}}{=}\ln f(A,F_1,G_1).
\end{align}
remembering equation \eqref{f causal}, the definition of \(f\),  this ends our proof.
\end{proof}

Using \(\tilde{S}\) we introduce the current associated to it.

%\begin{Def}
%Let \(A,F\in\mathcal{V}\), define
%\begin{equation}
%j_A(F):=i\partial_F \left\langle\Omega, \tilde{S}_{A,A+F}\Omega\right\rangle = i \partial_F \ln \left\langle\Omega, \tilde{S}_{A,A+F}\Omega\right\rangle.
%\end{equation}
%\end{Def}

\begin{Thm}[evaluation of the current of the corrected lift]
For general \(A,F\in\mathcal{V}\) we have
\begin{equation}
j_A(F)=-i\beta_A(F).
\end{equation}
So in particular for \(G\in\mathcal{V}\)
\begin{equation}
\partial_G j_{A+G}(F)=-2i c^+_A(F,G).
\end{equation}
holds.
\end{Thm}
\begin{proof}
Pick \(A,F\in\mathcal{V}\) as in the theorem. We calculate
\begin{align}
i\partial_F \ln \left\langle\Omega, \tilde{S}_{A,A+F}\Omega\right\rangle\\
=i\partial_F\left( -\alpha_{A+F}-\alpha_A + \ln \left\langle\Omega, \hat{S}_{0,A}^{-1} \hat{S}_{0,A+F}\Omega\right\rangle\right)\\
=i\partial_F\left( -\alpha_{A+F}+\ln z(A,A+F) + \ln \left\langle\Omega, \overline{S}_{A,A+F}\Omega\right\rangle\right)
\end{align}
The last summand vanishes, as can be seen by the following calculation
\begin{align}
\partial_{F} \ln \left\langle \Omega, \overline{S}_{A,A+F}\Omega\right\rangle\\
=i\partial_F\ln \det_{\mathcal{H}^-} (P^-S_{A,A+F}P^-\AG(P^-S_{A,A+F}P^-)^{-1})\\
=i\partial_F\ln \det_{\mathcal{H}^-} |P^-S_{A,A+F}P^-|\\
=\frac{i}{2} \partial_F \ln \det_{\mathcal{H}^-} ((P^- S_{A,A+F}P^-)^*P^- S_{A,A+F}P^-)\\
=\frac{i}{2} \partial_F \det (P^- S_{A+F,A}P^-S_{A,A+F}P^-)\\
=\frac{i}{2}\tr(\partial_F P^-S_{A+F,A}P^-S_{A,A+F}P^-)\\
=\frac{i}{2}\tr(\partial_F P^-S_{A,A+F}P^-+\partial_F P^-S_{A+F,A}P^-)=0\end{align}
where we made use of \eqref{diff det}.
So we are left with
\begin{align}
j_A(F)=i\partial_F (-\alpha_{A+F}+\ln z(A,A+F))\\
=i(-\beta_A(F)-\chi_A(F)+\chi_A(F))=-i\beta_A(F).
\end{align}

Finally by taking the derivative with respect to \(G\in\mathcal{V}\) and using the definition of \(\beta\) we find
\begin{equation}
\partial_G j_{A+G}(F)=-2i c_A^+(F,G).
\end{equation}


\end{proof}



\section{Simple Formula for the Scattering Operator}

\subsection{Defining One-Particle Scattering-Matrix}\label{sec:one-particle}


%The goal of this and the next section is to introduce some results, which are
%known to the community and form the basis of my work. 
In order to introduce the one-particle dynamics I introduce Diracs equation \eqref{dirac} and reformulate it in integral form in equation \eqref{dirac_integral}. By iterating this equation we will naturally be led to the informal series expansion of the scattering operator equation \eqref{DefU}, whose convergence is discussed in the next section. 
%\Dirk{ordne es anders: wir wollen $S$, dazu Zeitentwicklung $U$, dazu Dirac
%Gleichung, Integralversion, formale Iteration, Konvergenz}
%\Markus{So? Oder wolltest du, dass ich auch die Mathematik umordne?} Gut so.

Throughout this thesis I will consider four-potentials $A, F$ or \(G\) to be smooth functions
in \(C_{c}^\infty(\mathbb{R}^4)\otimes \mathbb{C}^4\), where the index \(c\)
denotes that the elements have compact support. The Dirac
equation for a wave function \(\phi \in L^2(\mathbb{R}^3)\otimes \mathbb{C}^4\)
is
\begin{equation}\label{dirac}
0= (i\slashed{\partial}-e\slashed{A}-m \id) \phi,
\end{equation}
where \(m\) is the mass of the electron, \(\id: \mathbb{C}^4\rightarrow \mathbb{C}^4\) is the identity  and crossed out letters mean that their four-index is contracted with Dirac matrices
\begin{equation}
\slashed{A}:= A_\alpha \gamma^\alpha,
\end{equation}
where Einstein's summation convention is used. These matrices fulfil the anti-commutation relation
\begin{equation}
\forall \alpha, \beta \in \{0,1,2,3\}:\{\gamma^\alpha, \gamma^\beta\}:= \gamma^\alpha \gamma^\beta+ \gamma^\beta \gamma^\alpha= g^{\alpha \beta},
\end{equation}
where \(g\) is the Minkowski metric. I work with the \(+---\) metric signature and the Dirac representation of this algebra. Squared four dimensional objects always refer to the Minkowski square, meaning for all \(a\in \mathbb{C}^4\), \(a^2:= a^{\alpha} a_{\alpha}\). 

In order to define Lorentz invariant measures for four dimensional integrals I employ the same notation as in \cite{ivp1}. The standard volume form over \(\mathbb{R}^4\) is denoted by \(\mathrm{d}^4 x= \mathrm{d}x^0 \mathrm{d}x^1\mathrm{d}x^2 \mathrm{d}x^3\), the product of forms is understood as the wedge product. The symbol \(\mathrm{d}^3x\)  means the 3-form \(\mathrm{d}^3x= \mathrm{d}x^1\mathrm{d}x^2\mathrm{d}x^3\) on \(\mathbb{R}^4\). Contraction of a form \(\omega\) with a vector \(v\) is denoted by \(\mathfrak{i}_v(\omega)\). The notation \(\mathfrak{i}_v (\omega)\) is also used for the spinor matrix valued vector \(\gamma=(\gamma^0,\gamma^1,\gamma^2,\gamma^3)=\gamma^\alpha e_\alpha\):
\begin{equation}
\mathfrak{i}_\gamma (\mathrm{d}^4x) := \gamma^\alpha \mathfrak{i}_{e_\alpha}(\mathrm{d}^4 x),
\end{equation} 

with \((e_\alpha)_{\alpha}\) being the canonical basis of \(\mathbb{C}^4\). Let \(\mathcal{C}_A\) be the space of solutions to \eqref{dirac} which have compact support on any spacelike hyperplane \(\Sigma\). Let \(\phi, \psi\) be in \(\mathcal{C_A}\), the scalar product \(\langle \cdot, \cdot\rangle\) of elements of \(\mathcal{C}_A\) is defined as


%\begin{equation}
%\langle \phi, \psi \rangle := \int_{\Sigma} \overline{\phi (x)} \mathfrak{i}_{\gamma} (\mathrm{d}^4x) \psi (x)=: \int_{\Sigma} \phi^\dagger (x) \gamma^0 \mathfrak{i}_{\gamma} (\mathrm{d}^4x) \psi (x) .
%\end{equation}
%Furthermore define \(\mathcal{H}\) to be \(\mathcal{H}:=\overline{\mathcal{C}_A}^{\langle \cdot, \cdot \rangle}\). The mas-shell \(\mathcal{M}\subset \mathbb{R}^4\) is given by
%\begin{equation}
%\mathcal{M}=\{p\in \mathbb{R}^4\mid p^2=m^2\}.
%\end{equation}
%The subset \(\mathcal{M}^+\) of \(\mathcal{M}\) is defined to be \(\mathcal{M}^+:=\{p\in\mathcal{M}\mid p^0>0\}\). The image  of \(\mathcal{H}\) by the projector \(1_{\mathcal{M^+}}\), given in momentum space representation, is denoted by \(\mathcal{H}^+\) and its orthogonal complement by \(\mathcal{H}^-\). 
%I introduce a family of Cauchy hypersurfaces \((\Sigma_t)_{t\in\mathbb{R}}\) governed by a family of normal vector fields \((\left.v_t n\right|_{\Sigma_t})\), where \(n: \mathbb{R}^4 \times \mathbb{R} \rightarrow \mathbb{R}^4\) and \(v: \mathbb{R}^4 \times \mathbb{R} \rightarrow \mathbb{R}\) are smooth functions. For \(x\in\Sigma_t\) the vector \(n_t(x)\) denotes the future directed unit-normal vector to \(\Sigma_t\) at \(x\) and \(v_t(x)\) the corresponding normal velocity of the flow of the Cauchy surfaces. 

%Now we have the tools to recast the Dirac equation into an integral version
%which will allow me to define the scattering operator. 
%Let \(\psi \in \mathcal{C}_A\), for any \(t\in\mathbb{R}\) I denote by \(\phi_t\) the solution to the free Dirac equation, that is equation \eqref{dirac} with \(A=0\), with \(\left.\psi\right|_{\Sigma_t}\) as initial condition on \(\Sigma_t\). Let \(t_0\in\mathbb{R}\) have some fixed value, equation \eqref{dirac} can be reformulated, c.f. theorem 2.23 of \cite{ivp1}, as
%\begin{multline}\label{dirac_integral}
%\phi_t(y)=\phi_{t_0}(y)
%-i \int_{t_0}^t \text{d}s \int_{\Sigma_s}\int_{\mathcal{M}}\frac{\slashed{p}+m}{2m^2}e^{ip(x-y)}\mathfrak{i}_p(\text{d}^4p) \frac{\mathfrak{i}_{\gamma}(\text{d}^4x)}{(2\pi)^{3}}\\
%v_s(x)\slashed{n}_s(x) \slashed{A}(x)\phi_s(x),
%\end{multline}
%which holds for any \(t\in\mathbb{R}\). Employing the following rewriting of integrals

%\begin{equation}
%\int_{\mathcal{M}}\frac{\slashed{p}+m}{2 m^2} f(p) \mathfrak{i}_p(\text{d}^4p)=\frac{1}{2\pi i}   \left( \int_{\mathbb{R}^4-i \epsilon e_0}-\int_{\mathbb{R}^4+i \epsilon e_0} \right) (\slashed{p}-m)^{-1} f(p)  \text{d}^4p,
%\end{equation}
%which is due to the theorem of residues, equation \eqref{dirac_integral} assumes the form

%\begin{multline}
%\phi_t(y)=\phi_{t_0}(y)
%- \int_{[t_0,t]\times\mathbb{R}^3}  \left( \int_{\mathbb{R}^4-i \epsilon e_0}-\int_{\mathbb{R}^4+i \epsilon e_0} \right)\\
% (\slashed{p}-m)^{-1} e^{ip(x-y)}  \text{d}^4p  \frac{\text{d}^4x}{(2\pi)^{4}}\slashed{A}(x)\phi_s(x). 
%\end{multline} 
%In the last expression I picked all hypersurfaces \(\Sigma_s\) to be equal time
%hyperplanes such that \(v_s=1\) and \(\slashed{n}_s=\gamma^0 e_0\). We identify
%the advanced and retarded Greens functions of the Dirac equation:
%\begin{equation}
%\Delta^\pm (x):= \frac{-1}{(2\pi)^4} \int_{\mathbb{R}^4\pm i \varepsilon e_0} \frac{\slashed{p}+ m}{p^2-m^2} e^{-ipx} d^4 p,
%\end{equation}
%yielding
%\begin{multline}\label{dirac integral split}
%\phi_t(y)=\phi_{t_0}(y)
%+ \int_{[t_0,t]\times\mathbb{R}^3}  (\Delta^--\Delta^+)(y-x)  \text{d}^4x \slashed{A}(x)\phi_s(x). 
%\end{multline} 

% Iteratingequation \eqref{dirac integral split} and picking \(t\) in the future of
%\(\supp A\) and \(t_0\) in the past of it, denoting them by \(\pm \infty\) since 
%their exact value is no longer important, the following series expansion is 
%obtained informally

%\begin{equation}\label{DefU}
%\phi_\infty(y)=U^A \phi_{-\infty} :=\sum_{k=0}^\infty Z_k(A) \phi_{-\infty},
%\end{equation} 
%with \(Z_0=\id \), the identity on \(\mathbb{C}^4\), and where for arbitrary \(\phi\in \mathcal{H}\), \(Z_k \) is defined as
%\begin{align*}
%&Z_k(A)\phi(y):= \int_{\mathbb{R}^4}  (\Delta^--\Delta^+)(y-x_1)  \text{d}^4x_1 \slashed{A}(x_1) \\
%&\prod_{l=2}^k \left[\int_{[-\infty,x^0_{l-1}]\times\mathbb{R}^3}  (\Delta^--\Delta^+)(x_{l-1}-x_l)   \slashed{A}(x_l)\text{d}^4x_l\right]
% \phi(x_k).
%\end{align*}
%Now since the integration variables are time ordered and \(\supp \Delta^\pm \subseteq \text{Cau}^\pm\) 
%in every one but the first factor the contribution of \(\Delta^-\) vanishes. Therefore we can simply \noch{führe Cau als kausale Menge ein}
%drop it. Furthermore we may continue the integration domain to all of \(\mathbb{R}^4\), since
%there \(\Delta^+\) gives no contribution, giving
%\begin{multline}\label{Z_kDelta}
%Z_k(A)\phi(y)= (-1)^{k-1}\int_{\mathbb{R}^4}\text{d}^4x_1  (\Delta^--\Delta^+)(y-x_1)   \slashed{A}(x_1) \\
%\prod_{l=2}^k \left[\int_{\mathbb{R}^4}\text{d}^4x_l \Delta^+(x_{l-1}-x_l)   \slashed{A}(x_l)\right]
% \phi(x_k).
%\end{multline}


% This is convenient, because we may now use the spacetime
%integration with the exponential factor of the definition of \(\Delta^-\) as a Fourier transform
%acting on the four-potentials and the wave function. 
%Undoing the substitutions again for the first factor and executing the just mentioned Fourier
%transforms using the convolution theorem inductively results in

%\begin{multline}\label{explicit_Zk}
%Z_k(A)\phi(y) =- i  \int_{\mathcal{M}}\frac{\mathfrak{i}_p(\text{d}^4p_1)}{(2\pi)^{3}} \frac{\slashed{p}_1+m}{2m} e^{-ip_1y}  \\
%  \prod_{l=2}^{k} \left[ \int_{\mathbb{R}^4+i \epsilon e_0}\frac{\text{d}^4p_l}{(2\pi)^{4}} \slashed{A}(p_{l-1}-p_l)  (\slashed{p}_l-m)^{-1}  
% \right]\\
% \int_{\mathcal{M}}  \mathfrak{i}_p(\text{d}^4p_{k+1})\slashed{A}(p_{k}-p_{k+1})\hat{\phi}(p_{k+1}).
%\end{multline}

%Due to the representation \eqref{Z_kDelta} one may also represent \(Z_k\) in terms of The operators
%\begin{align}
%\Delta^0:= \Delta^+-\Delta^-\\
%L_A^{\pm,0}:= \Delta^{\pm,0} \ast \slashed{A}
%\end{align}
%in this manner
%\begin{equation}
%Z_k(A)\phi(y)= (-1)^{k} L^0_A \left({L_A^+}^{k-1}( \phi)\right) (y),
%\end{equation}
%where the upper right index for an operator means iterative application of said operator.

\noch{delete derivation; simply state series representation and convergence result citing something}

\subsection{Construction of the Second Quantised Scattering-Matrix}\label{sec:second quant}
 In the following I outline how the construction of the
second quantised scattering operator is to be carried out, we will naturally be
led to an informal power series representation for the scattering operator \(S\). 

First I fix some more notation in agreement with \cite{ivp2}. Using a general Hilbertspace \(\mathcal{H}\) as a one-particle Hilbertspace. 
A closed subspace \(\mathcal{H}^+\) of \(\mathcal{H}\) is called polarisation if both \(\mathcal{H}^+\) and \(\mathcal{H}^-:=\left(\mathcal{H}^+\right)^\perp\)
are infinite dimensional, where by \(\perp\) I denote the orthogonal complement. With a polarisation \(\mathcal{H}^+\) comes also the orthogonal
projection operator \(P^+\) onto the subspace \(\mathcal{H}^+\) and its complement \(P^-=1-P^+\). For one particle operators \(C\) we 
introduce the notation \(C_{\#\ddag}:= P^\# C P^\ddag\), where \(\#,\ddag\in\{+,-\}\).
%\Dirk{am besten schon oben einführen}
One constructs the Fock space associated with \(\mathcal{H}\) and a polarisation \(\mathcal{H}^+\) of \(\mathcal{H}\) in the following way.
We define \(\overline{\mathcal{H}^-}\) identical with \(\mathcal{H}^-\) as a set, but scalar multiplication as 
\(\mathbb{C}\times \overline{\mathcal{H}} \ni (a, \psi)\mapsto \overline{a} \psi\) where the bar denotes complex conjugation of complex numbers.
A wedge \(\wedge\) in the exponent denotes that only elements which are antisymmetric with respect to permutations
are allowed. This antisymmetric product as well as the tensor product are to be understood in the Hilbert space sense. 
The Factor \(\left(\mathcal{H}^{\pm}\right)^0\) is understood as
\(\mathbb{C}\). We now define Fock space as

\begin{equation}
\mathcal{F}:=\bigoplus_{m,p=0}^\infty \left(\mathcal{H}^+ \right)^{\wedge m} \otimes \left(\overline{\mathcal{H}^- }\right)^{\wedge p}.
\end{equation}

I will denote the sectors of Fock space of fixed particle
numbers by \(\mathcal{F}_{m,p}\). The element of
\(\mathcal{F}_{0,0}\) of norm \(1\) will be denoted by \(\Omega\).
The simplest and yet interesting example of this construction is
the Fock space constructed on a hyperplane prior to the support of an external field,
in this case \(\mathcal{H}=L^2(\mathbb{R}^3,\mathbb{C}^4)\) and \(\mathcal{H}^+\)
consists of the wavefunctions that can be constructed from the generalised eigenfunctions
of positive energy with respect to the free Dirac Hamiltonian.

The
annihilation operator \(a\) acts on an arbitrary sector of Fock space
\(\mathcal{F}_{m,p}\), for any \(m,p\in\mathbb{N}_0\) with either of the operator types


\begin{align}
a: &\overline{\mathcal{H}}\otimes \mathcal{F}_{m,p} \rightarrow \mathcal{F}_{m-1,p}\oplus \mathcal{F}_{m,p+1}\\
a: &\overline{\mathcal{H}}\times \mathcal{F}_{m,p} \rightarrow \mathcal{F}_{m-1,p}\oplus \mathcal{F}_{m,p+1}
\end{align}
regardless of the exact type of the annihilation operator I will denote it by \(a\). Also here the tensor product is 
understood in the algebraic sense.
I start out by defining \(a\) on elements of 
\(\{\bigwedge_{l=1}^m \varphi_l \otimes \bigwedge_{c=1}^p \phi_c  \mid \forall c:  \varphi_c \in \mathcal{H}^+, \phi_c \in \mathcal{H}^-   \}\)
which spans a dense subset of \(\mathcal{F}_{m,p}\), then one continues this operator uniquely by 
linearity and finally by the bounded linear extension theorem to all of \(\mathcal{F}_{m,p}\) and then 
again by linearity to all of \(\overline{\mathcal{H}}\otimes \mathcal{F}_{m,p}\).
\begin{align}
&a\left(\phi \otimes \bigwedge_{l=1}^m \varphi_l \otimes \bigwedge_{c=1}^p \phi_c\right)=a\left(\phi,\bigwedge_{l=1}^m \varphi_l \otimes \bigwedge_{c=1}^p \phi_c\right)\\
&= \sum_{k=1}^m (-1)^{1+k} \langle P^+ \phi, \varphi_k\rangle \bigwedge_{\overset{l=1}{l\neq k}}^m \varphi_l \otimes \bigwedge_{c=1}^p \phi_c + \bigwedge_{l=1}^m \varphi_l \otimes P^- \phi \wedge \bigwedge_{c=1}^p \phi_c
\end{align}


where \(\langle, \rangle\) denotes that the scalar product of \(\mathcal{H}\). The first summand on the right hand side is taken to vanish for \(m=0\). 
For \(\varphi\in \mathcal{H}\) I will also use the abbreviation \(a(\varphi):=a(\varphi,\cdot)\).

Now we turn to the construction of the \(S\)-matrix, the second quantised analogue of \(U^A\). This construction is carried out axiomatically. The first axiom makes sure that the following diagram, and the analogue for the adjoint of the annihilation operator commute.
\begin{equation}
\begin{CD}								%heuristics with infinite wedge space?
\mathcal{F}     @>S^A>>  \mathcal{F}\\
@AAaA        @AAaA\\
\overline{\mathcal{H}}\otimes \mathcal{F}     @>U^A\otimes S^A>>  \overline{\mathcal{H}}\otimes \mathcal{F} 
\end{CD}
\end{equation}
\begin{axiom}
The \(S\) operator fulfils the ``lift condition''.
\begin{align}\label{lift_condition1}
\forall \phi\in \mathcal{H}:& \hspace{0.5cm} S^A \circ a(\phi)=a\left( U^A \phi \right)  \circ S^A,\tag{lift condition}\\
\label{lift_condition2}
\forall \phi\in \mathcal{H}:& \hspace{0.5cm} S^A \circ a^*(\phi)=a^*\left( U^A \phi \right)  \circ S^A,\tag{adjoint lift condition}
\end{align}
where \(a^*\) is the adjoint of the annihilation operator, the creation operator. 
\end{axiom}

There is a convergent power series of the one-particle scattering operator \(U^A\):
\begin{equation}\label{U_expansion}
U^A = \sum_{k=0}^\infty \frac{1}{k!} Z_k(A),
\end{equation}
where \(Z_k(A)\) are bounded operators on \(\mathcal{H}\), which are homogeneous of degree \(k\) in \(A\).
We try an analogous formal power series ansatz for the second quantised scattering operator \(S^A\)

\begin{equation}\label{S_expansion}
S^A=\sum_{k=0}^\infty \frac{1}{k!} T_k(A).
\end{equation}
Here \(T_k\) are assumed to be homogeneous of degree \(k\) in \(A\); however, they will only turn out to be bounded on
fixed particle number subspaces \(\mathcal{F}_{m,p}\) of Fock space. It is the goal of the following  sections to
show that this ansatz indeed works. That is, we can identify operators \(T_k\) such that \eqref{S_expansion}
holds up to a global phase and furthermore the question of convergence can be settled if one assumes that 
the phase is analytic in the external field \(A\). %In constructing a guess for the scattering operator \(S^A\) we will assume \eqref{S_expansion} to converge absolutely when applied to an element of Fock space with finitely many particles.
In order to fully characterise \(S^A\) it is enough to characterise all of the \(T_k\) operators. 
Using the \eqref{lift_condition1} one can derive commutation relations for the operators 
\(T_k\) by plugging in \eqref{U_expansion} and \eqref{S_expansion} into \eqref{lift_condition1} and \eqref{lift_condition2}
and collecting all terms with the same degree of homogeneity. They are given by

\begin{equation}\label{logarithmic lift condition}
\left[T_m(A) , a^\# (\phi)\right]= \sum_{j=1}^{m} \begin{pmatrix} m \\ j \end{pmatrix} a^\# \left(Z_j (A) \phi \right) T_{m-j}(A), 
\end{equation}
where \(a^\#\) is either \(a\) or \(a^*\). Together \(T_k\) and \(\langle T_k\rangle\) characterise the operator \(T_k\) on the whole algebraic
direct sum, it can then be further extended to all of Fock space.

Before we go on to construct a concrete form of the scattering operator, we will first define a certain kind of unitary operator on Fock space.

\subsection{Differential second quantisation}

Let \(B:\mathcal{H}\rightarrow\mathcal{H}\) be a bounded
operator on \(\mathcal{H}\), such that \(i B\) is self adjoint and \(B_{+-}\) is a Hilbert-Schmidt operator. 
We would like to construct a version \(\mathrm{d}\Gamma(B)\) of \(B\) that acts on Fock space and also is skew adjoint.
The strategy of this section is to construct an operator in two steps that is essentially self adjoint of the Fock space of 
finitely many particles, a dense subset of Fock space. It is denoted by

\begin{Def}
\begin{equation}
\mathcal{F}':=\bigobot_{m,p=0}^\infty \mathcal{F}_{m,p},
\end{equation}
where \(\bigobot\) refers to the algebraic direct sum.
\end{Def}
Because \(B_{-+}:\mathcal{H}^+\rightarrow \mathcal{H}^-\) is compact, there is an ONB \((\varphi_n)_{n\in\mathbb{N}}\) 
of \(\mathcal{H}^+\) and likewise an ONB \((\varphi_{-n})_{n\in\mathbb{N}}\) of \(\mathcal{H}^-\) such that it takes the canonical form 
of compact operators

\begin{equation}
B_{-+} = \sum_{n\in\mathbb{N}} \lambda_n |\varphi_{-n}\rangle \langle \varphi_{n}|, \quad \lambda_n \ge 0.
\end{equation}
Here the numbers \(\lambda_n\) fulfil \(\sum_{k=1}^\infty \lambda_k^2 = \|B_{-+}\|_{\text{HS}}<\infty\). As a consequence we have

\begin{equation}
B_{+-} = -\sum_{n\in\mathbb{N}} \lambda_n |\varphi_{n}\rangle \langle \varphi_{-n}|.
\end{equation}

With respect to this basis we define the set of finite linear combinations of product states of finitely many particles

\begin{Def}
We define
\begin{equation}
\mathcal{F}^0\!\!:=\! \mathrm{span}\!\! \left\{\prod_{k=1}^m \!a^*\!(\varphi_{L_k}\!)\!\prod_{c=1}^p\!\! a(\varphi_{-C_c})\Omega\mid m,p\!\in\!\!\mathbb{N}, (L_k)_k,\!(C_c)_c\!\subset\!\mathbb{N} \!\right\}\!,
\end{equation}
we will refer to a subset of this set for fixed values of \(m\) and \(p\) by \(\mathcal{F}^0_{m,p}\).
\end{Def}

In order to do so, the following splitting turns out to be advantageous. 

\begin{Def}
We define the following operators of type \(\mathcal{F}^0\rightarrow \mathcal{F}\)

\begin{align}\label{predefdGamma}
\mathrm{d}\Gamma(B_{++})&:= \sum_{n\in\mathbb{N}}  a^*(B_{++} \varphi_n) a(\varphi_n) \\
\mathrm{d}\Gamma(B_{--})&:= -\sum_{n\in\mathbb{N}}   a(\varphi_{-n})a^*(B_{--} \varphi_{-n}) \\
\mathrm{d}\Gamma(B_{-+})&:= \sum_{n\in\mathbb{N}}  a^*(B_{-+}\varphi_{n}) a(\varphi_n)
\end{align}
where the sum converges in the strong operator topology and \((\varphi_n)_n , (\varphi_{-n})_n\) are arbitrary ONBs of \(\mathcal{H}^+\) and \(\mathcal{H}^-\).
\end{Def}



\begin{Lemma}
The operators \(\mathrm{d}\Gamma(B_{++}),\mathrm{d}\Gamma(B_{--})\) and \(\mathrm{d}\Gamma(B_{-+})\) 
restricted to \(|_{\mathcal{F}^0_{m,p}}\) they have the following type
\begin{align}
\mathrm{d}\Gamma(B_{++})|_{\mathcal{F}^0_{m,p}}&: \quad \mathcal{F}^0_{m,p} \rightarrow \mathcal{F}_{m,p}\\
\mathrm{d}\Gamma(B_{--})|_{\mathcal{F}^0_{m,p}}&: \quad \mathcal{F}^0_{m,p} \rightarrow \mathcal{F}_{m,p}\\
\mathrm{d}\Gamma(B_{-+})|_{\mathcal{F}^0_{m,p}}&: \quad \mathcal{F}^0_{m,p} \rightarrow \mathcal{F}_{m-1,p-1}
\end{align}
 and fulfil
the following bounds for all \(m,p\)
\begin{align}
\|\mathrm{d}\Gamma(B_{++})|_{\mathcal{F}^0_{m,p}}\|&\le (m+1)\|B_{++}\|\\
\|\mathrm{d}\Gamma(B_{--})|_{\mathcal{F}^0_{m,p}}\|&\le (p+1)\|B_{--}\|\\
\|\mathrm{d}\Gamma(B_{-+})|_{\mathcal{F}^0_{m,p}}\|&\le \|B_{-+}\|_{\text{HS}}.
\end{align}
\end{Lemma}
\begin{proof}
Pick \(\alpha\in\mathcal{F}^0_{m,p}\) for \(m,p\in\mathbb{N}_0\), \(\alpha\) can be expressed in terms of a general ONB 
\((\tilde{\varphi}_k)_{k\in\mathbb{N}}\) of \(\mathcal{H}^+\) and \((\tilde{\varphi}_{-k})_{k\in\mathbb{N}}\) of \(\mathcal{H}^-\)
\begin{equation}
\alpha=\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}\!\!\!\!\!\!\alpha_{L,C} \prod_{l=1}^m a^*(\tilde{\varphi}_{L_l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C_c}) \Omega.
\end{equation}
In this expansion only finitely many coefficients \(\alpha_{\cdot, \cdot}\) are nonzero. Our operators all map the vacuum onto the zero vector, so commuting them 
through the products of of creation and annihilation operators in the expansion of \(\alpha\) we can make the action of them more explicit:
\begin{align}\nonumber
\mathrm{d}\Gamma(B_{++}) \alpha =\hspace{-0.5cm} \sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}\!\!\!\!\!\!\alpha_{L,C} \sum_{b=1}^m 
\prod_{l=1}^{b-1} a^*(\tilde{\varphi}_{L_l})  \sum_{n\in\mathbb{N}} a^*(B_{++}\varphi_n) \langle \varphi_n, \tilde{\varphi}_{L_b}\rangle \\
\prod_{l=b+1}^m a^*(\tilde{\varphi}_{l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C_c}) \Omega\\
=\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}\!\!\!\!\!\!\alpha_{L,C} \sum_{b=1}^m 
\prod_{l=1}^{b-1} a^*(\tilde{\varphi}_{L_l})  ~~ a^*(B_{++} \tilde{\varphi}_{L_b})  \!\!\!
\prod_{l=b+1}^m a^*(\tilde{\varphi}_{l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C_c}) \Omega.
\end{align}
We notice, that \(\mathrm{d}\Gamma(B_{++})\alpha \in \mathcal{F}_{m,p}\) holds. What is left to show for the first operator is therefore
its norm. For estimating this we see that \(B_{++}\) in the last line can be replaced by 
\begin{equation}
B^L_{L_b}:=\left(1-\sum_{\overset{l=1}{l\neq b}}^m |\tilde{\varphi}_{L_l}\rangle \langle \tilde{\varphi}_{L_l}|\right) B_{++},
\end{equation}
due to the antisymmetry of fermions. Expanding 
\begin{align}\nonumber
&\|\mathrm{d}\Gamma(B_{++})\alpha\|^2 = \langle \mathrm{d}\Gamma(B_{++})\alpha, \mathrm{d}\Gamma(B_{++})\alpha \rangle \\\nonumber
&= \hspace{-1cm}\sum_{\overset{L,C, L',C'\subset \mathbb{N}}{|L'|=|L|=m,|C'|=|C|=p}}\hspace{-1cm}\overline{\alpha_{L,C}}\alpha_{L',C'} \sum_{b,b'=1}^m 
\left\langle \prod_{l=1}^{b-1} a^*(\tilde{\varphi}_{L_l})  ~~ a^*(B^{L}_{L_b} \tilde{\varphi}_{L_b})\right.  \\\nonumber
&\prod_{l=b+1}^m a^*(\tilde{\varphi}_{L_l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C_c}) \Omega, 
\prod_{l=1}^{b'-1} a^*(\tilde{\varphi}_{L'_l})  ~~ a^*(B_{L'_{b'}}^{L'} \tilde{\varphi}_{L'_b})  \\
&\left.\prod_{l=b'+1}^m a^*(\tilde{\varphi}_{L'_l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C'_c}) \Omega\right\rangle
\end{align}
we see that in fact \(C\) and \(C'\) need to agree, because we can just commute the corresponding annihilation operators from one end of the 
scalar product to the other. Furthermore only a single wavefunction on each side of the scalar product is modified, this implies that in order for the
scalar product not to vanish \(|L\cap L'|\ge m-2\) has to hold. If \(L\neq L'\) the double sum over \(n,n'\) has only the contribution where 
\(b=L_l \not\in L'\) and \(b'=L'_{l'}\not\in L\) are selected. Otherwise the full sum contributes, yielding
\begin{align}\nonumber
&\|\mathrm{d}\Gamma(B_{++})\alpha\|^2 = \\\nonumber
&= \hspace{-0.4cm}\sum_{\overset{L,C\subset \mathbb{N}}{\overset{|C|=p}{|L|=m-1}}}\hspace{-0.2cm}\sum_{n\neq n'\in\mathbb{N}\backslash L }
\hspace{-0.4cm}\overline{\alpha_{L\cup\{n\},C}}\alpha_{L\cup\{n'\},C}
 \langle B^{L\cup\{n\}}_n \tilde{\varphi}_{n}, B^{L\cup\{n'\}}_{n'}\tilde{\varphi}_{n'}\rangle (-1)^{g(L,n)+g(L,n')}\\\label{B++estimate}
&+\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}\hspace{-0.4cm} |\alpha_{L,C}|^2
 \sum_{b,b'=1}^m 
\left\langle \prod_{l=1}^{b-1} a^*(\tilde{\varphi}_{L_l})  ~~ a^*(B^{L}_{L_b} \tilde{\varphi}_{L_b})\right.  \\\nonumber
&\prod_{l=b+1}^m a^*(\tilde{\varphi}_{L_l}) \Omega, 
\prod_{l=1}^{b'-1} a^*(\tilde{\varphi}_{L_l})  ~~ a^*(B_{L_{b'}}^{L} \tilde{\varphi}_{L_b})  \left.\prod_{l=b'+1}^m a^*(\tilde{\varphi}_{L_l}) ) \Omega\right\rangle,
\end{align}
where \(g(L,n):=|\{l\in L \mid l<n\}|\) keeps track of the number of anti commutations. In the first sum we add and subtract the terms 
where \(n=n'\). The enlarged sum can then be reformulated

\begin{align}\nonumber
&\sum_{\overset{L,C\subset \mathbb{N}}{\overset{|L|=m-1}{|C|=p}}}\hspace{-0.1cm}\sum_{n,n'\in\mathbb{N}\backslash L} \hspace{-0.3cm}\overline{\alpha_{L\cup\{n\},C}}\alpha_{L\cup\{n'\},C} 
 \langle B^{L\cup\{n\}}_n \tilde{\varphi}_{n}, B^{L\cup\{n'\}}_{n'}\tilde{\varphi}_{n'}\rangle (-1)^{g(L,n)+g(L,n')}\\\nonumber
 &=\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m-1,|C|=p}}\left\|\sum_{n\in\mathbb{N}\backslash L}\alpha_{L\cup\{n\},C}  B^{L\cup\{n\}}_n \tilde{\varphi}_{n} (-1)^{g(L,n)} \right\|^2\\\label{B++ first term}
  &=\sum_{\overset{L,C\subset \mathbb{N}}{\overset{|L|=m-1}{|C|=p}}}\left\|\left(1-\sum_{l\in L}|\tilde{\varphi}_l\rangle\langle \tilde{\varphi}_l | \right)B_{++}\hspace{-0.2cm}\sum_{n\in\mathbb{N}\backslash L}\hspace{-0.2cm}\alpha_{L\cup\{n\},C}  \tilde{\varphi}_{n} (-1)^{g(L,n)} \right\|^2
\end{align}
Now the operator product inside the norm has operator norm \(\|B_{++}\|\) and so we can estimate the whole object by
\begin{equation}\label{B++estimatefinal1}
\eqref{B++ first term}\le \|\alpha\|^2 \|B_{++}\|^2.
\end{equation}
Now for the first term in \eqref{B++estimate} we need to estimate the term we added to complete the norm square, this is done as follows
\begin{align}\nonumber
&\sum_{\overset{L,C\subset\mathbb{N}}{|L|=m-1,|C|=p}} \hspace{-0.4cm}\sum_{n\in\mathbb{N}\backslash L} |\alpha_{L\cup\{n\},C}|^2 \|B_n^{L\cup\{n\}} \tilde{\varphi}_{n}\|^2\\\label{B++estimatefinal2}
&\le \hspace{-0.6cm}\sum_{\overset{L,C\subset\mathbb{N}}{|L|=m,|C|=p}}\hspace{-0.5cm} \|B_{++}\|^2|\alpha_{L,C}|^2 =\|\alpha\|^2 \|B_{++}\|^2.
\end{align}
What remains is the second sum in \eqref{B++estimate}, for this term there are two cases.  If \(b=b'\) then the scalar product is 
equal to \(\langle B_{L_b}^L \tilde{\varphi}_b, B_{L_{b}}^L \tilde{\varphi}_{b}\rangle\). If \(b\neq b'\) the scalar product is, up to a sign,
equal to \(\langle B_{L_b}^L \tilde{\varphi}_b,\tilde{\varphi}_{b}\rangle \langle \tilde{\varphi}_{b'}, B_{L_{b'}}^L \tilde{\varphi}_{b'}\rangle\).
However both of these terms can be estimated by \(\|B_{++}\|^2\). So all \(m^2\) summands of this sum contribute \(\|B_{++}\|^2\). Overall 
this estimate yields
\begin{align}\nonumber
&\|\mathrm{d}\Gamma(B_{++})\alpha\|^2 \le \eqref{B++estimatefinal1}+\eqref{B++estimatefinal2} + \|\alpha\|^2 m^2 \|B_{++}\|^2 \\\nonumber
&= \|\alpha\|^2 (2+m^2) \|B_{++}\|^2.
\end{align}
For convenience of notation the estimate can be weakened to 
\begin{equation}
\|\mathrm{d}\Gamma(B_{++})\alpha\| \le (m+1) \|B_{++}\|,
\end{equation}
because for all \(m\neq0\) 
this estimate is and upper bound on what we found, but for \(m=0\) the operator \(\mathrm{d}\Gamma(B_{++})\) is actually the zero operator.
A completely analogous argument works for \(\mathrm{d}\Gamma(B_{--})\). 

So lets move on to \(\mathrm{d}\Gamma(B_{-+})\). Applying it to the same \(\alpha\in \mathcal{F}^0_{m,p}\) again we permute all the operators
to the right, where they annihilate the vacuum. The remaining terms are

\begin{align}\nonumber
\sum_{n\in\mathbb{N}} a^*(B_{-+}\varphi_n)a(\varphi_{n})\hspace{-0.5cm}\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}  \hspace{-0.5cm}\alpha_{L,C} 
\prod_{l=1}^m a^*(\tilde{\varphi}_{L_l}) \prod_{c=1}^p a(\tilde{\varphi}_{-C_c}) \Omega  \\\nonumber
=\sum_{\overset{L,C\subset \mathbb{N}}{|L|=m,|C|=p}}\hspace{-0.5cm} \alpha_{L,C} \sum_{b=1}^m \sum_{d=1}^p (-1)^{m-1+b+d} \langle B_{+-} \tilde{\varphi}_{-C_d},\tilde{\varphi}_{L_b}\rangle \\
\prod_{\overset{l=1}{l\neq b}}^m a^*(\tilde{\varphi}_{L_l})
\prod_{\overset{c=1}{c\neq d}}^p a(\tilde{\varphi}_{-C_c})\Omega.
\end{align}
By counting the remaining creation and annihilation operators we immediately see that \(\mathrm{d}\Gamma(B_{-+})\alpha\in \mathcal{F}_{m-1,p-1}\). 
For estimating the norm of this vector, we switch basis from \((\tilde{\varphi}_{\pm n})_n\) to \((\varphi_{\pm n}')_n\), the basis where 
\(B_{-+}\) takes its canonical form. Then the scalar product involving \(B_{-+}\) reduces to \(\lambda_{L_b}\delta_{L_b,C_d}\). We estimate

\begin{align}\nonumber
&\|\mathrm{d}\Gamma(B_{-+})\alpha\|^2= \hspace{-0.5cm}\sum_{\overset{L,L',C,C'\subset\mathbb{N}}{\overset{|L|=|L'|=m}{|C|=|C'|=p}}} ~\sum_{a,a'=1}^m \sum_{b,b'=1}^p
\overline{\alpha}_{L,C} \alpha_{L',C'}(-1)^{b+d+b'+d'}\lambda_{L_b} \lambda_{L_{b'}'} \\
&\delta_{L_b,C_d} \delta_{L_{b'}',C_{d'}'} \left\langle \prod_{\overset{l=1}{l\neq b}}^m a^*(\varphi_{L_l}')\prod_{\overset{c=1}{c\neq d}}^p 
a(\varphi_{-C_c}')\Omega, \prod_{\overset{l=1}{l\neq b'}}^m a^*(\varphi_{L_l'}')
\prod_{\overset{c=1}{c\neq d'}}^p a(\varphi_{-C_c'}')\Omega\right\rangle.
\end{align}

The scalar product in the second line tells us that \(L\backslash \{L_b\}=L'\backslash \{L_{b'}'\}\) and \(C\backslash \{C_{d}\}=C'\backslash \{C_{d'}'\}\) have
to hold in order for the term not to vanish. So this means that \(L\) and \(L'\) as well as \(C\) and \(C'\) can respectively differ at most by one element
which then has to be in the intersection \(L\cap C\). Because this sum is really just a finite sum, we can reorder it in the following way

\begin{align}\nonumber
\|\mathrm{d}\Gamma(B_{-+})\alpha\|^2
&=\hspace{-0.4cm}\sum_{\overset{L,C\subset\mathbb{N}}{\overset{|L|=m-1}{|C|=p-1}}} \sum_{b,b'\in \mathbb{N}\backslash (L\cup C)}\hspace{-0.3cm} \lambda_{b} \lambda_{b'} 
\overline{\alpha}_{L\cup\{b\},C\cup \{b\}} \alpha_{L\cup\{b'\},C\cup\{b'\}}\\
&(-1)^{g(L,b)+g(C,b)+g(L,b')+g(C,b')},
\end{align}
where \(g(L,b)=|\{l\in L \mid l<b\}|\) as before. This expression can be rewritten in terms of a scalar product in \(\ell^2(\mathbb{N})\)

\begin{align}\nonumber
\|\mathrm{d}\Gamma(B_{-+})\alpha\|^2
&=\hspace{-0.4cm}\sum_{\overset{L,C\subset\mathbb{N}}{\overset{|L|=m-1}{|C|=p-1}}} \left|\left\langle 1_{(L\cup C)^c} \alpha_{L\cup \{\cdot \}, C\cup \{\cdot\}} (-1)^{g(L,\cdot)+g(C,\cdot)},\lambda_\cdot \right\rangle_{\ell^2}  \right|^2 \\
&\le \hspace{-0.4cm}\sum_{\overset{L,C\subset\mathbb{N}}{\overset{|L|=m-1}{|C|=p-1}}} \sum_{b\in \mathbb{N}} 1_{(L\cup C)^c}(b) |\alpha_{L\cup\{b\},C\cup\{b\}}|^2 \sum_{d\in\mathbb{N}}\lambda_d^2\\
&\le \|\alpha\|^2 \|B_{-+}\|^2_{\text{HS}}.
\end{align}

\end{proof}

\begin{Corollary}
The operators \(\mathrm{d}\Gamma(B_{--})\) and \(\mathrm{d}\Gamma(B_{++})\) can be extended by continuity on \(\mathcal{F}^0_{m,p}\) to unbounded operators on all of \(\mathcal{F}'\).
The operator \(\mathrm{d}\Gamma(B_{-+})\) can be continuously extended to all of \(\mathcal{F}\).
\end{Corollary}

\begin{Lemma}
The operator \(\left(\mathrm{d}\Gamma(B_{-+})\right)^*\)  acts on elements of \(\mathcal{F}^0\) as

\begin{equation}
- \sum_{n\in\mathbb{N}} a^*(B_{+-}\varphi_{-n}) a(\varphi_{-n})=:-\mathrm{d}\Gamma(B_{+-}).
\end{equation}
So also \(\mathrm{d}\Gamma(B_{+-}):\mathcal{F}^0\rightarrow \mathcal{F}\) can be extended continuously to all of \(\mathcal{F}\).
Moreover \(\mathrm{d}\Gamma(B_{-+})+\mathrm{d}\Gamma(B_{+-})\) is skew-adjoint.
\end{Lemma}
\begin{proof}
Pick \(\beta,\alpha \in \mathcal{F}^0\). We expand those states with respect to the basis \((\varphi_k')_{k\in\mathbb{Z}\backslash \{0\}}\). Consider

\begin{align}\nonumber
&\langle \beta, \mathrm{d}\Gamma(B_{-+}) \alpha \rangle=\left\langle \beta, \sum_{n\in\mathbb{N}} a^*(B_{-+}\varphi_n)a(\varphi_{n}) \alpha \right\rangle\\\nonumber
&=\sum_{n\in\mathbb{N}} \langle \beta , a^*(B_{-+}\varphi_n)a(\varphi_{n}) \alpha\rangle
=\sum_{n\in\mathbb{N}}  \langle a^*(\varphi_{n})  a(B_{-+}\varphi_n)\beta , \alpha\rangle\\\nonumber
&=\left\langle \sum_{n\in\mathbb{N}}a^*(\varphi_{n})  a(B_{-+}\varphi_n) \beta, \alpha \right\rangle
=\left\langle \sum_{n\in\mathbb{N}} \lambda_n a^*(\varphi_{n})  a(\varphi_{-n}) \beta, \alpha \right\rangle\\
&=\left\langle \sum_{n\in\mathbb{N}}  a^*(- B_{+-}\varphi_{-n})  a(\varphi_{-n}) \beta, \alpha \right\rangle
=-\langle \mathrm{d}\Gamma(B_{+-})  \beta, \alpha \rangle,
\end{align}
 So we see that \(\mathrm{d}\Gamma(B_{+-})\)
and \(\mathrm{d}\Gamma(B_{-+})^*\) agree on \(\mathcal{F}^0\) which is dense. So they are the same bounded and continuous operator on all of
Fock space. 
\end{proof}

\begin{Lemma}
The operator \(\mathrm{d}\Gamma(B):\mathcal{F}'\rightarrow \mathcal{F}\),
\begin{equation}
\mathrm{d}\Gamma(B):=\mathrm{d}\Gamma(B_{++})+\mathrm{d}\Gamma(B_{+-})+\mathrm{d}\Gamma(B_{-+})+\mathrm{d}\Gamma(B_{--})
\end{equation}
is skew symmetric.
\end{Lemma}
\begin{proof}
Since the sum of skew symmetric operators is skew symmetric, it suffices to show skew symmetry of \(\mathrm{d}\Gamma(B_{++})\) and \(\mathrm{d}\Gamma(B_{--})\).
Moreover since both of these operators are extended versions of operators of the same name of type \(\mathcal{F}^0\rightarrow \mathcal{F}\) it suffices to show skew symmetry
on this domain. We will only do the calculation for \(\mathrm{d}\Gamma(B_{++})\), the other calculation is analogous. 
First we notice that
\begin{equation}
\mathrm{d}\Gamma(B_{++})=\sum_{n\in\mathbb{N}} a^*(B_{++}\varphi_{n})a(\varphi_n)
=\sum_{n\in\mathbb{N}} \sum_{m\in\mathbb{N}}  \langle \varphi_m, B_{++}\varphi_n\rangle a^*(\varphi_m) a(\varphi_n)
\end{equation}
holds.  Pick \(\alpha,\beta \in \mathcal{F}^0\). Consider
\begin{align}\nonumber
\left\langle \beta, \mathrm{d}\Gamma(B_{++}) \alpha \right\rangle
= \sum_{L,L',C,C'\subset \mathbb{N}} \overline{\beta}_{L',C'}\alpha_{L,C} 
\left\langle \prod_{l=1}^{|L'|}a^*(\varphi_{L_l'})\prod_{c=1}^{|C'|} a(\varphi_{-C_c'})\Omega,\right. \\ \nonumber
\left. \sum_{n\in\mathbb{N}} a^*(B_{++}\varphi_{n})a(\varphi_n) \prod_{l=1}^{|L|}a^*(\varphi_{L_l})\prod_{c=1}^{|C|} a(\varphi_{-C_c})\Omega\right\rangle\\\nonumber
= \sum_{L,L',C,C'\subset \mathbb{N}} \overline{\beta}_{L',C'}\alpha_{L,C} \sum_{n\in\mathbb{N}}
\left\langle \prod_{l=1}^{|L'|}a^*(\varphi_{L_l'})\prod_{c=1}^{|C'|} a(\varphi_{-C_c'})\Omega,\right. \\ \nonumber
\left. a^*(B_{++}\varphi_{n})a(\varphi_n) \prod_{l=1}^{|L|}a^*(\varphi_{L_l})\prod_{c=1}^{|C|} a(\varphi_{-C_c})\Omega\right\rangle\\\nonumber
= \sum_{L,L',C,C'\subset \mathbb{N}} \overline{\beta}_{L',C'}\alpha_{L,C} \sum_{n\in\mathbb{N}}
\left\langle a^*(\varphi_n) a(B_{++}\varphi_{n})\prod_{l=1}^{|L'|}a^*(\varphi_{L_l'})\prod_{c=1}^{|C'|} a(\varphi_{-C_c'})\Omega,\right. \\ \nonumber
\left.  \prod_{l=1}^{|L|}a^*(\varphi_{L_l})\prod_{c=1}^{|C|} a(\varphi_{-C_c})\Omega\right\rangle\\\nonumber
= \sum_{L,L',C,C'\subset \mathbb{N}} \overline{\beta}_{L',C'}\alpha_{L,C} 
\left\langle \sum_{n\in\mathbb{N}} \sum_{m\in\mathbb{N}} \langle B_{++}\varphi_n,\varphi_m\rangle a^*(\varphi_n) a(\varphi_{m})\right. \\ \nonumber
\left. \prod_{l=1}^{|L'|}a^*(\varphi_{L_l'})\prod_{c=1}^{|C'|} a(\varphi_{-C_c'})\Omega, \prod_{l=1}^{|L|}a^*(\varphi_{L_l})\prod_{c=1}^{|C|} a(\varphi_{-C_c})\Omega\right\rangle.
\end{align}
Now because \(B_{++}^*=-B_{++}\) we see that 
\begin{equation}
\left\langle \beta, \mathrm{d}\Gamma(B_{++})\alpha\right\rangle =- \left\langle \mathrm{d}\Gamma(B_{++})\beta, \alpha\right\rangle 
\end{equation}
holds.
\end{proof}



Now we would like to define \(e^{\mathrm{d}\Gamma(B)}\), in order to do so, we will show that \(\mathrm{d}\Gamma(B)\) is essentially skew-adjoint. 
One way of doing so is by Nelson's analytic vector theorem. 

\begin{Thm}[Nelson's analytic vector theorem]
Let \(C\) be a symmetric operator on a Hilbert space \(\mathscr{H}\). If \(D(C)\) contains a total set 
\(S\subset \bigcap_{n=1}^\infty D(C^n)\) of analytic vectors, then \(C\) is essentially self adjoint. 
A vector \(\phi\in \bigcap_{n=1}^\infty D(C^n)\) is called analytic if there is \(t>0\) such that
\(\sum_{k=0}^\infty \frac{\|C^n \phi\|}{n!} t^n<\infty\) holds. A set \(S\) is said to be total if \(\overline{\text{span}(S)}=\mathscr{H}\)
\end{Thm}
For a proof see e.g. \cite{SimonReed2}.

\begin{Lemma}\label{Gamma exponential bound}
For any \( \alpha \in \mathcal{F}', t>0\) the operator \(\mathrm{d}\Gamma(B):\mathcal{F}'\rightarrow \mathcal{F}\) satisfies
\begin{equation}
\sum_{k=0}^\infty \frac{\|\mathrm{d}\Gamma(B)^k \alpha\|}{k!} t^k <\infty.
\end{equation}
\end{Lemma}
\begin{proof}
 By definition of \(\mathcal{F}'\) there are \(m,p\in\mathbb{N}\) such that \(\alpha \in \bigobot_{l=0}^m\bigobot_{c=0}^p \mathcal{F}_{l,p}\). Fix \(t>0\). 
We dissect \(\alpha\) into its parts of fixed particle numbers:
\begin{equation}
\sum_{k=0}^\infty \frac{\|\mathrm{d}\Gamma(B)^k \alpha\|}{k!} t^k \le \sum_{l=0}^m\sum_{c=0}^p \sum_{k=0}^\infty \frac{\|\mathrm{d}\Gamma(B)^k \alpha_{l,c}\|}{k!} t^k .
\end{equation}
 Using the following abbreviations
\begin{align}
&\Gamma_{-1}:=\mathrm{d}\Gamma(B)_{-+}\\
&\Gamma_0:=\mathrm{d}\Gamma(B)_{++}+\mathrm{d}\Gamma(B)_{--}\\
&\Gamma_{+1}:=\mathrm{d}\Gamma(B)_{+-}\\
&\beta:=\max\{\|B_{++}\|+\|B_{--}\|,\|B_{-+},\|_{\mathrm{HS}}\}
\end{align}
we estimate
\begin{align}\nonumber
\|\mathrm{d}\Gamma(B)^k \alpha_{l,c}\|\le \sum_{x\in \{-1,0,+1\}^k} \left\| \prod_{b=1}^k \Gamma_{x_b}\alpha_{l,c}\right\|\\\label{essentialSelfadjointnessOperatorProduct}
\le  \sum_{x\in \{-1,0,+1\}^k} \prod_{b=1}^k \left\| \Gamma_{x_b}|_{\mathcal{F}_{l+\sum_{d=1}^{b-1} x_d,c+\sum_{d=1}^{b-1} x_d}}\right\| \|\alpha_{l,c}\|\\
\le 3^k \|\alpha\| \max_{x\in \{-1,0,+1\}^k} \prod_{b=1}^k\left\| \Gamma_{x_b}|_{\mathcal{F}_{l+\sum_{d=1}^{b-1} x_d,c+\sum_{d=1}^{b-1} x_d}}\right\|  .
\end{align}
At this point the factors only depend on the number of particles the Fock space vector attains as we act on it with the operators \(\Gamma_{\cdot}\). 
As these bounds increase with the particle number we can restrict the set \(\{-1,0,+1\}\) in the last line to \(\{0,+1\}\).
We notice that the bound in \eqref{essentialSelfadjointnessOperatorProduct} will only increase if  we exchange each pair 
\(x_{i}=1, x_{h}=0\) by the pair \(x_{\max\{i,h\}}=1, x_{\min\{i,h\}}=0\) so that the norm of the operator that acts like
a particle number operator is taken after the particle number is increased. The maximum therefore has the form \((c+l+2+2d)^{k-d}\), which we bound by
\(2^k (c/2+d/2+1+d)^{k-d}\).
For maximising this object we treat \(d\) as a continuous variable take the derivative and set it to zero. From the form of the function to be maximised
it is clear that it is equal to \(1\) for \(d=k\) and at \(d=-c/2-l/2\), but for \(k\) large it will be bigger in between. We abbreviate \(y=c/2+l/2+1\).
\begin{align}
0= (y+d)^{k-d} (-\ln(y+d) + \frac{k-d}{y+d})\\
\iff \frac{k-d}{y+d}= \ln (y+d)\\
\iff \frac{k+y}{y+d}  -1 = -1 + \ln (e (y+d))\\
\iff e(k+y)=e(y+d)\ln(e(y+d))\\
\iff e(k+y)=\ln(e(y+d)) e^{\ln(e(y+d))}\\
\iff W_0(e(k+y))=\ln(e(y+d))\\
\iff e^{W_0(e(k+y))-1}-y=d,
\end{align}

where we made use of the Lambert W function, which is the inverse function of \(x\mapsto x e^x\) and has multiple branches; however as \(e(y+d)>0\) 
\(W_0\) is the only real branch which is applicable here, it corresponds to the inverse of \(x\mapsto x e^x\) for \(x>-1\). 
From the form of the maximising value we see, that it is always bigger than \(-y\). Plugging this back onto our
function we find its maximum

\begin{align}\nonumber
&\max_{d\in ]-y,\infty[} (y+d)^{k-d}=e^{(W_0(e(k+y))-1) (k+y)- (W_0(e(k+y))-1)e^{W_0(e(k+y))-1}}\\\nonumber
&=e^{-(k+y) + (k+y)W_0(e(k+y)) + e^{W_0(e(k+y))-1} -((k+y)e)/e}\\\nonumber
&=e^{-2(k+y) + (k+y)W_0((k+y)e)+ \frac{e(k+y)}{eW_0((k+y)e)}}\\
&=e^{(k+y)(-2+W_0((k+y)e) + W_0((k+y)e)^{-1})},
\end{align}
where we repeatedly used \(W_0(x)e^{W_0(x)}=x\). Putting things together we find

\begin{align}
\|\Gamma(B)^k\alpha_{l,c}\|\le (6\beta )^k \|\alpha\| e^{(k+y)(-2+W_0((k+y)e) + W_0((k+y)e)^{-1})}.
\end{align}
Dividing this by \(k!\) and using the lower bound given by Sterling's formula we would like to prove that 

\begin{align}\label{essentialSelfadjointnessSimplifiedSum}
\sum_{k=1}^\infty (6\beta t )^k   e^{k(1-\ln(k))-\frac{1}{2}\ln(k) +(k+y)(-2+W_0((k+y)e) + W_0((k+y)e)^{-1})}<\infty
\end{align}
holds, where we neglected constant factors and the summand \(k=0\) which do not matter for the task at hand. Next we are going
to use an inequality about the growth of \(W_0\) proven in \cite{hoorfar2008inequalities}. For any \(x\ge e\) 
\begin{equation}
W_0(x)\le \ln(x)-\ln( \ln (x)) + \frac{e}{e-1}\frac{\ln (\ln (x))}{\ln (x)}
\end{equation}
holds true. Plugging this into our sum the exponent is bounded from above by

\begin{align}\nonumber
&k(1-\ln(k))-\frac{1}{2}\ln(k) +(k+y)\Big[-1+\ln(k+y) - \ln(1+ \ln (k+y))\\ \nonumber
&\left.+\frac{e}{e-1} \frac{\ln(1+\ln(k+y))}{1+\ln(k+y)} + W_0((k+y)e)^{-1}\right]\\\nonumber
&=-y + k \ln\left(1+\frac{y}{k}\right) + y \ln (k+y) -\frac{1}{2}\ln(k) +\\\nonumber
&(k+y)\left[ \ln (1+\ln(k+y))\frac{1-(e-1)\ln(k+y)}{(e-1)(1+\ln(k+y))} + W_0((k+y)e)^{-1}\right]\\\label{essentialSelfadjointnessExponent}
&\le y \ln (k+y) -\frac{1}{2}\ln(k) + (k+y)W_0((k+y)e)^{-1} +\\\nonumber
&(k+y) \ln (1+\ln(k+y))\frac{1-(e-1)\ln(k+y)}{(e-1)(1+\ln(k+y))} .
\end{align}
Now it is important to notice that the only remaining term that grows faster than linearly in magnitude is the last summand.
This term; however, is negative for large \(k\), as the fraction converges to \(-(e-1)\) for large \(k\), while the double logarithm
in front grows without bounds. So there is a \(k^*\) big enough such that  for all \(k>k^*\) \eqref{essentialSelfadjointnessExponent} 
is smaller than \(- k (\ln(6\beta t) + 1)\), proving that \eqref{essentialSelfadjointnessSimplifiedSum} in fact holds.

\end{proof}



\begin{Thm}\label{Gamma essential selfadjointness}
The operator \(\mathrm{d}\Gamma(B):\mathcal{F}'\rightarrow \mathcal{F}\) is essentially skew adjoint and hence by Stones theorem
 generates a strongly continuous unitary group \(\left( e^{t ~\widehat{\mathrm{d}\Gamma(B)}}\right)_t\), where \(\widehat{\mathrm{d}\Gamma(B)}\) is the closure of 
 \(\mathrm{d}\Gamma(B)\).
\end{Thm}
\begin{proof}
In order to apply Nelson's analytic vector theorem we pick \(C=\mathcal{F}'\). Pick \(\alpha \in\mathcal{F}'\). We need to show that there is \(t>0\) such that
\begin{equation}
\sum_{k=0}^\infty \frac{\|\mathrm{d}\Gamma(B)^k \alpha\|}{k!} t^k <\infty
\end{equation}
holds. This is guaranteed by the last lemma.
\end{proof}

Lastly in this chapter, we will investigate the commutation properties of \(\mathrm{d}\Gamma(B)\) with general creation and annihilation operators.
These properties are the reason we are interested in this operator, they will prove to be very useful in the next chapter.

\begin{Thm}\label{Commutation Gamma}
For \(\psi \in \mathcal{H}\) we have
\begin{equation}
[\mathrm{d}\Gamma(B),a^\# (\psi)]=a^\#(B\psi),
\end{equation}
where \(a^\#\) can be either \(a\) or \(a^*\).
\end{Thm}
\begin{proof}
Because \(\mathrm{d}\Gamma(B)\) is defined as the extension of an operator on \(\mathcal{F}^0\) it suffices to show the desired identity on this space. In order to do so
we first restrict \(\psi\in \text{span}\{\varphi_{n}| n \in \mathbb{Z}\backslash\{0\}\}\). We will first cover the case \(a(\psi)\).  
As a first step we decompose \(\mathrm{d}\Gamma(B)\) into its four parts

\begin{align}
\left[ \mathrm{d}\Gamma(B),a(\psi) \right] = \left[ \mathrm{d}\Gamma(B_{++})
+\mathrm{d}\Gamma(B_{-+})+\mathrm{d}\Gamma(B_{-+})+\mathrm{d}\Gamma(B_{--}),a(\psi) \right],
\end{align}
each of those parts is evaluated directly. We begin with the \(B_{++}\) part, this can be expressed as

\begin{align}
\left[ \mathrm{d}\Gamma(B_{++}),a(\psi) \right] \\
= \sum_{n\in\mathbb{N}} a^*(B_{++}\varphi_n)a(\varphi_n) a(\psi) - \sum_{n\in\mathbb{N}} a(\psi) a^*(B_{++}\varphi_n)a(\varphi_n) \\
=\sum_{n\in\mathbb{N}} \left[ -\langle \psi, B_{++} \varphi_n\rangle a(\varphi_n) +a(\psi) a^*(B_{++}\varphi_n)a(\varphi_n) \right]  \\
- \sum_{n\in\mathbb{N}} a(\psi) a^*(B_{++}\varphi_n)a(\varphi_n).
\end{align}

Let \(\alpha \in \mathcal{F}^0\). Now applying the expression in the last two lines to \(\alpha\) online finitely many elements of the sum in fact contribute.
So we may split the firs sum into two and observe the cancellation between the last two terms. Continuing we find

\begin{align}
\left[ \mathrm{d}\Gamma(B_{++}),a(\psi) \right] \alpha
=-\sum_{n\in\mathbb{N}}  \langle \psi, B_{++} \varphi_n\rangle a(\varphi_n)\alpha\\
=-a\left(\sum_{n\in\mathbb{N}} \langle B_{++}\varphi_n, \psi\rangle  \varphi_n  \right)\alpha
=a\left(\sum_{n\in\mathbb{N}} \langle \varphi_n, B_{++}\psi\rangle  \varphi_n  \right)\alpha\\
=a(B_{++}\psi)\alpha,
\end{align}

where we used \(B^*=-B^*\). Now for a general \(\psi\in\mathcal{H}\) we pick a sequence 
\((\psi_k)_{k\in\mathbb{N}}\subset \text{span}\{\varphi_{n}| n \in \mathbb{Z}\backslash\{0\}\}\)
such that \(\lim_{k\rightarrow \infty} \psi_k = \psi\). Now because of the calculation we have the equality

\begin{equation}
\left[ \mathrm{d}\Gamma(B_{++}),a(\psi_k) \right] \alpha =a(B_{++}\psi_k)\alpha
\end{equation}

for each \(k\in\mathbb{N}\) and hence if a limit exists it also holds in the limit. Now on the right hand side, because
\(a\) is a bounded operator on all of \(\mathcal{F}\) clearly the limit exists and is equal to \(a(B_{++}\psi)\alpha\).
On the left hand side we know \(\mathrm{d}\Gamma(B)\) to be bounded and hence continuous on every \(\mathcal{F}_{m,p}\)
for every \(m,p\in\mathbb{N}\).  Furhtermore since \(\alpha\in\mathcal{F}^0\) there is are \(m',p'\in\mathbb{N}\) such that 
\(\alpha \in \bigobot_{m=0}^{m'}\bigobot_{p=0}^{p'} \mathcal{F}_{m,p}\) holds and hence we can exchange the limit also 
with \(\mathrm{d}\Gamma(B)\) and find

\begin{equation}
\left[ \mathrm{d}\Gamma(B_{++}),a(\psi) \right] \alpha =a(B_{++}\psi)\alpha
\end{equation}

for general \(\psi\in\mathcal{H}\). The final extension of this equation to all \(\alpha \in \mathcal{F}'\) happens via the continuous linear
extension theorem on \(\mathcal{F}_{m,p}\) for each \(m,p\in\mathbb{N}\). The proof in all seven other cases are completely analogous.
Putting thins together again we obtain

\begin{align}
\left[ \mathrm{d}\Gamma(B_{++}),a(\psi) \right] +\left[ \mathrm{d}\Gamma(B_{-+}),a(\psi) \right] \\
+\left[ \mathrm{d}\Gamma(B_{+-}),a(\psi) \right] +\left[ \mathrm{d}\Gamma(B_{--}),a(\psi) \right]  =\\
a(B_{++}\psi)+a(B_{+-}\psi)+a(B_{-+}\psi)+a(B_{--}\psi)\iff \\
\left[ \mathrm{d}\Gamma(B),a(\psi) \right] =a(B\psi)
\end{align}
on all of \(\mathcal{F}'\).

\end{proof}

 

\subsection{Presentation and Proof of the Formula}\label{sec:proof simple formula}

In this chapter we verify the formula for the \(S\)-matrix directly.
For a heuristic derivation in the appendix in section\ref{sec:heuristic construction}


\begin{Thm}\label{sleek_second_quantised_scattering_operator}
For \(A\) such that 
\begin{equation}
\|\id-U^A\|<1.
\end{equation}\label{eq:sleek_scattering}
The second quantized scattering operator fulfils
\begin{equation}\label{eq:sleek_second_quantised_scattering_operator}
S^A= e^{i \varphi^A} e^{\mathrm{d}\Gamma(\ln (U^A))}
\end{equation}
for some phase \(\varphi^A\in\mathbb{R}\), that may depend on the external field \(A\).

\end{Thm}
\begin{proof}
In order to establish this theorem we need to verify that the expression given in \eqref{eq:sleek_scattering} for the scattering operator
 is a well defined object
and fulfils \eqref{lift_condition1} and \eqref{lift_condition2}. Because these conditions uniquely fix the Operator \(S^A\)  up to a phase this suffices as a proof.

Well definedness is established, by theorem \ref{Gamma essential selfadjointness}, because for unitary \(U^A\)
with \(\|1-U^A\|<1\) the power series of the logarithm converges and fulfils
\begin{align}
\|\ln(U^A)\|=\|\ln (1-(1-U^A))\|= \left\| -\sum_{k=1}^\infty \frac{(1-U^A)^k}{k} \right\|\\
 \le   \sum_{k=1}^\infty \frac{\|1-U^A\|^k}{k}=-\ln(1-\|1-U^A\|)
\end{align}
implying that the power series of the logarithm around the identity is a well defined map from the one particle operators of norm less than
one to the bounded one particle operators. Moreover this operator fulfils \([\ln (U^A)]^*=\ln (U^A)^*= \ln (U^A)^{-1}=-\ln (U^A)\), so 
\(\mathrm{d}\Gamma(\ln U^A)\) is a well defined unbounded operator that is essentially self adjoint on the finite particle sector of Fockspace \(\mathcal{F}'\).


Let \(\varphi\in \mathcal{H}\), for any \(k\in \mathbb{N}_0\) we see applying the commutation relation of \(\mathrm{d}\Gamma\):
\begin{multline*}
\mathrm{d}\Gamma(\ln U) \sum_{l=0}^k \binom{k}{l} a^\# \left(\left(\ln U\right)^l \varphi \right) \left(\mathrm{d}\Gamma(\ln U)\right)^{k-l} = \\
\sum_{l=0}^k \binom{k}{l} a^\# \left(\left(\ln U\right)^{l+1} \varphi \right) \left(\mathrm{d}\Gamma(\ln U)\right)^{k-l}\\
+\sum_{l=0}^k \binom{k}{l} a^\# \left(\left(\ln U\right)^l \varphi \right) \left(\mathrm{d}\Gamma(\ln U)\right)^{k-l+1}\\
= \sum_{b=0}^{k+1} \left( \binom{k}{b-1} + \binom{k}{b}\right) a^\#\left( (\ln U)^b \varphi\right) \left( \mathrm{d}\Gamma(\ln U)\right)^{k+1-b}\\
=\sum_{b=0}^{k+1}  \binom{k+1}{b}  a^\#\left( (\ln U)^b \varphi\right) \left( \mathrm{d}\Gamma(\ln U)\right)^{k+1-b},
\end{multline*}
so we see that for \(k\in\mathbb{N}_0\)
\begin{equation}
\left(\mathrm{d}\Gamma(\ln U)\right)^k a^\# (\varphi) = \sum_{b=0}^{k}  \binom{k}{b}  a^\#\left( (\ln U)^b \varphi\right) \left( \mathrm{d}\Gamma(\ln U)\right)^{k-b}
\end{equation}
holds. Let \(\alpha \in \mathcal{F}'\). Using what we just obtained, we conclude
\begin{multline*}
e^{\mathrm{d}\Gamma(\ln U)}a^\#(\varphi) = \sum_{k=0}^\infty \frac{1}{k!} \left(\mathrm{d}\Gamma(\ln U)\right)^k a^\# (\varphi)\alpha\\
=\sum_{k=0}^\infty \frac{1}{k!}  \sum_{b=0}^{k}  \binom{k}{b}  a^\#\left( (\ln U)^b \varphi \right) \left( \mathrm{d}\Gamma(\ln U)\right)^{k-b}\alpha\\
\overset{*}{=}\sum_{c=0}^\infty \sum_{l=0}^\infty \frac{1}{c! l!} a^\#\left( (\ln U)^c \varphi \right) \left( \mathrm{d}\Gamma(\ln U)\right)^{l}\alpha\\
=a^\#\left( e^{\ln U} \varphi \right) e^{\mathrm{d}\Gamma( \ln U)}\alpha
=a^\#\left( U \varphi \right) e^{\mathrm{d}\Gamma( \ln U)}\alpha.
\end{multline*}
For the marked equality changing oder of summation is justified, because by the bounds
 \(\|a^\#((\ln U)^c \varphi)\|\le \|\ln U\|^c\) and  lemma \ref{Gamma exponential bound} the sum obtained by changing the order
 of summands converges absolutely.
Clearly multiplying the second quantised operator by an additional phase as in 
\eqref{sleek_second_quantised_scattering_operator} does not influence this calculation.
\end{proof}

\noch{decide whether to use or delete this part.}
As a preparation for calculating the vacuum polarisation current we proof the following 
\begin{Lemma}\label{G_kommutator}
Let \(P_k,P_l\in Q\) then the following holds
\begin{equation}
\left[G(P_k),G(P_l)\right]= 
\tr\left(P_{\stackrel{k}{-+}}P_{\stackrel{l}{+-}}\right)
-\tr\left(P_{\stackrel{l}{-+}}P_{\stackrel{k}{+-}}\right) 
+G\left(\left[P_k,P_l\right]\right)
.\end{equation}
\end{Lemma}
For a proof of this lemma let \(P_k,P_l \in Q\), we compute
\begin{align*}
&\left[G(P_k),G(P_l)\right]\stackrel{\eqref{G commutator}}{=}\\
&=\sum_{n,b\in\mathbb{N}} \left[ a^*\left(P_k\varphi_n\right) a(\varphi_n), a^*\left(P_l\varphi_b\right)a(\varphi_n)\right]\\
&-\sum_{-b,n\in\mathbb{N}}\left[a^*\left(P_k\varphi_n\right)a(\varphi_n), a(\varphi_b) a^*\left(P_l\varphi_b\right)\right]\\
&-\sum_{-n,b\in\mathbb{N}}\left[a(\varphi_n)a^*\left(P_k\varphi_n\right),a^*\left(P_l\varphi_b\right)a(\varphi_b)\right]\\
&+\sum_{n,b\in\mathbb{N}}\left[ a(\varphi_n)a^*\left(P_k\varphi_n\right), a(\varphi_b)a^*\left(P_l\varphi_b\right)\right]\\
&=\sum_{n,b\in\mathbb{N}} \left(a^*\left(P_k\varphi_n\right)\left<\varphi_n,P_l\varphi_b\right>a(\varphi_b)-a^*\left(P_l\varphi_b\right) \left<\varphi_b,P_k\varphi_n\right>a(\varphi_n) \right)\\
&-\sum_{-b,n\in\mathbb{N}}\left( - \left<\varphi_b,P_k \varphi_n\right>a(\varphi_n)a^*\left(P_l\varphi_b\right) + a(\varphi_b) a^*\left(P_k\varphi_n\right)\left<\varphi_n,P_l\varphi_b\right>\right)\\
&-\sum_{-n,b\in\mathbb{N}} \left( - \left< \varphi_n,P_l\varphi_b\right> a^*\left(P_k\varphi_n\right) a(\varphi_b) + a^*\left(P_l\varphi_b\right)a(\varphi_n)\left<\varphi_b,P_k\varphi_n\right>\right)\\
&+\sum_{n,b\in -\mathbb{N}} \left(a(\varphi_n) \left< \varphi_b,P_k\varphi_n\right>a^*\left(P_l\varphi_b\right)-a(\varphi_b)\left<\varphi_n,P_l\varphi_b\right> a^*\left(P_k\varphi_n\right)\right)\\
&=\sum_{b\in\mathbb{N}} a^*\left(P_k P_{\stackrel{l}{++}}\varphi_b\right)a(\varphi_b) - \sum_{n\in\mathbb{N}}a^*\left(P_l P_{\stackrel{k}{++}}\varphi_n\right)a(\varphi_n)\\
&+\sum_{n\in\mathbb{N}}a(\varphi_n)a^*\left(P_l P_{\stackrel{k}{-+}}\varphi_n\right) - \sum_{-b\in\mathbb{N}} a(\varphi_b)a^*\left(P_k P_{\stackrel{l}{+-}}\varphi_b\right)\\
&+\sum_{b\in\mathbb{N}}a^*\left(P_k P_{\stackrel{l}{-+}}\varphi_b\right)a(\varphi_b)-\sum_{-n\in\mathbb{N}}a^*\left(P_l P_{\stackrel{k}{+-}}\varphi_n\right) a(\varphi_n)\\
&+\sum_{-n\in\mathbb{N}}a(\varphi_n)a^*\left(P_l P_{\stackrel{k}{--}}\varphi_n\right) - \sum_{-b \in \mathbb{N}} a(\varphi_b)a^*\left(P_k P_{\stackrel{l}{--}}\varphi_b\right)\\
=&\sum_{n\in\mathbb{N}} a^*\left(P_k P_l \varphi_n \right) a(\varphi_n) - \sum_{n\in\mathbb{N}} a^*\left(P_l P_{\stackrel{k}{++}} \varphi_n \right) a(\varphi_n)\\
&+\tr \left( P_{\stackrel{l}{+-}} P_{\stackrel{k}{-+}}\right) - \sum_{n\in\mathbb{N}} a^*\left( P_l P_{\stackrel{k}{-+}} \varphi_n\right)a(\varphi_n)\\
&-\tr \left( P_{\stackrel{l}{-+}} P_{\stackrel{k}{+-}}\right) + \sum_{-b\in\mathbb{N}} a(\varphi_b) a^*\left(P_l P_{\stackrel{k}{+-}} \varphi_b\right)\\
&+\sum_{-b\in\mathbb{N}} a(\varphi_b) a^*\left( P_l P_{\stackrel{k}{--}}\varphi_b\right) - \sum_{-b\in\mathbb{N}} a(\varphi_b) a^*\left( P_k P_l \varphi_b\right)\\
&=\tr \left( P_{\stackrel{l}{+-}} P_{\stackrel{k}{-+}}\right)
-\tr \left( P_{\stackrel{l}{-+}} P_{\stackrel{k}{+-}}\right)\\
&+\sum_{n\in\mathbb{N}} a^*\left(\left[P_k ,P_l\right] \varphi_n \right) a(\varphi_n)
+\sum_{-b\in\mathbb{N}} a(\varphi_b)a^*\left(\left[P_l ,P_k\right] \varphi_b \right) \\
&=\tr \left( P_{\stackrel{l}{+-}} P_{\stackrel{k}{-+}}\right)
-\tr \left( P_{\stackrel{l}{-+}} P_{\stackrel{k}{+-}}\right)
+G\left(\left[P_k,P_l\right]\right)
\end{align*}
\qed

\begin{Def}
For \(k\in\mathbb{N}_0\), \(X,Y\in \mathcal{B}(\mathcal{H})\) the nested commutator \([X,Y]_k\) is defined inductively as
\begin{align*}
[X,Y]_0&:= Y\\
[X,Y]_{k+1}&:=[X,[X,Y]_{k}] \quad \forall k\in\mathbb{N}_0.
\end{align*}
\end{Def}

\begin{Lemma}\label{nested_kommuted_G}
For \(m\in\mathbb{N}\) and \(B,C \in Q\) the following holds
\begin{multline}
\left[ G(B),G(C)\right]_m=  \tr\left(P_-BP_+[B,C]_{m-1}\right) - \tr\left(P_+BP_-[B,C]_{m-1}\right)\\
+G\left([B,C]_m\right) .
\end{multline}
\end{Lemma}
\textbf{Proof:} Proof by Induction is the first thing that comes to mind, looking at the claim. Indeed, \(m=1\) is the consequence
of the lemma \ref{G_kommutator}. For \(m\) general we have

\begin{multline}
\left[ G(B),G(C)\right]_{m+1}
=\left[ G(B),\left[ G(B),G(C)\right]_{m}\right]\\
\stackrel{\text{ind.hyp.}}{=}\left[ G(B), \tr\left(P_-BP_+[B,C]_{m-1}\right) - \tr\left(P_+BP_-[B,C]_{m-1}\right)
+G\left([B,C]_m\right) \right]\\
=\left[ G(B),G\left([B,C]_m\right) \right]\\
\stackrel{\text{lemma } \ref{G_kommutator}}{=} 
\tr\left(P_- B P_+ [B,C]_m\right)
-\tr\left(P_+BP_- [B,C]_m \right) 
+G\left(\left[B,[B,C]_m\right]\right)\\
=
\tr\left(P_- B P_+ [B,C]_m\right)
-\tr\left(P_+BP_- [B,C]_m \right) 
+G\left([B,C]_{m+1}\right)
\end{multline}
\qed 

\begin{Lemma}\label{lemma:derivativeJ}
For external potentials \(A, X\) small enough the derivatives of the scattering operator can be computed to fulfil
\begin{align}\label{eq:derivativeS1}
\partial_\varepsilon |_{\varepsilon=0} e^{G \ln U^{A+\varepsilon X}} &= e^{G \ln U^A} j_A^0(X) + e^{G \ln U^A} G( (U^A)^{-1} \partial_{\varepsilon} U^{A+\varepsilon X})\\
\partial_\varepsilon |_{\varepsilon=0} e^{-G \ln U^{A+\varepsilon X}} &=- e^{-G \ln U^A} j_A^0(X) + G( \partial_{\varepsilon} \left(U^{A+\varepsilon X}\right)^{-1} U^A ) e^{-G \ln U^A},
\end{align}
with 
\begin{multline}\label{def:vacuumExpectationCurrent}
j^0_A(X):= \sum_{l\in\mathbb{N}_0} \frac{(-1)^{l+1}}{(l+2)!} \left(\tr P_- \ln U^A P_+ \left[ \ln U^A, \partial_\varepsilon \ln U^{A+\varepsilon X}\right]_{l}\right.\\
\left. - \tr P_+ \ln U^A P_- \left[ \ln U^A, \partial_\varepsilon \ln U^{A+\varepsilon X}\right]_{l} \right).
\end{multline}
\end{Lemma}
\textbf{Proof:} We start out by employing Duhamel's and Hadamard's formulas. \todo{ref!! + restrictions, something better than 
 \href{https://s3.amazonaws.com/academia.edu.documents/46627661/CBH.pdf?AWSAccessKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1517999839&Signature=m\%2FGNTMS\%2FNAH7ioWII76ZlULcCRY\%3D&response-content-disposition=inline\%3B\%20filename\%3DCrib_Notes_on_Campbell-Baker-Hausdorff_e.pdf}{this}}
These are

\begin{equation}\label{Duhamel}
\partial_{\alpha}\left. e^{Y+\alpha X}\right|_{\alpha=0} = \int_0^1 d t e^{(1-t) Y} X e^{t Y}\tag{Duhamel's formula}
\end{equation}

and
\begin{equation}\tag{Hadamard's formula}\label{Hadamard}
e^{X}Ye^{-X}=\sum_{k=0}^\infty \frac{1}{k!} [X,Y]_k.
\end{equation}

So one gets

\begin{align}\label{proof:duhamelApplied}
\partial_\varepsilon |_{\varepsilon=0} e^{G \ln U^{A+\varepsilon X}} &= \int_0^1 d z e^{(1-z) G \ln U^A} \partial_\varepsilon |_{\varepsilon=0} G \ln U^{A+\varepsilon X} e^{z G \ln U^A}\\\notag
&=e^{G \ln U^A} \int_0^1 d z \sum_{l\in\mathbb{N}_0} \frac{1}{l!} \left[ - z G \ln U^A, \partial_\varepsilon |_{\varepsilon=0} G \ln U^{A+\varepsilon X} \right]_l\\\notag
&=e^{G \ln U^A} \int_0^1 d z \sum_{l\in\mathbb{N}_0} \frac{(-z)^l}{l!} \partial_\varepsilon |_{\varepsilon=0} \left[  G \ln U^A,  G \ln U^{A+\varepsilon X} \right]_l.
\end{align}
At this point we see that for \(l=0\) the summand vanishes. For all other values of \(l\) we use lemma \ref{nested_kommuted_G}, yielding
\begin{multline}
\partial_\varepsilon |_{\varepsilon=0} e^{G \ln U^{A+\varepsilon X}}= 
e^{G \ln U^A} \int_0^1 d z \sum_{l\in\mathbb{N}} \frac{(-z)^l}{l!} \partial_\varepsilon |_{\varepsilon=0} \left( G\left(\left[ \ln U^A, \ln U^{A+\varepsilon X}\right]\right) \right.\\
+\tr P_- \ln U^A P_+ \left[ \ln U^A, \partial_\varepsilon |_{\varepsilon=0} \ln U^{A+\varepsilon X}\right]_{l-1}\\
\left. - \tr P_+ \ln U^A P_- \left[ \ln U^A, \partial_\varepsilon |_{\varepsilon=0} \ln U^{A+\varepsilon X}\right]_{l-1}\right).
\end{multline}

The last two terms together result in the first term of \eqref{eq:derivativeS1} after performing the integration and shifting the summation
index. For the first term we will use linearity and continuity of \(G\)\todo{contiuity of G!!}   ~and use the same identities backwards to give

\begin{multline}
e^{G \ln U^A} \int_0^1 d z \sum_{l\in\mathbb{N}} \frac{(-z)^l}{l!} \partial_\varepsilon |_{\varepsilon=0} G\left(\left[ \ln U^A, \ln U^{A+\varepsilon X}\right]\right) \\
=e^{G \ln U^A}  G\left( \int_0^1 d z \sum_{l\in\mathbb{N}} \frac{1}{l!}  \left[ -z \ln U^A,\partial_\varepsilon|_{\varepsilon=0} \ln U^{A+\varepsilon X}\right]\right) \\
=e^{G \ln U^A}  G\left(e^{- \ln U^A} \int_0^1 d z e^{ \ln U^A} e^{-z \ln U^A}\partial_\varepsilon|_{\varepsilon=0} \ln U^{A+\varepsilon X} e^{z \ln U^A}\right) \\
=e^{G \ln U^A}  G\left(e^{ \ln \left(U^A\right)^{-1}} \partial_\varepsilon|_{\varepsilon=0} e^{ \ln U^{A+\varepsilon X}} \right) \\
=e^{G \ln U^A}  G\left(\left(U^A\right)^{-1} \partial_\varepsilon|_{\varepsilon=0}U^{A+\varepsilon X} \right).
\end{multline}
Putting things together results in the first equality we wanted to prove. For the second one the computation is completely analogous, except for after applying Duhamel's formula as in \eqref{proof:duhamelApplied} we substitute \(u=1-z\). The minus sign in front of the first term then arises by the chain rule, where as the second term does not share the sign change with the first, since we have to revert the use of the chain rule in the second half of the calculation when we apply  \eqref{Duhamel} backwards. \qed

\begin{Def}
We use Bogoliubov's formula to define the vacuum expectation value of the current \todo{ref!!}
\begin{equation}
j_A(F) = i \partial_{\varepsilon}\left. \langle \Omega, {S^{A} }^* S^{A+\varepsilon F}\Omega \rangle \right|_{\varepsilon=0}.
\end{equation}
\end{Def}



\begin{Thm}\label{thm:CurrentExact}
The vacuum expectation value of the current of the scattering operator takes the form
\begin{align*}
j_A(F)&=- \partial_{\varepsilon} \left. \varphi(A+\varepsilon F) \right|_{\varepsilon=0}\\
-2\int_0^1 &d z (1-z)  \Im \tr\left(P_+ \ln U^A P_- e^{ -z \ln U^A} \partial_{\varepsilon} \left. \ln U^{A+\varepsilon F}\right|_{\varepsilon=0} e^{ z \ln U^A}\right)\\
&=- \partial_{\varepsilon} \left.\varphi(A+\varepsilon F) \right|_{\varepsilon=0}\\
  - 2\Im \sum_{k=0}^\infty&\frac{(-1)^k}{(k+2)!}  \tr \left( P_+ \ln U^A P_-\left[\ln U^A,\left.\partial_{\varepsilon}\ln U^{A+\varepsilon F} \right|_{\varepsilon=0}\right]_{k}\right) 
\end{align*}
\end{Thm}
\textbf{Proof:} By theorem \ref{sleek_second_quantised_scattering_operator} and abbreviating
\(\varphi(A)= \sum_{n\in\mathbb{N}} \frac{C_n(A)}{n!} \)we see that the current can be written in the form

\begin{multline}\label{sleek_current_calc1}
j_A(F) = i \partial_{\varepsilon}\left. \langle \Omega, {S^{A} }^* S^{A+\varepsilon F}\Omega \rangle \right|_{\varepsilon=0}\\
=i \partial_{\varepsilon}\left. \langle \Omega, e^{-i\varphi(A)} e^{-G(\ln (U^A))} 
e^{i\varphi(A+\varepsilon F)}  e^{G(\ln (U^{A+\varepsilon F}))} \Omega\rangle \right|_{\varepsilon=0}\\
=- \partial_{\varepsilon} \left. \varphi(A+\varepsilon F) \right|_{\varepsilon=0}
+i\langle \Omega,\partial_{\varepsilon}\left.  e^{-G(\ln (U^A))} 
e^{G(\ln (U^{A+\varepsilon F}))} \Omega\rangle \right|_{\varepsilon=0},
\end{multline}
so the first summand works out just as claimed. For the second summand we employ lemma \ref{lemma:derivativeJ} and note that the vacuum expectation value of \(G\) vanishes no matter its argument.

\begin{multline}\label{sleek_current_calc3}
i\langle \Omega,\partial_{\varepsilon}\left.  e^{-G(\ln (U^A))} 
e^{G(\ln (U^{A+\varepsilon F}))} \Omega\rangle \right|_{\varepsilon=0}\\
=-i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{(-1)^k}{(k+2)!} 
 \tr\left(P_- \ln U^A P_+[\ln U^A ,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
 +i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{(-1)^k}{(k+2)!}  \tr\left(P_+ \ln U^A P_-[\ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\ 
\end{multline}

In order to apply Hadamard's formula once again in the opposite direction, we introduce two auxiliary integrals.
The second term then becomes

\begin{multline}\label{sleek_current_calc4}
 i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{(-1)^k}{(k+2)!}  \tr\left(P_+ \ln U^A P_-[\ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
= i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{(-1)^k}{k!} \int_0^1 d t \int_0^1 s^k t^{k+1}
\tr\left(P_+ \ln U^A P_-[\ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
= i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{1}{k!} \int_0^1 d t \int_0^1 ds\ t
\tr\left(P_+ \ln U^A P_-[ -t s \ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
= i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{1}{k!} \int_0^1 d z \int_z^1 ds\ 
\tr\left(P_+ \ln U^A P_-[ -z \ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
= i  \partial_{\varepsilon} \left.\sum_{k=0}^\infty \frac{1}{k!} \int_0^1 d z (1-z)
\tr\left(P_+ \ln U^A P_-[ -z \ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
= i  \partial_{\varepsilon} \left. \int_0^1 d z (1-z) 
\tr\left(P_+ \ln U^A P_- \sum_{k=0}^\infty \frac{1}{k!} [ -z \ln U^A,\ln U^{A+\varepsilon F} ]_{k}\right) \right|_{\varepsilon=0}\\
\stackrel{\eqref{Hadamard}}{=} i  \partial_{\varepsilon} \left. \int_0^1 d z (1-z) 
\tr\left(P_+ \ln U^A P_- e^{ -z \ln U^A}\ln U^{A+\varepsilon F} e^{ z \ln U^A}\right) \right|_{\varepsilon=0}\\
=i  \int_0^1 d z (1-z) 
\tr\left(P_+ \ln U^A P_- e^{ -z \ln U^A} \partial_{\varepsilon} \left. \ln U^{A+\varepsilon F}\right|_{\varepsilon=0} e^{ z \ln U^A}\right) .
\end{multline}

The calculation for the first term of \eqref{sleek_current_calc3} is identical.
At this point we notice that \eqref{sleek_current_calc4} and the term where the 
projectors are exchanged are complex conjugates of one another. So summarising we find
\begin{multline*}
j_A(F)=- \partial_{\varepsilon} \left. \varphi (A+\varepsilon F) \right|_{\varepsilon=0}\\
-2\int_0^1 d z (1-z)  \Im \tr\left(P_+ \ln U^A P_- e^{ -z \ln U^A} \partial_{\varepsilon} \left. \ln U^{A+\varepsilon F}\right|_{\varepsilon=0} e^{ z \ln U^A}\right).
\end{multline*}
\qed

\begin{Thm}
Independent of the phase that is used to correct the scattering operator the following formula holds true for any 
 four potentials \(A,F,H\), with \(A\) small enough so that the relevant series converge.
\begin{multline}
\partial_\varepsilon |_{\varepsilon=0} ( j_{A+\varepsilon H} (F)-j_{A+\varepsilon F}(H)) = \\
2 \Im \tr \left(P_+ \left(U^A\right)^{-1} \partial_{\varepsilon}|_{\varepsilon=0} U^{A+\varepsilon F} P_-\left(U^A\right)^{-1} \partial_{\delta}|_{\delta=0} U^{A+\delta H}\right)
\end{multline}
\end{Thm}
\textbf{Proof:} We compute \(\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon F}(H) \). 

\begin{align*}
&-i\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon H}(F)=\\
&\partial_\varepsilon |_{\varepsilon=0} \partial_\delta |_{\delta=0} \langle \Omega, e^{i\varphi(A+\varepsilon H + \delta F)-i\varphi(A+\varepsilon H)} e^{-G \ln U^{A+\varepsilon H}} e^{G \ln U^{A+\varepsilon H + \delta F}}\Omega \rangle\\
\end{align*}

We first act with the derivative with respect to \(H\), fixing \(F\).

\begin{align*}
&-i\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon H}(F)=\\
&\partial_\delta |_{\delta=0}   i(\partial_\varepsilon |_{\varepsilon=0}\varphi(A+\varepsilon H + \delta F)-\partial_\varepsilon |_{\varepsilon=0}\varphi(A+\varepsilon H ))e^{i\varphi(A + \delta F)-i\varphi(A)} \\
&\langle \Omega, e^{-G \ln U^{A}} e^{G \ln U^{A + \delta F}}\Omega \rangle\\
&+\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)} \langle \Omega
\partial_\varepsilon |_{\varepsilon=0} e^{-G \ln U^{A+\varepsilon H}} e^{G \ln U^{A + \delta F}}\Omega \rangle\\
&+\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)} 
 \langle \Omega e^{-G \ln U^{A}} \partial_\varepsilon |_{\varepsilon=0}e^{G \ln U^{A+\varepsilon H + \delta F}}\Omega \rangle
\end{align*}

In computing further one can notice a few cancellations. For the first summand the first factor vanishes if \(\delta\) is set to zero, so the only 
the first summand in the product rule will not vanish. For the second and third summand we will use lemma \ref{lemma:derivativeJ},
giving

\begin{align*}
&-i\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon H}(F)=\\
&\partial_\delta |_{\delta=0}   i\partial_\varepsilon |_{\varepsilon=0}\varphi(A+\varepsilon H + \delta F)\\
&-\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)}  j^0_{A}(H) 
\langle \Omega, e^{-G \ln U^{A}} e^{G \ln U^{A + \delta F}}\Omega \rangle \\
&+\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)} \langle \Omega,
 G \left(\partial_\varepsilon |_{\varepsilon=0} \left(U^{A+\varepsilon H}\right)^{-1} U^A\right) e^{-G \ln U^{A}} e^{G \ln U^{A + \delta F}}  \Omega \rangle\\
&+\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)} j^0_{A+\delta F}(H)
\langle \Omega, e^{-G \ln U^{A}} e^{G \ln U^{A+ \delta F}}\Omega \rangle\\
&+\partial_\delta |_{\delta=0} e^{i\varphi(A + \delta F)-i\varphi(A)} 
\langle \Omega, e^{-G \ln U^{A}} e^{G \ln U^{A+ \delta F}}G\left( \left(U^{A+\delta F}\right)^{-1}\partial_\varepsilon |_{\varepsilon=0} U^{A+\varepsilon H + \delta F} \right) \Omega \rangle.
\end{align*}

Now there are a few further simplifications to appreciate: since \(\langle \Omega, G \Omega \rangle=0\), in the third and last summand only the derivatives with respect to \(\delta\) which produce by lemma \ref{lemma:derivativeJ} another factor of \(G\)  will contribute to the sum.
 For the other summands except for the first we can spot the appearance of \(j^0\). Respecting all this results in

\begin{align*}
&-i\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon H}(F)=
i\partial_\delta |_{\delta=0}   \partial_\varepsilon |_{\varepsilon=0}\varphi(A+\varepsilon H + \delta F)\\
&-i\partial_\delta |_{\delta=0}\varphi(A + \delta F)j^0_{A}(H) -  j^0_{A}(H) j^0_A(F)\\
&+\langle \Omega,
 G \left(\partial_\varepsilon |_{\varepsilon=0} \left(U^{A+\varepsilon H}\right)^{-1} U^A\right) G\left( \left(U^{A}\right)^{-1}\partial_\delta |_{\delta=0} U^{A +\delta F} \right)  \Omega \rangle\\
&+i\partial_\delta |_{\delta=0} \varphi(A + \delta F) j^0_{A}(H)
+\partial_\delta |_{\delta=0}  j^0_{A+\delta F}(H)
+ j^0_{A}(H)j^0_A(F)\\
&+\langle \Omega, G\left( \left(U^{A}\right)^{-1}\partial_\delta |_{\delta=0} U^{A + \delta F} \right) G\left( \left(U^{A}\right)^{-1}\partial_\varepsilon |_{\varepsilon=0} U^{A+\varepsilon H} \right) \Omega \rangle.
\end{align*}

A few more terms cancel in the second and fourth line, also since \(\partial_\varepsilon |_{\varepsilon=0} \left(U^{A+\varepsilon H}\right)^{-1} U^{A+\varepsilon H}=0\) we can combine the two products of \(G\) into a commutator:

\begin{align*}
&-i\partial_\varepsilon |_{\varepsilon=0} j_{A+\varepsilon H}(F)=
i\partial_\delta |_{\delta=0}   \partial_\varepsilon |_{\varepsilon=0}\varphi(A+\varepsilon H + \delta F)\\
&+\partial_\delta |_{\delta=0}  j^0_{A+\delta F}(H)\\
&+\langle \Omega, \left[G\left( \left(U^{A}\right)^{-1}\partial_\delta |_{\delta=0} U^{A + \delta F} \right), G\left( \left(U^{A}\right)^{-1}\partial_\varepsilon |_{\varepsilon=0} U^{A+\varepsilon H} \right)\right] \Omega \rangle.
\end{align*}

So we can once again apply lemma \ref{G_kommutator}, which results in exactly right hand side of the equation
we claimed to produce in the statement of this theorem. So all that is left is to recognise that one can combine
the first two summands into \(-i \partial_{\varepsilon} j_{A+\varepsilon H} (F)\), which is a direct consequence
of theorem \ref{thm:CurrentExact}.\qed

\subsection{Quantitative Estimates}
\noch{probably this part cannot be made rigorous. Decide whether to keep it as heuristics}
Since we do not only want to give an expression for the time evolution operator, but also give bounds on the numerical errors
which are due to truncate the occurring series we need to look at these series a little closer. The series involve powers of the 
second quantisation operator \(G\), so we start by examining these in greater depth. In order to do so we define an object 
closely related to \(G\).

\begin{Def}
\begin{multline}\label{def:L}
L: \{M\subset B(\mathcal{H})\mid |M|<\infty\} \times \{M\subset B(\mathcal{H})\mid |M|<\infty\} \rightarrow B(\mathcal{F})\\
L(\{A_1,\dots, A_c\},\{ B_1,\dots ,B_m\}):= \prod_{l=1}^m a(\varphi_{-k_l}) \\
\prod_{l=1}^c a^*(A_l \varphi_{n_l}) \prod_{l=1}^m a^*(B_l \varphi_{-k_l}) \prod_{l=1}^c a(\varphi_{n_l}),
\end{multline}
where for notational reasons we chose to list the occurring one-particle operators in a specific order; however, 
the order does not matter, since commutation of the relevant creation and annihilation operators always results an 
overall factor of one.
\end{Def}

Since this operator \(L\) occurs when computing powers of \(G\) we compute is product with some \(G\) with 
the following 

\begin{Lemma}\label{lem:Ntimes1} For any \(a,b,\in\mathbb{N}_0\) and apropriate one particle operators \(A_k, B_l, C\) for \(1\le k\le a\), \(1\le l\le b\) we have the following equality
\begin{align}
&L\Big(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\Big)G(C) =\\\label{Ntimes1:simplyAdd1}
 &(-1)^{a+b} L\Big(\bigcup_{l=1}^a \{A_l\}\cup \{C\}; \bigcup_{l=1}^b \{B_l\}\Big) \\\label{Ntimes1:simplyAdd2}
 &+(-1)^{a+b+1} L\Big(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\cup \{C\} \Big) \\\label{Ntimes1:n+1atEnd1}
&+ \sum_{f=1}^a  L\Big(\bigcup_{\stackrel{l=1}{l\neq f}}^a \{A_l\}\cup \{A_fP_+C \}; \bigcup_{l=1}^b \{B_l\}\Big) \\\label{Ntimes1:n+1atBeginning1}
&+\sum_{f=1}^a
 L\Big(\bigcup_{\stackrel{l=1}{f\neq l}}^a \{A_l\}\cup \{- CP_- A_f\}; \bigcup_{l=1}^b \{B_l\}\Big)\\\label{Ntimes1:n+1atEnd2}
& -\sum_{f=1}^a L\Big(\bigcup_{\stackrel{l=1}{f\neq l}}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\cup \{A_f P_+ C\}\Big)\\\label{Ntimes1:n+1atBeginning2}
&+ \sum_{f=1}^b L\Big(\bigcup_{l=1}^a \{A_l\}; \bigcup_{\stackrel{l=1}{l\neq f}}^b \{B_l\}\cup \{-CP_- B_f\}\Big)\\\label{Ntimes1:TrTerm}
&+ (-1)^{a+b+1} \sum_{f=1}^a \tr \Big(P_+ C P_- A_f\Big) L\Big(\bigcup_{\stackrel{l=1}{l \neq f}}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\Big)\\\label{Ntimes1:middle1}
&+ (-1)^{a+b+1} \sum_{\stackrel{f_1,f_2=1}{f_1\neq f_2}}^a L\Big(\bigcup_{\stackrel{l=1}{l\neq f_1,f_2}}^a \{A_l\}\cup \{-A_{f_2} P_+ C P_- A_{f_1}\}; \bigcup_{l=1}^b \{B_l\}\Big)\\\label{Ntimes1:middle2}
&+(-1)^{a+b+1} \sum_{f=1}^b \sum_{g=1}^a L\Big(\bigcup_{\stackrel{l=1}{l\neq g}}^a \{A_l\}; \bigcup_{\stackrel{l=1}{l\neq f}}^b \{B_l\}\cup \{-A_g P_+ C P_- B_f\}\Big).
\end{align}
\end{Lemma}
{\bfseries Proof:}  The proof of this equality is a rather long calculation, where \eqref{def:L} is used repeatedly. We break up the calculation into 
several parts. Let us start with

\begin{multline}
L\left(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\right) L(C;)=\\
\prod_{l=1}^b a(\varphi_{-k_l}) \prod_{l=1}^a a^*(A_l \varphi_{n_l}) \prod_{l=1}^b a^*(B_l \varphi_{-k_l}) \prod_{l=1}^a a(\varphi_{n_l}) a^*(C \varphi_m) a(\varphi_m).
\end{multline}

We (anti)commute the creation operator involving \(C\) to its place at the end of the second product, after that the term
will be normally ordered and can be rephrased in terms of \(L\)s. During the commutation the creation operator
in question can be picked up by any of the annihilation operators in the rightmost product. For each term where that happens
we can perform the sum over the basis of \(\mathcal{H}^-\) related to the annihilation operator whose anticommutator triggered.
After this sum the corresponding term is also normally ordered and can be rephrased in terms of an \(L\) after some 
reshuffling which may only produce signs. So performing these steps we get

\begin{multline}
L\left(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\right) L(C;)=\\
\sum_{f=a}^1 (-1)^{a-f} \prod_{l=1}^b a(\varphi_{-k_l}) \prod_{l=1}^{f-1} a^*(A_l \varphi_{n_l}) a^*(A_fP_+C\varphi_m)\\
 \prod_{l=f+1}^a a^*(A_l \varphi_{n_l}) \prod_{l=1}^b a^*(B_l \varphi_{-k_l}) \prod_{\stackrel{l=1}{l\neq f}}^a a(\varphi_{n_l}) a(\varphi_m)\\
+ L\left(\bigcup_{l=1}^a \{A_l\} \cup \{C\}; \bigcup_{l=1}^b \{B_l\}\right)\\
=\sum_{f=1}^a  L\left(\bigcup_{\stackrel{l=1}{l \neq f}}^a \{A_l\} \cup \{A_f P_+ C\}; \bigcup_{l=1}^b \{B_l\}\right)\\
+ L\left(\bigcup_{l=1}^a \{A_l\} \cup \{C\}; \bigcup_{l=1}^b \{B_l\}\right).
\end{multline}

Now the remaining case is more laborious, that is why we will split off and treat some of the appearing terms separately. 
We start off analogous to before 

\begin{multline}
L\left(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\right) L(;C)=\\
\prod_{l=1}^b a(\varphi_{-k_l}) \prod_{l=1}^a a^*(A_l \varphi_{n_l}) \prod_{l=1}^b a^*(B_l \varphi_{-k_l}) \prod_{l=1}^a a(\varphi_{n_l})a(\varphi_{-m}) a^*(C \varphi_{-m}).
\end{multline}

This time we need to (anti)commute the rightmost annihilation operator all the way to the end of the first product and the creation operator to the end of the second but last product. So there will be several qualitatively different terms. From the first step alone we get
\begin{align}\notag
L\left(\bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\right) L(;C)&=\\\notag
(-1)^{a}\sum_{f=b}^1 (-1)^{b-f} \prod_{l=1}^b a(\varphi_{-k_l}) &\prod_{l=1}^a a^*(A_l \varphi_{n_l}) \prod_{\stackrel{l=1}{l\neq f}}^b a^*(B_l \varphi_{-k_l})\\ \label{Ntimes1 term 1}
& \prod_{l=1}^a a(\varphi_{n_l}) a^*(C P_- B_f \varphi_{-k_f})\\\notag
+(-1)^{a+b}\sum_{f=a}^1 (-1)^{b-f} \prod_{l=1}^b a(\varphi_{-k_l}) &\prod_{\stackrel{l=1}{l\neq f}}^a a^*(A_l \varphi_{n_l})\\\label{Ntimes1 term 2}
& \prod_{l=1}^b a^*(B_l \varphi_{-k_l}) \prod_{l=1}^a a(\varphi_{n_l}) a^*(CP_- \varphi_{n_f})\\\notag
+(-1)^b\prod_{l=1}^b a(\varphi_{-k_l}) a(\varphi_{-m}) &\prod_{l=1}^a a^*(A_l \varphi_{n_l}) \\ \label{Ntimes1 term 3}
&\prod_{l=1}^b a^*(B_l \varphi_{-k_l}) \prod_{l=1}^a a(\varphi_{n_l})a^*(C \varphi_{-m}).
\end{align}

We will discuss terms \eqref{Ntimes1 term 1}, \eqref{Ntimes1 term 2} and \eqref{Ntimes1 term 3} separately. 
In Term \eqref{Ntimes1 term 1} we need to commute the last creation operator into its place in the third product,
it can be picked up by one of the annihilation operators of the last product, but after performing the sum over
the corresponding basis the resulting term can be rephrased in terms of an \(L\) operator by commuting
only creation operators of the second and third product. Performing these steps yields the identity

\begin{multline}
\eqref{Ntimes1 term 1}=\sum_{f=1}^b L\left( \bigcup_{l=1}^a \{A_l\}; \bigcup_{\stackrel{l=1}{l\neq f}}^b \{B_l\}\cup  \{CP_- B_f \}\right)\\
+(-1)^{a+b+1}\sum_{f=1}^b \sum_{g=1}^a L\left( \bigcup_{\stackrel{l=1}{l\neq g}}^a \{A_l\}; \bigcup_{\stackrel{l=1}{l\neq f}}^b \{B_l\} \{A_gP_+CP_- B_f \}\right).
\end{multline}

For \eqref{Ntimes1 term 2} the last creation operator needs to be commuted to the end of the second product. It can be picked up by 
one of the annihilation operators of the last product, but here we have to distinguish between two cases. If the index of this
annihilation operator equals \(f\) the resulting commutator will be \(\tr P_+ C P_- A_f \) otherwise one can again perform the sum
over the corresponding index and express the whole Product in terms of an \(L\) operator. All this results in 

\begin{multline}
\eqref{Ntimes1 term 2}=\sum_{f=1}^a L\left( \bigcup_{\stackrel{l=1}{l\neq f}}^a \{A_l\}\cup \{C P_- A_f\}; \bigcup_{l=1}^b \{B_l\}\right)\\
+(-1)^{a+b}\sum_{f=1}^a  L\left( \bigcup_{\stackrel{l=1}{l\neq f}}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\} \right) \tr (P_+ C P_- A_f )\\
+(-1)^{a+b+1}\sum_{\stackrel{f_1,f_2=1}{f_1\neq f_2}}^a L\left( \bigcup_{\stackrel{l=1}{l\neq f_1,f_2}}^a \{A_l\} \cup \{A_{f_2} P_+CP_- A_{f_1} \}; \bigcup_{l=1}^b \{B_l\} \right).
\end{multline}

For \eqref{Ntimes1 term 3} the procedure is basically the same as for \eqref{Ntimes1 term 1}, it results in

\begin{multline}
\eqref{Ntimes1 term 3}= (-1)^{a+b} L\left( \bigcup_{l=1}^a \{A_l\}; \bigcup_{l=1}^b \{B_l\}\right)\\
+ \sum_{f=1}^a L\left( \bigcup_{\stackrel{l=1}{l \neq f}}^a \{A_l\}\cup \{C P_- A_f\}; \bigcup_{l=1}^b \{B_l\}\cup \{A_f P_+ C\}\right).
\end{multline}

Putting the results of the calculation together results in the claimed equation, after pulling in some factors of \(-1\) into \(L\). \qed

We carry on with defining the important quantities for powers of \(G\). First we introduce for each \(k \in \mathbb{N}\) a linear
bounded operator on \(\mathcal{H}\), \(X_k\) which fulfils \(\tr P_+ X_k P_- X_k<\infty\wedge \tr P_- X_k P_+ X_k<\infty\). 

\begin{Def}
Let 
\begin{equation*}
Y:=\{X_k\mid k\in\mathbb{N}\}.
\end{equation*}
Let for \(n\in\mathbb{N}\)
\begin{equation*}
\langle n\rangle := \{X_l\mid l\in\mathbb{N}, l\le n\}.
\end{equation*}
\end{Def}

\begin{Def}
Let for  \(b\subset Y\), such that \(|b|<\infty\)
\begin{align}\notag
f_b:\{l\in\mathbb{N}\mid l\le |b|\}\rightarrow b\\
\forall k<|b| : f_b(k)=X_l\wedge f_b(k+1)=X_m\rightarrow l<m
\end{align}
\end{Def}

\begin{Def}
For any set \(b\), we denote by \(S(b)\) the symmetric group (group of permutations) over \(b\).
\end{Def}

\begin{Def}
Let for  \(b\subset Y\), such that \(|b|<\infty\) and \(\sigma_b \in S(b)\)
\begin{align*}
\text{VZ}^b_{\sigma_b}: \{k\in\mathbb{N}\mid k<|b|\} \rightarrow \{-1,1\}\\
\text{VZ}^b_{\sigma_b}(k):=\text{sgn}\big[f_b^{-1}(\sigma_b(f_b(k+1))) - f_b^{-1}(\sigma_b(f_b(k)))  \big]
\end{align*}
\end{Def}

In what is to follow the order of one particle operators will be changed in all possible ways, to keep track of this by
use of a compact notation we introduce
\begin{Def}
\begin{align*}
W: \{(b,\sigma_b) \mid b\subseteq Y \wedge |b|<\infty \wedge \sigma_b \in S(b) \} \rightarrow B(\mathcal{H})\\
W(b,\sigma_b):= \left( \prod_{k=1}^{|b|-1} \sigma_{b}(f_b(k)) P_{\text{VZ}_{\sigma_b}^b(k)} \text{VZ}_{\sigma_b}^b(k) \right) \sigma_b (f_b(|b|))
\end{align*}
\end{Def}

\begin{Def} Let \(l\) be any finite subset of \(Y\). Denote by \(X^l_{\text{max}}\) the operator \(X_k\in l \)
such that for any \(X_c\in l \) the relation \(k\ge c\) is fulfilled. Furthermore define
\begin{align*}
&\text{PT}: \{T\subset \mathcal{P}(Y)\mid |T|<\infty, \forall b\in T: |b|<\infty\}\rightarrow \mathbb{C}\\
&\text{for: } T=\emptyset: \text{PT}(T)=1, \text{ otherwise: }\\
&\text{PT}(T)=\sum_{\stackrel{\forall l \in T:}{\sigma_l \in S(l \backslash \{X_{\text{max}}^l\})}} \prod_{l\in T} 
\tr [P_+ X^l_{\text{max}} P_- W(l, \sigma_l)]
\end{align*}
\end{Def}

There is one more function left to define
\begin{Def}
\begin{align*}
\text{Op}:  \{R\in \mathcal{P}(Y)\mid |R|<\infty\} \times \{D\subset \mathcal{P}(Y)\mid |T|<\infty\}\rightarrow \mathcal{B}(\mathcal{F})\\
\text{Op}(R,D)=\sum_{\stackrel{\forall l \in D:}{\sigma_l \in S(l)}} \sum_{a \subseteq R \cup \bigcup_{l\in D} \{W(l,\sigma_l)\}} L(a,a^c)(-1)^{|a|+  \frac{(|R| + |D|)(|R|+|D|+1)}{2}}
\end{align*}
\end{Def}

Now we are able to state the main theorem which will help us do quantitative estimates.

\begin{Thm}
Let \(n\in\mathbb{N}\), \(X_1,\dots, X_n \in Y\) then the following equation holds

\begin{equation}\label{eq:ProductG}
\prod_{k=1}^n G(X_k)= 
\sum_{\stackrel{\langle n \rangle = \dot{\Cup}_{l\in T} l \dot{\cup} \dot{\Cup}_{l\in D} l \dot{\cup} R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T) \text{Op}(R,D),
\end{equation}
where the abbreviation \(\langle n\rangle:= \{X_k\mid k\le n\}\) was used.
\end{Thm}
{\bfseries Proof:} The proof will be by induction on \(n\). Since the formula in the claim reduces to 1 for \(n=0\) we will
not spend any more time on the start of the induction. The general strategy of the proof is to break up the right 
hand side of \eqref{eq:ProductG} for \(n+1\) into small pieces and show for each piece that it corresponds to one of
the contributions of lemma \ref{lem:Ntimes1}, while also each term in this lemma is represented by one of the terms
obtained by breaking up \eqref{eq:ProductG}.

As a first step we break the right hand side of \eqref{eq:ProductG} into three pieces separated by in which set \(X_{n+1}\) 
ends up in :
\begin{align}\notag
\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T) \text{Op}(R,D)=\\\label{ProductGI}
\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{\stackrel{\exists l \in T: X_{n+1}\in l}{ \forall l \in T \cup D: |l|\ge 2}}} \text{PT}(T) \text{Op}(R,D)\\\label{ProductGII}
+\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{\stackrel{\exists l\in D: X_{n+1}\in l}{ \forall l \in T \cup D: |l|\ge 2}}} \text{PT}(T) \text{Op}(R,D)\\\label{ProductGIII}
+\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{\stackrel{X_{n+1}\in R}{ \forall l \in T \cup D: |l|\ge 2}}} \text{PT}(T) \text{Op}(R,D),
\end{align}

We will discuss each term separately. For term \eqref{ProductGI} the term containing \(X_{n+1}\) is in one of the elements \(l'\) of \(T\), 
but each such element has to have more than one element. So if we were to sum over the partitions of \(\langle n\rangle \) instead,
the rest of \(l'\backslash \{X_{n+1}\}\) is either an element of \(D\) or, if it contains only one element, of \(R\). Picking \(D\) instead of \(T\)
is at this stage an arbitrary choice, but this choice leads to the terms of lemma \ref{lem:Ntimes1}. Alls this means that one
correct rewriting of term \eqref{ProductGI} is

\begin{multline}\label{eq:ProductGI2}
\eqref{ProductGI}= \sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} } \sum_{b \in D \cup \{ \{r\} \mid r\in R \}}  \\
\text{PT}(T\cup \{\{X_{n+1} \cup f\}) \text{Op}(R \backslash b, D\backslash \{b\}).
\end{multline}

Next we pull one factor and the corresponding sum out of PT and write out Op. Then we see that the sums over permutations 
can be merged into one. There we take the convention that for any set \(f\) such that \(|f|=1\) holds, we define \(\sigma_f\) to be
the identity on that set.

This results in

\begin{align}\notag
\eqref{eq:ProductGI2}= \sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\sum_{b \in D \cup \{ \{r\} \mid r\in R \}}  \sum_{\sigma_b \in S(b)}\\\notag
 \tr[P_+ X_{n+1} P_- W(b,\sigma_b)] \text{PT}(T) \sum_{\stackrel{\forall l \in D\backslash \{b\}}{\sigma_l \in S(l)}} \\\notag
 \sum_{a\subseteq R\backslash b \cup \bigcup_{l\in D\backslash \{b\}}\{W(l,\sigma_l)\}}  L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|-1)(|R|+|D|)}{2}}\\\notag
 =\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}  \sum_{b \in D \cup \{ \{r\} \mid r\in R \}} \text{PT}(T)\\\notag
 \sum_{a\subseteq R\backslash b \cup \bigcup_{l\in D\backslash \{b\}}\{W(l,\sigma_l)\}}  L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|-1)(|R|+|D|)}{2}}\\\notag
\tr[P_+ X_{n+1} P_- W(b,\sigma_b)]   \\\notag
=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}   \text{PT}(T)  \sum_{a\subseteq R \cup \bigcup_{l\in D}\{W(l,\sigma_l)\}}\\\notag
\sum_{b \in D \cup \{ \{r\} \mid r\in R \}} \id_{W(b,\sigma_b)\in a}  L(a\backslash\{b\},a^c) (-1)^{|a|+1}\\\notag
(-1)^\frac{(|R|+|D|-1)(|R|+|D|)}{2} \tr[P_+ X_{n+1} P_- W(b,\sigma_b)]\\\notag
=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\text{PT}(T) \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}  \sum_{a\subseteq R \cup \bigcup_{l\in D}\{W(l,\sigma_l)\}} \\\notag
 \sum_{b \in a  }   L(a\backslash\{b\},a^c) (-1)^{|a|+\frac{(|R|+|D|+1)(|R|+|D|)}{2}}\\\notag
 (-1)^{1+|R|+|D|} \tr[P_+ X_{n+1} P_- W(b,\sigma_b)]\\\notag
 =\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\text{PT}(T) \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}  \sum_{a\subseteq R \cup \bigcup_{l\in D}\{W(l,\sigma_l)\}} \\
   (-1)^{|a|+\frac{(|R|+|D|+1)(|R|+|D|)}{2}}  \eqref{Ntimes1:TrTerm}_{L(a,a^c) G(X_{n+1})},
\end{align}

where the notation in the last line is to be taken as ``apply Lemma \ref{lem:Ntimes1} apply it to \(L(a,a^c) G(X_{n+1})\) and
pick only term \eqref{Ntimes1:TrTerm}''. We will use this abbreviating notation also for the next terms.

The next term is \eqref{ProductGII}. Here we need a few more notational conventions. For any  set 
\(b\subseteq \langle n \rangle\) and corresponding
permutation \(\sigma_b\in S(b)\), we denote by the same symbol \(\sigma_b\) the continuation of \(\sigma_b\) to \(b\cup \{X_{n+1}\}\),
where for this continuation \(X_{n+1}\) is a fixed point. Furthermore we define for any set 
\(b\subseteq \langle n \rangle\), \(\sigma_c^b\) by

\begin{align}\notag
&\sigma_c^b \in  S(b\cup\{X_{n+1}\}), \\\notag
\forall k\le |b|: &\sigma_c^b(f_{b\cup \{X_{n+1}\}}(k))=f_{b\cup \{X_{n+1}\}}(k+1)\\
 &\sigma^b_c (X_{n+1})=f_b(1).
\end{align}

Finally we define for sets \(b_1,b_2 \subseteq \langle n \rangle, b_1\cap b_2=\emptyset\) and corresponding
permutations \(\sigma_{b_1}\in S(b_1), \sigma_{b_2} \in S(b_2)\) the permutation 
\(\sigma_{b_1,b_2}^{n+1}\) by

\begin{align}\notag
M_{b_1,b_2}^{n+1} :=b_1\cup b_2 \cup \{X_{n+1}\}\\\notag
\sigma_{b_1,b_2}^{n+1}\in S(M_{b_1,b_2}^{n+1} )\\\notag
\forall 1\le k \le |b_1|: \sigma_{b_1,b_2}^{n+1}(f_{M_{b_1,b_2}^{n+1}}(k))=\sigma_{b_1}(f_{b_1}(k))\\\notag
\sigma_{b_1,b_2}^{n+1}(f_{M_{b_1,b_2}^{n+1}}(|b_1|+1))=X_{n+1}\\\notag
\forall |b_1|+2\le k \le |b_1|+|b_2|+1:\\
 \sigma_{b_1,b_2}^{n+1}(f_{M_{b_1,b_2}^{n+1}}(k))
= \sigma_{b_2} ( f_{b_2}(k-|b_1|-1))
\end{align}

The beginning of the treatment of term \eqref{ProductGII} is analogous to \eqref{ProductGI}, we rewrite the
partition of \(\langle n+1\rangle \) into one of \(\langle n \rangle \) with an additional sum over where the
other operators packed to together with \(X_{n+1}\) come from. This splits into three parts, either \(X_{n+1}\)
is put at the beginning of the compound operator, or its put at the end of the compound object, or 
to the left as well as to the right are operators with smaller index. Since the overall sign is decided by 
how often the operator index rises or falls, this separation into cases is helpful. The last case we then
rewrite as picking two sets of operators, one of which will be in front of \(X_{n+1}\) and the other one
behind this operator. 

The calculation is as follows

\begin{align}\notag
&\eqref{ProductGII}= \sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{\stackrel{\exists l\in D: X_{n+1}\in l}{ \forall l \in T \cup D: |l|\ge 2}}} \text{PT}(T) \text{Op}(R,D)\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \text{Op} (R\backslash b , D\cup \{ b \cup \{X_{n+1}\}\backslash \{b\}\})\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D \cup \{b \cup \{X_{n+1}\}\}}{\sigma_l \in S(l)}}\\\notag
 &\sum_{a \subseteq R\backslash b \cup \bigcup_{l \in D \cup \{b \cup \{X_{n+1}\} \}\backslash \{b\}}\{W(l,\sigma_l)\}} L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}\Big[\\\label{ProductGII.1}
 &\sum_{a \subseteq R\backslash b \cup \bigcup_{l \in D\backslash \{b\}}\{W(l,\sigma_l)\} \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\}} L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\\\label{ProductGII.2}
&+\sum_{a \subseteq R\backslash b \cup \bigcup_{l \in D\backslash \{b\}}\{W(l,\sigma_l)\}\cup \{W(b\cup \{X_{n+1}\},\sigma^b_c \circ\sigma_b)\}} L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\Big]\\\notag
&+\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in \overline{D}}l \dotcup \overline{R}}{\forall l \in \overline{D}\cup T: |l|\ge 2}} \text{PT}(T) \sum_{\stackrel{b_1,b_2\in \overline{D} \cup \{\{r\}\mid r \in \overline{R}\}}{b_1 \neq b_2}} \sum_{\stackrel{\forall l \in \overline{D} }{\sigma_l \in S(l)}}\\\label{ProductGII.3}
&\sum_{a \subseteq \tilde{R}\cup \bigcup_{l \in \tilde{D}}\{W(l,\sigma_l)\} \cup \{W(b_1\cup \{X_{n+1}\}\cup b_2,\sigma^{n+1}_{b_1,b_2})\}} L(a,a^c) (-1)^{|a|+ \frac{(|\overline{R}|+|\overline{D}|-1)(|\overline{R}|+|\overline{D}|)}{2}}
\end{align}

where \(\tilde{R}=\overline{R} \backslash (b_1\cup b_2)\) and
\(\tilde{D}:=\overline{D} \cup \{b_1 \cup \{X_{n+1}\} \cup b_2 \}\backslash \{b_1,b_2\}\). For the term 
\eqref{ProductGII.3} we had to reshuffle the outermost
sum a bit. For each term in the original sum where \(X_{n+1}\) is neither the first nor the last factor in its product (we will call the set of factors in front of \(X_{n+1}\)  \( \alpha\) and the factors behind it \(\beta\)) there is a different splitting of \(\langle n \rangle \) into \(\overline{R}\) and \(\overline{D}\) such that \(\alpha\) and \(\beta\) are separate elements of \(\overline{D}\cup \{\{r\}\mid r \in \overline R\}\).
So we replace the original sum over \(D\) and \(R\) into one of \(\overline{D}\) and \(\overline{R}\). Since this is a one to one
correspondence and the sum is finite this is always possible. The exponent of the sign also changes for this reason, since
\(|R|+|D|=|\overline{R}|+|\overline{D}|-1\) holds. Continuing with \eqref{ProductGII.1} the next steps are similar to the last steps
in treating \eqref{ProductGI}. They are

\begin{align}\notag
&\eqref{ProductGII.1}=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}\\\notag
 &\sum_{a \subseteq R\backslash b \cup \bigcup_{l \in D\backslash \{b\}}\{W(l,\sigma_l)\} \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\}} L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\\\notag
 &=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \\\notag
 &\sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\id_{W(b,\sigma_b)\in a} \\\notag
& \big[L(a\backslash \{W(b,\sigma_b)\} \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\},a^c) \\\notag
& -L(a\backslash \{W(b,\sigma_b)\},a^c \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\}) \big]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T)  \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \\\notag
 &\sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}
 \sum_{W(b,\sigma_b) \in a }  \\\notag
& \big[L(a\backslash \{W(b,\sigma_b)\} \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\},a^c) \\\notag
& -L(a\backslash \{W(b,\sigma_b)\},a^c \cup \{W(b\cup \{X_{n+1}\},\sigma_b)\}) \big]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T)  \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} \\
 & (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}
 (\eqref{Ntimes1:n+1atEnd1}+\eqref{Ntimes1:n+1atEnd2})_{L(a,a^c)G(X_{n+1})}.
\end{align}

Almost the same procedure applies to \eqref{ProductGII.2}. It yields %\label{Ntimes1:n+1atBeginnign1}

\begin{align}\notag
&\eqref{ProductGII.2}=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}\\\notag
 &\sum_{a \subseteq R\backslash b \cup \bigcup_{l \in D\backslash \{b\}}\{W(l,\sigma_l)\} \cup \{W(b\cup \{X_{n+1}\},\sigma^b_c\circ \sigma_b)\}} L(a,a^c) (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}\\\notag
 &=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T) \sum_{b\in D \cup \{\{r\}\mid r \in R\}} \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \\\notag
 &\sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}} \\\notag
& \big[ \id_{W(b,\sigma^b_c\circ\sigma_b)\in a} L(a\backslash \{W(b,\sigma_b)\} \cup \{W(b\cup \{X_{n+1}\},\sigma^b_c \circ\sigma_b)\},a^c) \\\notag
& +\id_{W(b,\sigma^b_c\circ \sigma_b)\in a^c} L(a\backslash \{W(b,\sigma_b)\},a^c \cup \{W(b\cup \{X_{n+1}\},\sigma^b_c \circ \sigma_b)\}) \big]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T)  \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \\\notag
 &\sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}
  \\\notag
& \big[ \sum_{W(b,\sigma_b) \in a }L(a\backslash \{W(b,\sigma_b)\} \cup \{W(b\cup \{X_{n+1}\},\sigma^b_c \circ\sigma_b)\},a^c) \\\notag
&+  \sum_{W(b,\sigma_b) \in a^c } L(a,a^c \backslash \{W(b,\sigma_b)\} \cup \{W(b\cup \{X_{n+1}\},\sigma^b_c \circ \sigma_b)\}) \big]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} \text{PT}(T)  \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}} \sum_{a \subseteq R \cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} \\
 & (-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}}
 (\eqref{Ntimes1:n+1atBeginning1}+\eqref{Ntimes1:n+1atBeginning2})_{L(a,a^c)G(X_{n+1})}.
\end{align}


Also for \eqref{ProductGII.3} the procedure is almost the same. We bring the sums into a form such that one can read off the
terms generated by the induction. We begin be renaming the sets which we had to change by resumming back to the names 
of the original sets. 


\begin{align}\notag
&\eqref{ProductGII.3}=
\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in \overline{D}}l \dotcup \overline{R}}{\forall l \in \overline{D}\cup T: |l|\ge 2}} 
\text{PT}(T) 
\sum_{\stackrel{b_1,b_2\in \overline{D} \cup \{\{r\}\mid r \in \overline{R}\}}{b_1 \neq b_2}} 
\sum_{\stackrel{\forall l \in \overline{D} }{\sigma_l \in S(l)}}\\\notag
&\sum_{a \subseteq \tilde{R}\cup \bigcup_{l \in \tilde{D}}\{W(l,\sigma_l)\} \cup \{W(b_1\cup \{X_{n+1}\}\cup b_2,\sigma^{n+1}_{b_1,b_2})\}} L(a,a^c) (-1)^{|a|+ \frac{(|\overline{R}|+|\overline{D}|-1)(|\overline{R}|+|\overline{D}|)}{2}}\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} 
\text{PT}(T) 
\sum_{\stackrel{b_1,b_2\in D \cup \{\{r\}\mid r \in R\}}{b_1 \neq b_2}} 
\sum_{\stackrel{\forall l \in D }{\sigma_l \in S(l)}}\\\notag
&\sum_{a \subseteq R\cup \bigcup_{l \in D}\{W(l,\sigma_l)\} \cup \{W(b_1\cup \{X_{n+1}\}\cup b_2,\sigma^{n+1}_{b_1,b_2})\}} L(a,a^c) (-1)^{|a|+ \frac{(| R|+|D|-1)(|R|+|D|)}{2}}\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} 
\text{PT}(T) 
\sum_{\stackrel{b_1,b_2\in D \cup \{\{r\}\mid r \in R\}}{b_1 \neq b_2}} 
\sum_{\stackrel{\forall l \in D }{\sigma_l \in S(l)}} \sum_{a \subseteq R\cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} \\\notag
&(-1)^{|R|+|D|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}} \id_{W(b_1,\sigma_1)\in a}\\\notag
&\left[+(-1)^{|a|+1}\id_{W(b_2,\sigma_2)\in a} L\Big(a\backslash\{W(b_1,\sigma_1),W(b_2,\sigma_2)\}\cup\right.\\\notag
&\cup \{W(b_1\cup \{X_{n+1}\}\cup b_2,\sigma^{n+1}_{b_1,b_2})\} ,a^c\Big) \\\notag
&+(-1)^{|a|+1}\id_{W(b_2,\sigma_2)\in a^c}L\Big(a\backslash\{W(b_1,\sigma_1)\} ,a^c \backslash\{W(b_2,\sigma_2)\}\cup\\\notag
&\left. \cup \{W(b_1\cup \{X_{n+1}\}\cup f_2,\sigma^{n+1}_{b_1,b_2})\}\Big) \right]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} 
\text{PT}(T) 
\sum_{\stackrel{\forall l \in D }{\sigma_l \in S(l)}} \sum_{a \subseteq R\cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} \\\notag
&(-1)^{|R|+|D|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}} \\\notag
&\Big[(-1)^{|a|+1}\sum_{\stackrel{b_1,b_2 \in a}{b_1 \neq b_2}}  L\Big(a\backslash\{W(b_1,\sigma_1),W(b_2,\sigma_2)\}\cup\\\notag
&\cup \{W(b_1\cup \{X_{n+1}\}\cup b_2,\sigma^{n+1}_{b_1,b_2})\} ,a^c\Big) \\\notag
&+(-1)^{|a|+1}\sum_{b_1\in a,b_2\in a^c}  L\Big(a\backslash\{W(b_1,\sigma_1)\} ,a^c \backslash\{W(b_2,\sigma_2)\}\cup\\\notag
&\left. \cup \{W(b_1\cup \{X_{n+1}\}\cup f_2,\sigma^{n+1}_{b_1,b_2})\}\Big) \right]\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D}l \dotcup R}{\forall l \in D\cup T: |l|\ge 2}} 
\text{PT}(T) 
\sum_{\stackrel{\forall l \in D }{\sigma_l \in S(l)}} \sum_{a \subseteq R\cup \bigcup_{l \in D}\{W(l,\sigma_l)\}} \\\notag
&(-1)^{|a|+ \frac{(|R|+|D|)(|R|+|D|+1)}{2}} (\eqref{Ntimes1:middle1}+\eqref{Ntimes1:middle2})_{L(a,a^c)G(X_{n+1})}
\end{align}

Lastly we will discuss term \eqref{ProductGIII}; luckily, this term is less involved than the other two. The general procedure;
however, stays the same. First we reformulate the partition of \(\langle n+1\rangle\) into one of \(\langle n \rangle \), where
the terms acquire modifications. Secondly we massage these terms until the involved sums look exactly like the one 
in our induction hypothesis \eqref{eq:ProductG} and realise that the terms are produced by lemma \ref{lem:Ntimes1}.
For term \eqref{ProductGIII}  this results in

\begin{align}\notag
&\eqref{ProductGIII}
=\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{\stackrel{X_{n+1}\in R}{ \forall l \in T \cup D: |l|\ge 2}}} \text{PT}(T) \text{Op}(R,D)\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T)
\text{Op}(R\cup \{X_{n+1}\},D)\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T)
\sum_{\stackrel{\forall l \in D:}{\sigma_l \in S(l)}} \quad \sum_{a\subseteq R \cup \{X_{n+1}\} \cup \bigcup_{l\in D} \{W(l,\sigma_l)\}}\\\notag
&L(a,a^c)(-1)^{|a| + \frac{(|R|+1+|D|)(|R|+|D|+2)}{2}}\\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T)
\sum_{\stackrel{\forall l \in D:}{\sigma_l \in S(l)}} \quad \sum_{a\subseteq R \cup \bigcup_{l\in D} \{W(l,\sigma_l)\}}
(-1)^{|a| + \frac{(|R|+1+|D|)(|R|+|D|)}{2}}\\\notag
&\big(-L(a\cup\{X_{n+1}\},a^c)+L(a,a^c\cup \{X_{n+1}\}) \big)(-1)^{|R|+|D|+1} \\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T)
\sum_{\stackrel{\forall l \in D:}{\sigma_l \in S(l)}} \quad \sum_{a\subseteq R \cup \bigcup_{l\in D} \{W(l,\sigma_l)\}}
(-1)^{|a| + \frac{(|R|+1+|D|)(|R|+|D|)}{2}}\\\notag
&\big(L(a\cup\{X_{n+1}\},a^c)(-1)^{|R|+|D|}+L(a,a^c\cup \{X_{n+1}\})(-1)^{|R|+|D|+1} \big) \\\notag
&=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T)
\sum_{\stackrel{\forall l \in D:}{\sigma_l \in S(l)}} \quad \sum_{a\subseteq R \cup \bigcup_{l\in D} \{W(l,\sigma_l)\}}
(-1)^{|a| + \frac{(|R|+1+|D|)(|R|+|D|)}{2}}\\\notag
&\big(\eqref{Ntimes1:simplyAdd1}+\eqref{Ntimes1:simplyAdd2} \big)_{L(a,a^c)G(X_{n+1})}.
\end{align}

Summarising we showed 
\begin{align*}
&\sum_{\stackrel{\langle n +1 \rangle = \dotCup_{l\in T} l \dotcup \dotCup_{l\in D} l \dotcup R}{ \forall l \in T \cup D: |l|\ge 2}} \text{PT}(T) \text{Op}(R,D)\\
 &=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\text{PT}(T) \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}  \sum_{a\subseteq R \cup \bigcup_{l\in D}\{W(l,\sigma_l)\}} \\
  & (-1)^{|a|+\frac{(|R|+|D|+1)(|R|+|D|)}{2}}  \\
  &\big( \eqref{Ntimes1:TrTerm}+\eqref{Ntimes1:n+1atEnd1}+\eqref{Ntimes1:n+1atEnd2} 
  +\eqref{Ntimes1:n+1atBeginning1}+\eqref{Ntimes1:n+1atBeginning2}\\
 &+\eqref{Ntimes1:middle1}+\eqref{Ntimes1:middle2}
  +\eqref{Ntimes1:simplyAdd1}+\eqref{Ntimes1:simplyAdd2}\big)_{L(a,a^c) G(X_{n+1})}\\
 &=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\text{PT}(T) \sum_{\stackrel{\forall l \in D}{\sigma_l \in S(l)}}  \sum_{a\subseteq R \cup \bigcup_{l\in D}\{W(l,\sigma_l)\}} \\
  & (-1)^{|a|+\frac{(|R|+|D|+1)(|R|+|D|)}{2}} L(a,a^c)G(X_{n+1})\\
  &=\sum_{\stackrel{\langle n \rangle = \dotCup_{l\in T}l \dotcup \dotCup_{l\in D} l \dotcup R}{\forall l \in D \cup T: |l|>2} }\text{PT}(T) \text{Op}(R,D)G(X_{n+1})\\
  &=\prod_{l=1}^n G(X_{l}) \quad G(X_{n+1}),
\end{align*}

which ends our proof by induction.\qed




\appendix

\backmatter

\chapter{Appendix}

\section{Heuristic Construction of \(S\)-Matrix expression}\label{sec:heuristic construction}

In the following I derive a recursive equation for the coefficients of the expansion 
of the second quantized scattering operator. The starting point of this derivation is 
the commutator of \(T_m\), equation \eqref{logarithmic lift condition}.

\subsection{Guessing Equations}

Why at this point one might suspect that such a representation exists is, because
looking at equation \eqref{logarithmic lift condition} for a while, one
comes to the conclusion that if one replaces \(T_m\) by 
\begin{equation}
T_m - \frac{1}{2} \sum_{k=1}^{m-1} \begin{pmatrix} m \\ k\end{pmatrix} T_k T_{m-k},
\end{equation}
no \(T_k\) with \(k>m-2\) will occur on the right hand side of the resulting equation.
So if one subtracts the right polynomial in \(T_k\) for suitable \(k\) one might achieve
a commutator which contains only the creation respectively annihilation operator 
concatenated with some one particle operator. From our treatment of \(T_1\)
\noch{place proper reference to definition of G operator} we know which
operators have such commutation relations. 

So having this in Mind we start with the ansatz

\begin{equation}\label{Def Gamma_m}
\Gamma_m := \sum_{g=2}^m \sum_{\stackrel{b\in\mathbb{N}^g}{|b|=m}} c_{b} \prod_{k=1}^g T_{b_k}.
\end{equation}

Now in order to show that \(T_m\) and \(\Gamma_m\) agree up to operators which have a commutation 
relation of the form \eqref{G commutator}, we calculate \(\left[ T_m-\Gamma_m, a^\#(\varphi_n) \right]\)
for arbitrary \(n\in\mathbb{Z}\) and try to choose the coefficients \(c_b\) of \eqref{Def Gamma_m}
such that all contributions vanish which do not have the form \(a^\# \left( \prod_k Z_{\alpha_k}\right)\)
for any suitable \((\alpha_k)_k\subset \mathbb{N} \). If one does so, one is led to a system of equations
of which I wrote down a few to give an overview of its structure. The objects \(\alpha_k, \beta_l\) 
in the system of equations can be any natural Number for any \(k,l\in\mathbb{N}\).

\begin{align*}
&0 =c_{\alpha_1,\beta_1} + c_{\beta_1,\alpha_1}+ \binom{ \alpha_1 + \beta_1}{ \alpha_1} \\
&0 = c_{\alpha_1,\alpha_2,\beta_1} + c_{\beta_1,\alpha_1,\alpha_2} + c_{\alpha_2,\alpha_1,\beta_1} + 
\binom{\alpha_2 + \beta_1}{ \alpha_2} c_{\alpha_1,\alpha_2+\beta_1} \\
&\hspace{2cm}  +\binom{\alpha_1+\beta_1}{\alpha_1} c_{\alpha_1+\beta_1,\alpha_2}\\
&0= c_{\alpha_1,\alpha_2,\alpha_3,\beta_1} + c_{\alpha_1,\alpha_2,\beta_1,\alpha_3} 
+ c_{\alpha_1,\beta_1,\alpha_2,\alpha_3} + c_{\beta_1,\alpha_1,\alpha_2,\alpha_3}\\
&+\binom{\alpha_1+\beta_1}{\beta_1} 
c_{\alpha_1+\beta_1,\alpha_2,\alpha_3} 
+ \binom{\alpha_2+\beta_1}{\beta_1} c_{\alpha_1,\alpha_2+\beta_1,\alpha_3}\\
&\hspace{2cm} + \binom{\alpha_3+\beta_1}{\beta_1} c_{\alpha_1,\alpha_2,\alpha_3+\beta_1}\\
&0= c_{\alpha_1,\alpha_2,\beta_1,\beta_2} +c_{\alpha_1,\beta_1,\alpha_2,\beta_2} +
c_{\beta_1,\alpha_1,\alpha_2,\beta_2} +c_{\alpha_1,\beta_1,\beta_2,\alpha_2} \\
&+c_{\beta_1,\alpha_1,\beta_2,\alpha_2} +c_{\beta_1,\beta_2,\alpha_1,\alpha_2} 
+\binom{\alpha_1+\beta_1}{\alpha_1} (c_{\alpha_1+\beta_1,\alpha_2,\beta_2} \\
&+ c_{\alpha_1+\beta_1,\beta_2,\alpha_2})  
+\binom{\alpha_1+\beta_2}c_{\beta_1,\alpha_1+\beta_2,\alpha_1} \\
&+\binom{\alpha_2+\beta_1}{\alpha_2} c_{\alpha_1,\alpha_2+\beta_1,\beta_2}
+ \binom{\alpha_2+\beta_2}{\alpha_2} (c_{\alpha_1,\beta_1,\alpha_2+\beta_2}\\
&+ c_{\beta_1,\alpha_1,\alpha_2+\beta_2})
+ \binom{\alpha_1+\beta_1}{\alpha_1} \binom{\alpha_2+\beta_2}{\alpha_2}
 c_{\alpha_1+\beta_1,\alpha_2+\beta_2}\\
&0=c_{\alpha_1,\beta_1,\beta_2,\beta_3,\beta_4} 
+ c_{\beta_1,\alpha_1,\beta_2,\beta_3,\beta_4} 
+ c_{\beta_1,\beta_2,\alpha_1,\beta_3,\beta_4} \\
&\hspace{1cm}+ c_{\beta_1,\beta_2,\beta_3,\alpha_1,\beta_4} 
+ c_{\beta_1,\beta_2,\beta_3,\beta_4,\alpha_1} \\
&+\binom{\alpha_1+\beta_1}{\alpha_1} c_{\alpha_1+\beta_1,\beta_2,\beta_3,\beta_4}
+ \binom{\alpha_1+\beta_2}{\alpha_1} c_{\beta_1,\alpha_1+\beta_2,\beta_3,\beta_4}\\
&+ \binom{\alpha_1+\beta_3}{\alpha_1} c_{\beta_1,\beta_2,\alpha_1+\beta_3,\beta_4}
+ \binom{\alpha_1+\beta_4}{\alpha_1} c_{\beta_1,\beta_2,\beta_3,\alpha_1+\beta_4}\\
&0= c_{\alpha_1,\alpha_2,\beta_1,\beta_2,\beta_3} 
+c_{\alpha_1,\beta_1,\alpha_2,\beta_2,\beta_3} 
+c_{\beta_1,\alpha_1,\alpha_2,\beta_2,\beta_3} \\
&+c_{\alpha_1,\beta_1,\beta_2,\alpha_2,\beta_3} 
+c_{\beta_1,\alpha_1,\beta_2,\alpha_2,\beta_3} 
+c_{\beta_1,\beta_2,\alpha_1,\alpha_2,\beta_3} \\
&+c_{\alpha_1,\beta_1,\beta_2,\beta_3,\alpha_2} 
+c_{\beta_1,\alpha_1,\beta_2,\beta_3,\alpha_2} 
+c_{\beta_1,\beta_2,\alpha_1,\beta_3,\alpha_2} \\
&+c_{\beta_1,\beta_2,\beta_3,\alpha_1,\alpha_2} 
+\binom{\alpha_1+\beta_1}{\beta_1} (c_{\alpha_1+\beta_1,\alpha_2,\beta_2,\beta_3}\\
&+c_{\alpha_1+\beta_1,\beta_2,\alpha_2,\beta_3}
+c_{\alpha_1+\beta_1,\beta_2,\beta_3,\alpha_2})\\
&+\binom{\alpha_2+\beta_1}{\beta_1} c_{\alpha_1,\alpha_2+\beta_1,\beta_2,\beta_3}\\
&+\binom{\alpha_2+\beta_2}{\beta_2} (c_{\beta_1,\alpha_1,\alpha_2+\beta_2,\beta_3}
+c_{\alpha_1,\beta_1,\alpha_2+\beta_2,\beta_3})\\
&+\binom{\alpha_1+\beta_2}{\beta_2} (c_{\beta_1,\alpha_1+\beta_2,\alpha_2,\beta_3}
+c_{\beta_1,\alpha_1+\beta_2,\beta_3,\alpha_2})\\
&+\binom{\alpha_2+\beta_3}{\beta_3}( c_{\alpha_1,\beta_1,\beta_2,\alpha_2+\beta_3}
+c_{\beta_1,\alpha_1,\beta_2,\alpha_2+\beta_3}\\
&+c_{\beta_1,\beta_2,\alpha_1,\alpha_2+\beta_3})
+\binom{\alpha_1+\beta_3}{\beta_3} c_{\beta_1,\beta_2,\alpha_1+\beta_3,\alpha_2}\\
&+\binom{\alpha_1+\beta_1}{\alpha_1} \binom{\alpha_2+\beta_2}{\alpha_2} 
c_{\alpha_1+\beta_1,\alpha_2+\beta_2,\beta_3}\\
&+\binom{\alpha_1+\beta_2}{\alpha_1} \binom{\alpha_2+\beta_3}{\alpha_2} 
c_{\beta_1,\alpha_1+\beta_2,\alpha_2+\beta_3}\\
&+\binom{\alpha_1+\beta_1}{\alpha_1} \binom{\alpha_2+\beta_3}{\alpha_2} 
c_{\alpha_1+\beta_1,\beta_2,\alpha_2+\beta_3}\\
& \hspace{3cm} \vdots
\end{align*}

Solving the first few equations and plugging the solution into the consecutive
 equations one can see that at least the first equations are solved by 
\begin{equation}
c_{\alpha_1,\dots, \alpha_k} = \frac{(-1)^k}{k} \begin{pmatrix}\sum_{l=1}^k \alpha_l\\ \alpha_1\ \alpha_2 \ \cdots \alpha_k\end{pmatrix},
\end{equation}
where the last factor is the multinomial coefficient of the indices \(\alpha_1,\dots, \alpha_k\in\mathbb{N}\).

\subsection{Recursive equation for Coefficients of the second quantised scattering operator}

For the rest of this chapter, we are going to derive a concrete form of the second quantised scattering matrix. In order to turn the ``conjectures'' 
into ``theorems'' not only would one have to turn the rough sketches of the combinatorics into proofs, one also would have to show linearity (over real numbers) and
continuity of \(\mathrm{d}\Gamma(B)\) in \(B\).
However, since the final result can be verified to be well defined and to fulfil the lift conditions, this will not be necessary.
We will nonetheless come across various combinatorial assertions that we are going to prove rigorously. 
These will be clearly marked: ``lemma'' and ``proof''.

We are going to use the following definition of binomial coefficients:
\begin{Def}
For \(a\in\mathbb{C}, b\in\mathbb{Z}\) we define

\begin{equation}
\binom{a}{b} := \left\{\begin{matrix}
\prod_{l=0}^{b-1} \frac{a-l}{l+1} \quad \text{for } b\ge 0\\
0 \hspace{1.7cm} \text{otherwise.}
\end{matrix}\right.
\end{equation}
\end{Def}

Defining the binomial coefficient for negative lower index to be zero has the merit, that one can extend the
range of validity of many rules and sums involving binomial coefficients, also one does not have 
to worry about the range of summation in many cases.



The coefficients which we have already guessed more generally to be

\begin{Conj}\label{thm: T_n recursive}
For any \(n\in\mathbb{N}\) the n-th expansion coefficient of the second quantised scattering operator \(T_n\) is given by
\begin{align}\notag
&T_n = \sum_{g=2}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g T_{b_l} + C_n \id_{\mathcal{F}} \\ \label{T_n recursive}
&+ d\Gamma\left( \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^{g+1}}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g Z_{b_l}  \right),
\end{align}
for some \(C_n\in \mathbb{C}\) which depends on the external field \(A\). The last summand will henceforth
be abbreviated by \(\Gamma_n\).
\end{Conj}

\textbf{Motivation:} The way we will prove this is to compute the commutator of the difference between \(T_n\) and
the first summand of \eqref{T_n recursive} with the creation and annihilation operator of an element of the
basis of \(\mathcal{H}\). This will turn out to be exactly equal
to the corresponding commutator
of the second summand of \eqref{T_n recursive}, since two operators on Fock space only
have the same commutator with general creation and annihilation operators if they
agree up to multiples of the identity this will conclude the motivation of this conjecture. 

 In order to simplify the notation as much as possible, 
I will denote by \(a^\# z\) either \(a(z(\varphi_p))\) or
 \(a^*(z(\varphi_p))\) for any one particle operator \(z\) and any element
 \(\varphi_p\) of the orthonormal basis \((\varphi_p)_{p\in\mathbb{Z}\backslash\{0\}}\) of
 \(\mathcal{H}\). (We need not decide between creation and annihilation 
 operator, since the expressions all agree)
 
In order to organize the bookkeeping of all the summands which arise from iteratively
making use of the commutation rule \eqref{logarithmic lift condition} we organize them 
by the looking at a spanning set of the possible terms that arise my choice is

\begin{equation}\label{combinatorics span}
\left\{ \left. a^\# \prod_{k=1}^{m_1} Z_{\alpha_k} \prod_{k=1}^{m_2}T_{\beta_k} \right|
m_1\in\mathbb{N},m_2\in\mathbb{N}_0, \alpha\in \mathbb{N}^{m_1}, 
\beta \in \mathbb{N}^{m_2}, |\alpha|+|\beta|=n\right\}_.
\end{equation}

As a first step of computing the commutator in question we look at the summand
corresponding to a fixed value of the summation index \(g\) of 

\begin{equation}\label{combinatorics total sum of T}
-\sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g T_{b_l}.
\end{equation}

 We need to bring this object into the form of a sum
of terms which are multiples of elements of the set \eqref{combinatorics span}.
This we will commit ourselves to for the next few pages. First we apply
the product rule for the commutator:

\begin{align*}
&\left[ \sum_{\stackrel{\vec{l}\in\mathbb{N}^g}{|\vec{l}|=n}} \frac{(-1)^g}{g} \binom{n}{\vec{l}}
 \prod_{k=1}^g T_{l_k},a^\#\right]\\
 &= \sum_{\stackrel{\vec{l}\in\mathbb{N}^g}{|\vec{l}|=n}} \frac{(-1)^g}{g} \binom{n}{\vec{l}}
 \sum_{\tilde{k}=1}^g \prod_{j=1}^{\tilde{k}-1} T_{l_j} 
 \left[ T_{l_{\tilde{k}}},a^\#\right] \prod_{j=\tilde{k}+1}^g T_{l_j}\\
&=\sum_{\stackrel{\vec{l}\in\mathbb{N}^g}{|\vec{l}|=n}} \frac{(-1)^g}{g} \binom{n}{\vec{l}}
 \sum_{\tilde{k}=1}^g \prod_{j=1}^{\tilde{k}-1} T_{l_j} 
\sum_{\sigma_{\tilde{k}}=1}^{l_{\tilde{k}}} \binom{l_{\tilde{k}}}{\sigma_{\tilde{k}}} 
a^\# Z_f T_{l_{\tilde{k}}-\sigma_{\tilde{k}}} \prod_{j=\tilde{k}+1}^g T_{l_j},
\end{align*}
in the second step we used \eqref{logarithmic lift condition}. Now we commute
all the \(T_l\)s to the left of \(a^\#\) to its right:

\begin{equation}\label{combinatorics ordered product}
=\!\!\! \sum_{\stackrel{\vec{l}\in\mathbb{N}^g}{|l|=n}} \!\!\frac{(-1)^g}{g}\! \binom{n}{\vec{l}}
\!\! \sum_{\tilde{k}=1}^g \!\sum_{\stackrel{\forall 1\le j <\tilde{k}}{0\le \sigma_{j}\le l_j}}
\!\sum_{\sigma_{\tilde{k}}=1}^{l_{\tilde{k}}} \prod_{j=1}^{\tilde{k}}\! \binom{l_j}{\sigma_j}
a^\# \prod_{j=1}^{\tilde{k}} Z_{\sigma_j} \prod_{j=1}^{\tilde{k}} T_{l_j-\sigma_j}
\!\!\prod_{j=\tilde{k}+1}^g T_{l_j}.
\end{equation}
At this point we notice that the multinomial coefficient can be combined with all
the binomial coefficients to form a single multinomial coefficient of degree
\(g+\tilde{k}\). Incidentally this is also the amount of \(Z\) operators plus the amount
of \(T\) operators in each product. Moreover the indices of the Multinomial index
agree with the indices of the \(Z\) and \(T\) operators in the product. Because of 
this, we see that if we fix an element of the spanning set \eqref{combinatorics span}
\(a^\# \prod_{k=1}^{m_1} Z_{\alpha_k} \prod_{k=1}^{m_2}T_{\beta_k}\), each 
summand of \eqref{combinatorics ordered product} which contributes to
this element, has the prefactor

\begin{equation}
\frac{(-1)^g}{g} \binom{n}{\alpha_1 \ \cdots \alpha_{m_1} \ \beta_1 \cdots \beta_{m_2}}
\end{equation}

no matter which summation index \(l\in\mathbb{N}^g\) it corresponds to. In order
to do the matching one may ignore the indices \(\sigma_j\) and \(l_j-\sigma_j\) 
which vanish, because the corresponding operators \(Z_0\) and \(T_0\) are equal to
the identity operator on \(\mathcal{H}\) respectively Fock space. 

Since we know that 

\begin{align*}
\left[ d\Gamma\left(\sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}}  \prod_{l=1}^g Z_{b_l}\right), a^\#\right]\\
= a^\# \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}}  \prod_{l=1}^g Z_{b_l}
\end{align*}
holds, all that is left to show is that 
\begin{align}\label{combinatorics total commutator}
&\left[-\sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g T_{b_l}, a^\#\right]\\\notag
&= a^\# \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^{g+1}}{g} 
\binom{n}{\vec{b}}  \prod_{l=1}^g Z_{b_l}
\end{align}
also holds. For which we need to count the summands which are multiples of each element of \eqref{combinatorics span}
 corresponding to each \(g\) in \eqref{combinatorics total sum of T}. So let us fix some element
 \(K(m_1,m_2)\) of \eqref{combinatorics span} corresponding to some \(m_1\in\mathbb{N},
 m_2\in\mathbb{N}_0, \alpha \in \mathbb{N}^{m_1}\) and \( \beta\in \mathbb{N}^{m_2}\).
Rephrasing this problem, we can ask which products
\begin{equation}
\prod_{l=1}^g T_{\gamma_l}
\end{equation}
 for suitable \(g\) and \((\gamma_l)_l\) produce, when commuted with a creation or annihilation operator, 
  multiples of \(K(m_1,m_2)\)? We will call this number of 
 total contributions weighted with the factor 
 \( - \frac{(-1)^g}{g}\) borrowed from \eqref{combinatorics total sum of T} \(\#K(m_1,m_2)\).  
 Looking at the commutation relations 
\eqref{logarithmic lift condition} we split the set of indices \(\{\gamma_1\dots \gamma_g\}\) into
three sets \(A,B\) and \(C\), where the commutation relation has to be used in such a way, that

\begin{align*}
&\forall k: \gamma_k \in A \iff \exists j\le m_1: \gamma_k = \alpha_j, \\
\wedge& \forall k: \gamma_k \in B \iff \exists j\le m_2: \gamma_k = \beta_j\\
\wedge & \forall k: \gamma_k \in C \iff \exists j\le m_1, l\le m_2: \gamma_k = \alpha_j + \beta_l
\end{align*}
 holds. Unfortunately not every splitting corresponds to a contribution and not every
 order of multiplication of a legal splitting corresponds to a contribution either.
 However \(\prod_{j} T_{\alpha_j} \prod_j T_{\beta_j}\) gives
 a contribution and it is in fact the longes product that does.
 We may apply the commutation relations backwards to obtain any
 shorter valid combination and hence all combinations. 
 Transforming the commutation rule for \(T_k\) read from right to left
 into a game results in the following rules.
 
Starting from the string 
\begin{equation}
A_1A_2\dots A_{m_1} B_1 B_2 \dots B_{m_2},
\end{equation}

representing the longes product, where here and in the following \(A\)'s
represent operators \(T_k\) which will turn into \(Z_k\) by the commutation rule,
\(B\)'s represent operators \(T_k\) which will stay \(T_k\) after commutation and
\(C\)'s represent operators \(T_k\) which will produce both a \(Z_l\) in the creation/annihilation
operator and a \(T_{k-l}\) behind that operator. The indices are merely there to keep track of
which operator moved where.

So the game consists in the answering how many strings can we produce by 
applying the following rules to the initial string?
\begin{enumerate}
\item You may replace any occurrence of \(A_k B_j\) by \(B_j A_k\) for any \(j\) and \(k\).
\item You may replace any occurrence of \(A_k B_j\) by \(C_{k,j}\) for any \(j\) and \(k\).
\end{enumerate}
Where we have to count the number of times we applied the second rule, or equivalently
the number \(\#C\) of \(C\)'s in the resulting string, because the summation index \(g\) in 
\eqref{combinatorics total sum of T} corresponds to \(m_1+m_2-\#C\). 

Fix \(\#C \in\{0,\dots ,\min(m_1,m_2)\}\). A valid string has \(m_1+m_2-\#C\) characters,
because the number of its \(C\)s is \(\#C\), its number of \(A\)s is \(m_1-\#C\) and 
its number of \(B\)s is \(m_2-\#C\). Ignoring the labelling of the \(A\)s, \(B\)s and \(C\)s 
there are \(\binom{m_1+m_2-\#C}{\#C \ (m_1 - \#C) \ (m_2-\#C)}\) such strings. Now if
we consider one such string without labelling, e.g.

\begin{equation}
C A A B A C C B B A C B B A B B B B,
\end{equation}

there is only one correct labelling to be restored, namely the one where each \(A\) and the first index of 
any \(C\)  receive increasing labels from left to right and analogously for \(B\) and the second 
 index of any \(C\), resulting for our example in
 
\begin{equation}
 C_{1,1} A_2 A_3 B_2 A_4 C_{5,3} C_{6,4} B_{5} B_6 A_7 C_{8,7} B_8 B_9 A_9 B_{10} B_{11} B_{12} B_{13}.
\end{equation}

So any unlabelled  string corresponds to exactly one labelled string which in turn corresponds to 
exactly one choice of operator product \(\prod T\). 
So returning to our Operators, we found the number \(\#K(m_1,m_2)\) it is

\begin{equation}\label{combinatorics binomial sum}
\#K(m_1,m_2) =-\sum_{g=\max(m_1,m_2)}^{m_1+m_2} \frac{(-1)^g}{g} \binom{g}{(m_1+m_2-g) \ (g-m_1) \ (g - m_2)},
\end{equation}
where the total minus sign comes from the total minus sign in front of \eqref{combinatorics total commutator}
with respect to \eqref{T_n recursive}. 

Now since we introduced the slightly non-standard definition of binomial coefficients used in \cite{graham1994concrete} we
can make use of the rules for summing binomial coefficients derived there.
As a first step to evaluate \eqref{combinatorics binomial sum} we split the trinomial coefficient into binomial
ones and make use of the absorption identity

\begin{equation}\tag{absorption}\label{absorption}
\forall a \in \mathbb{C}\ \forall b \in \mathbb{Z}: b \binom{a}{b} = a \binom{a-1}{b-1} 
\end{equation}

for \(m_2,m_1\neq 0\) as follows

\begin{align*}
&\#K(m_1,m_2) \\
&=-\sum_{g=\max(m_1,m_2)}^{m_1+m_2} \frac{(-1)^g}{g} \binom{g}{(m_1+m_2-g) \ (g-m_1) \ (g - m_2)}\\
&=-\sum_{g=\max(m_1,m_2)}^{m_1+m_2} \frac{(-1)^g}{g} \binom{g}{m_2}\binom{m_2}{g-m_1}\\
&\stackrel{\eqref{absorption}}{=}-\sum_{g=\max(m_1,m_2)}^{m_1+m_2} \frac{(-1)^g}{m_2} \binom{g-1}{m_2-1}\binom{m_2}{g-m_1}\\
&=\frac{-1}{m_2} \sum_{g=\max(m_1,m_2)}^{m_1+m_2} (-1)^g \binom{g-1}{m_2-1}\binom{m_2}{g-m_1}\\
&\overset{m_1>0}{=}\frac{-1}{m_2} \sum_{g\in\mathbb{Z}} (-1)^g \binom{m_2}{g-m_1}\binom{g-1}{m_2-1}\\
&\stackrel{*}{=} \frac{-1}{m_2} (-1)^{m_2-m_1} \binom{m_1-1}{-1} = 0,
\end{align*}
where for the second but last equality \(m_1>0\) is needed for the \(g=0\) summand not to contribute and
for the marked equality we used summation rule (5.24) of \cite{graham1994concrete}. 
So all the coefficients vanish that fulfil \(m_1,m_2\neq 0\). The sum for the remaining cases
is readily computed, since there is just one summand. Summarising we find

\begin{equation*}
\#K(m_1,m_2)= \delta_{m_2,0} \frac{(-1)^{1+m_1}}{m_1} + \delta_{m_1,0} \frac{(-1)^{1+m_2}}{m_2},
\end{equation*}

where the second summand can be ignored, since terms with \(m_1=0\) are irrelevant for our considerations.

 So the left hand side of 
\eqref{combinatorics total commutator} can be evaluated

\begin{align*}
\left[-\sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^g}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g T_{b_l}, a^\#\right]\\
= \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|b|=n}} \frac{(-1)^{g+1}}{g} \binom{n}{\vec{b}}  a^\# \prod_{l=1}^g Z_{b_l},
\end{align*}

which is exactly equal to the right hand side of \eqref{combinatorics total commutator}. This ends the motivation of the conjecture.



\subsection{Solution to Recursive Equation}

So we found a recursive equation for the \(T_n\)s, now we need to solve it. 
In order to do so we need the following lemma about combinatorial distributions

\begin{Lemma}\label{stirling lemma}
For any \(g\in\mathbb{N},k\in\mathbb{N}\)
\begin{equation}
\sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{|\vec{g}|=k}} \binom{k}{\vec{g}}=\sum_{l=0}^g (-1)^l (g-l)^k \binom{g}{l}
\end{equation}
holds. The reader interested in terminology may be eager to know, that the right hand side is equal to
 \(g!\) times the Stirling 
number of the second kind \(\left\{\begin{matrix}k\\g\end{matrix}\right\}\).
\end{Lemma}
\textbf{Proof:} We would like to apply the multinomial theorem but there are all the summands missing where at least
one of the entries of \(\vec{g}\) is zero, so we add an appropriate expression of zero. We also give the expression in
question a name, since we will later on arrive at a recursive expression.
\begin{multline}
F(g,k):=\sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{|\vec{g}|=k}} \binom{k}{\vec{g}}
= \sum_{\stackrel{\vec{g}\in\mathbb{N}_0^g}{|\vec{g}|=k}} \binom{k}{\vec{g}}
- \sum_{\stackrel{\stackrel{\vec{g}\in\mathbb{N}_0^g}{|\vec{g}|=k}}{\exists l: g_l=0}} \binom{k}{\vec{g}}\\
= g^k 
 - \sum_{\stackrel{\stackrel{\vec{g}\in\mathbb{N}_0^g}{|\vec{g}|=k}}{\exists l: g_l=0}} \binom{k}{\vec{g}}
=g^k 
- \sum_{n=1}^{g-1} \sum_{\stackrel{\vec{g}\in\mathbb{N}_0^g}{|\vec{g}|=k}}
 \binom{k}{\vec{g}} 1_{\exists! i_1\dots i_n : \forall i_l\neq i_k \wedge \forall l :g_{i_l}=0}
\end{multline}
where in the last line the indicator function is to enforce there being exactly n different indices \(i_l\) for which \(g_{i_l}=0\)
holds. Now since it does not matter which entries of the vector vanish because the multinomial coefficient 
is symmetric and its value is identical to the corresponding multinomial coefficient where the vanishing entries
are omitted, we can further simplify the sum:

\begin{equation*}
F(g,k)= g^k -  \sum_{n=1}^{g-1} \binom{g}{n} \sum_{\stackrel{\vec{g}\in\mathbb{N}^n}{|\vec{g}|=k}}
 \binom{k}{\vec{g}}
\end{equation*}

The inner sum turns out to be \(F(g-n,k)\), so we found the recursive relation for \(F\):
\begin{equation}\label{combinatorics solution recursive}
F(g,k)= g^k -  \sum_{n=1}^{g-1} \binom{g}{n} F(n,k)= g^k -  \sum_{n=1}^{g-1} \binom{g}{n} F(g-n,k),
\end{equation}

where for the last equality we used the symmetry of binomial coefficients.
By iteratively applying this equation, we find the following formula, which we will now prove by induction

\begin{multline}\label{combinatorics induction}
\forall d\in\mathbb{N}_0: F(g,k)=\sum_{l=0}^d (-1)^l (g-l)^k \binom{g}{l}\\
+(-1)^{d+1} \sum_{n=1}^{g-d-1} \binom{n+d-1}{d} \binom{g}{n+d} F(g-d-n,k).
\end{multline}

We already showed the start of the induction, so what's left is the induction step. Before we do so the
following remark is in order: We are only interested in the case \(d=g\) and the formula seems meaningless
for \(d>g\); however, the additional summands in the left sum vanish, where as the right sum is empty
for these values of \(d\) since the  upper bound of the summation index is lower than its lower bound.

For the induction step, pick \(d\in\mathbb{N}_0\), use \eqref{combinatorics induction} and pull the first summand
 out of the second sum,
on this summand we apply the recursive relation \eqref{combinatorics solution recursive} resulting in

\begin{multline}
F(g,k)=\sum_{l=0}^d (-1)^l (g-l)^k \binom{g}{l}\\
 + (-1)^{d+1}\sum_{n=2}^{g-d-1} \binom{n+d-1}{d}\binom{g}{n+d} F(g-d-n,k)\\
  + (-1)^{d+1} \binom{d}{d} \binom{g}{d+1} F(g-d-1,k)\\
\overset{\eqref{combinatorics solution recursive}}{=}\sum_{l=0}^{d+1} (-1)^l (g-l)^k \binom{g}{l}\\
+(-1)^{d+1} \sum_{n=2}^{g-d-1} \binom{n+d-1}{d} \binom{g}{n+d} F(g-d-n,k)\\
-(-1)^{d+1} \binom{g}{d+1} \sum_{n=1}^{g-d-2} \binom{g-d-1}{n} F(g-d-1-n,k)\\
=\sum_{l=0}^{d+1} (-1)^l (g-l)^k \binom{g}{l}\\
+(-1)^{d+1} \sum_{n=1}^{g-d-2} \binom{n+d}{d} \binom{g}{n+d+1} F(g-d-1-n,k)\\
-(-1)^{d+1} \binom{g}{d+1} \sum_{n=1}^{g-d-2} \binom{g-d-1}{n} F(g-d-1-n,k).
\end{multline}
After the index shift we can combine the last two sums. 

\begin{multline}
F(g,k)= \sum_{l=0}^{d+1} (-1)^l (g-l)^k \binom{g}{l}\\
+ \sum_{n=1}^{g-d-2}\left[\binom{g}{d+1} \binom{g-d-1}{n} - \binom{n+d}{d} \binom{g}{n+d+1} \right] 
\\(-1)^{d+2} F(g-d-1-n,k).
\end{multline}


In order to combine the two binomials we reassemble \(\binom{g}{d+1}\binom{g-d-1}{n}\) 
into \(\binom{g}{n+d+1}\binom{n+d+1}{d+1}\), which can be seen to be possible by representing everything
in terms of factorials. This results in
\begin{multline}
F(g,k)= \sum_{l=0}^{d+1} (-1)^l (g-l)^k \binom{g}{l}\\
+(-1)^{d+2} \sum_{n=1}^{g-d-2}\left[\binom{n+d+1}{d+1} - \binom{n+d}{d}\right] \binom{g}{n+d+1} 
 F(g-d-1-n,k)\\
=\sum_{l=0}^{d+1} (-1)^l (g-l)^k \binom{g}{l}\\
+(-1)^{d+2}  \sum_{n=1}^{g-d-2} \binom{n+d}{d+1} \binom{g}{n+d+1}  F(g-d-1-n,k),
\end{multline}
where we used the addition formula for binomials:

\begin{equation}
\forall n\in \mathbb{C} \forall k \in \mathbb{Z}: \binom{n}{k} = \binom{n-1}{k} + \binom{n-1}{k-1}.
\end{equation}
This concludes the proof by induction. By setting \(d=g\) in equation \eqref{combinatorics induction} 
we arrive at the desired result. \qed

Using the previous lemma, we are able to show the next

\begin{Lemma}\label{combinatorics weak conjecture lemma 2}
For any \(k \in \mathbb{N}\backslash \{1\}\) the following equation holds
\begin{equation}
\sum_{g=1}^k \frac{(-1)^g}{g} \sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{|\vec{g}|=k}}\binom{k}{\vec{g}}=0.
\end{equation}
\end{Lemma}
\textbf{Proof:} Let \(k\in\mathbb{N}\backslash\{1\}\), as a first step we apply lemma \ref{stirling lemma}.
We change the order of summation, use \eqref{absorption}, extend the range of summation and shift 
summation index  to arrive at

\begin{multline}
\sum_{g=1}^k \frac{(-1)^g}{g} \sum_{l=0}^g (-1)^l (g-l)^k \binom{g}{l}
= \sum_{g=1}^k \frac{1}{g} \sum_{l=0}^g (-1)^{g-l} (g-l)^k \binom{g}{g-l}\\
= \sum_{g=1}^k \sum_{p=0}^g (-1)^{p} p^k \frac{1}{g} \binom{g}{p}
=\sum_{g=1}^k \sum_{p=0}^g (-1)^{p} p^k \frac{1}{p} \binom{g-1}{p-1}\\
=\sum_{g=1}^k \sum_{p\in\mathbb{Z}} (-1)^{p} p^{k-1}\binom{g-1}{p-1}
=\sum_{p\in\mathbb{Z}} (-1)^{p} p^{k-1} \sum_{g=1}^k \binom{g-1}{p-1}\\
=\sum_{p\in\mathbb{Z}} (-1)^{p} p^{k-1} \sum_{g=0}^{k-1} \binom{g}{p-1}.
\end{multline}

Now we use equation (5.10) of \cite{graham1994concrete}:

\begin{equation}\tag{upper summation}
\forall m,n\in\mathbb{N}_0: \sum_{k=0}^n \binom{k}{m} = \binom{n+1}{m+1},
\end{equation}
which can for example be proven by induction on \(n\).

We furthermore rewrite the power of the summation index \(p\) in terms of the derivative of an 
exponential and change order summation and differentiation. This results in

\begin{multline*}
\sum_{g=1}^k \frac{(-1)^g}{g} \sum_{l=0}^g (-1)^l (g-l)^k \binom{g}{l}
=\sum_{p\in\mathbb{Z}} (-1)^{p} p^{k-1}  \binom{k}{p}\\
=\sum_{p=0}^k (-1)^{p} \left. \frac{\partial^{k-1}}{\partial \alpha^{k-1}} e^{\alpha p}\right|_{\alpha=0}  \binom{k}{p}
=\left. \frac{\partial^{k-1}}{\partial \alpha^{k-1}}  \sum_{p=0}^k (-1)^{p} e^{\alpha p} \binom{k}{p}\right|_{\alpha=0} \\
=\left. \frac{\partial^{k-1}}{\partial \alpha^{k-1}}  \left( 1-e^{\alpha p}\right)^k \right|_{\alpha=0} 
=(-1)^k \left. \frac{\partial^{k-1}}{\partial \alpha^{k-1}} \left( \sum_{l=1}^\infty \frac{(\alpha p)^l}{l!} \right) ^k \right|_{\alpha=0} \\
=(-1)^k \left. \frac{\partial^{k-1}}{\partial \alpha^{k-1}} ((\alpha p)^k + \mathcal{O} ((\alpha p)^{k+1}) ) \right|_{\alpha=0} =0.
\end{multline*}
\qed




We are now in a position to state the solution to the recursive equation \eqref{T_n recursive}
and motivate that it is in fact a solution. 

\begin{Conj}
For \(n\in\mathbb{N}\) the solution of the recursive equation \eqref{T_n recursive} 
solely in terms of \(G_a\) and \(C_a\) is given by

\begin{equation}\label{recursive solution}
T_n = \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|= n}} \sum_{\vec{d}\in {\{0,1\}}^g} 
\frac{1}{g!} \binom{n}{\vec{b}} \prod_{l=1}^g F_{b_l,d_l},
\end{equation}
where \(F\) is given by
\begin{equation}\label{eq resursive weak solution}
F_{a,b} = \left\{ \begin{matrix}\mathrm\Gamma_a \quad \text{for } b=0 \\ C_a \quad \text{for } b=1  \end{matrix} \right._. 
\end{equation}
For the readers convenience we remind her, that \(\mathrm\Gamma_a\) and
the constants \(C_n\) are defined in theorem \ref{thm: T_n recursive}. 
\end{Conj}

\textbf{Motivation:} The structure of this proof will be induction over \(n\). For \(n=1\) the whole expression
on the right hand side collapses to \(C_1 + \mathrm\Gamma_1\), which we already know to be equal to \(T_1\). For
arbitrary \(n+1\in\mathbb{N}\backslash\{1\}\) we apply the recursive equation \eqref{T_n recursive}
once and use the induction hypothesis for all \(k\le n\) and thereby arrive at the rather convoluted 
expression

\begin{multline}\label{recursive weak conjecture proof}
T_{n+1} \stackrel{\eqref{T_n recursive}}{=} 
\mathrm\Gamma_{n+1} + C_{n+1}+ \sum_{g=2}^{n+1} \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n+1}} 
\frac{(-1)^g}{g} \binom{n+1}{\vec{b}} \prod_{l=1}^g T_{b_l}\\
\stackrel{\text{induction hyp}}{=} \mathrm\Gamma_{n+1} + C_{n+1}+ \sum_{g=2}^{n+1} \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n+1}} 
\frac{(-1)^g}{g} \binom{n+1}{\vec{b}} \prod_{l=1}^g \\
\sum_{g_l=1}^{b_l} \sum_{\stackrel{\vec{c}_l \in\mathbb{N}^{g_l}}{|\vec{c}_l|=b_l}} \sum_{\vec{e}_l \in \{0,1\}^{g_l}}
\frac{1}{g_l!} \binom{b_l}{\vec{c}_l} \prod_{k=1}^{g_l} F_{c_{l,k},e_{l,k}}.
\end{multline}

If we were to count the contributions of this sum to a specific product \(\prod F_{c_j,e_j}\) for some choice of 
\((c_j)_j, (e_j)_j\) we would first recognize that all the multinomial factors in \eqref{recursive weak conjecture proof}
combine to a single one whose indices are given by the first indices of all the \(F\) factors involved.
Other than this factor each contribution adds \(\frac{(-1)^g}{g} \prod_{l=1}^g \frac{1}{g_l!}\) to the sum. So we 
need to keep track of how many contributions there are and which distributions of \(g_l\) they belong to. 

Fix some product \(\prod F :=\prod_{j=1}^{\tilde{g}} F_{\tilde{b}_j,\tilde{d}_j}\). In the sum 
\eqref{recursive weak conjecture proof} we pick some initial short product of length \(g\) and split each
factor into \(g_l\) pieces to arrive at one of length \(\tilde{g}\) if the product is to contribute to
\(\prod F\). So clearly \(\sum_{l=1}^g g_l = \tilde{g}\) holds for any contribution to \(\prod F\). 
The reverse is also true, for any
\(g\) and \(g_1, \dots, g_g\in\mathbb{N}\) such that \(\sum_{l=1}^g g_l=\tilde{g}\) holds
the corresponding expression in \eqref{recursive weak conjecture proof} contributes to 
\(\prod F\). Furthermore \(\prod F\) and \(g\), \(g_1,\dots g_g\) is enough to uniquely
determine the summand of \eqref{recursive weak conjecture proof} the contribution
belongs to. For an illustration of this splitting see

\begin{align*}
\underbrace{\underbrace{F^1_{3,1} F^2_{2,0} F^3_{7,1}}_{g_1=3} \underbrace{F^4_{5,0}}_{g_2=1} \underbrace{F^5_{4,1} F^6_{2,1}}_{g_3=2} \underbrace{F^7_{1,1} F^8_{3,0} F^9_{4,1}}_{g_4=3} \underbrace{F^{10}_{4,1} F^{11}_{1,0}}_{g_5=2}}_{g=5}\\
 g_1+g_2+g_3+g_4+g_5=11=\tilde{g},
\end{align*}

where I labelled the factors in the upper right index for the readers convenience. We recognize
that the sum we are about to perform is by no means unique for each order of \(n\) but only 
depends on the number of appearing factors and the number of splittings performed on
them. By the preceding argument we need 

\begin{equation}\label{combinatorics weak conjecture reformulated into equation}
\sum_{g=2}^{\tilde{g}} \frac{(-1)^g}{g} \sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{|\vec{g}|=\tilde{g}}} \prod_{l=1}^g \frac{1}{g_l!}
= \frac{1}{\tilde{g}!} 
\end{equation}


to hold for \(\tilde{g}>1\), in order to find agreement with the proposed solution \eqref{eq resursive weak solution}.
Now proving \eqref{combinatorics weak conjecture reformulated into equation} is done by 
realizing, that one can include the right hand side into the sum as the \(g=1\) summand, dividing
the equation by \(\tilde{g}!\) and using lemma \ref{combinatorics weak conjecture lemma 2}
with \(k=\tilde{g}\). The remaining case, \(\tilde{g}=1\), can directly be
read off of \eqref{recursive weak conjecture proof}. This ends the motivation of this conjecture.

\begin{Conj}\label{Corollary T_n by G's and C's}
For \(n\in\mathbb{N}\), \(T_n\) can be written as

\begin{equation}
\frac{1}{n!} T_n = \sum_{\stackrel{1\le c+g\le n}{c,g\in\mathbb{N}_0}} 
\sum_{\stackrel{\stackrel{\vec{g}\in\mathbb{N}^g}{\vec{c}\in\mathbb{N}^c}}{|\vec{c}| + |\vec{g}|=n}} 
\frac{1}{c! g!} \prod_{l=1}^c \frac{1}{c_l!} C_{c_l} \prod_{l=1}^g \frac{1}{g_l!} \mathrm\Gamma_{g_l}.
\end{equation}
Please note that for ease of notation we defined \(\mathbb{N}^0:= \{1\}\).
\end{Conj}
\textbf{Motivation:} By an argument completely analogous to the combinatorial argument in the motivation of conjecture
\eqref{thm: T_n recursive} we see that we can disentangle the \(F\)s in \eqref{recursive solution}
into \(\mathrm\Gamma\)s and \(C\)s if we multiply by a factor of \(\binom{c+g}{c}\) where \(c\) is the 
number of \(C\)s and \(g\) is the number of \(\mathrm\Gamma\)s giving

\begin{multline}
T_n = \sum_{\stackrel{1\le c+g\le n}{c,g\in\mathbb{N}_0}}
\sum_{\stackrel{\stackrel{\vec{g}\in\mathbb{N}^g}{\vec{c}\in\mathbb{N}^c}}{|\vec{c}| + |\vec{g}|=n}} 
\binom{c+g}{c} \frac{1}{(c+g)!} \binom{n}{\vec{g}\oplus \vec{c}}
\prod_{l=1}^c  C_{c_l} \prod_{l=1}^g \mathrm\Gamma_{g_l},
\end{multline}

which directly reduces to the equation we wanted to prove, by plugging in the multinomials in terms of
factorials. 

\begin{Conj}
As a formal power series, the second quantized scattering operator can be written in the form
\begin{equation}\label{Corollary double exp}
S= e^{\sum_{l\in\mathbb{N}} \frac{C_{l}}{l!}}
 e^{\sum_{l\in\mathbb{N}} \frac{\mathrm\Gamma_{l}}{l!}}.
\end{equation}
\end{Conj}
\textbf{Proof:} We plug conjecture \ref{Corollary T_n by G's and C's} into the defining Series for the \(T_n\)s
giving

\begin{align}
&S= \sum_{n\in\mathbb{N}_0} \frac{1}{n!} T_n \\
&=\id_{\mathcal{F}}+ \sum_{n\in\mathbb{N}} \sum_{\stackrel{1\le c+g\le n}{c,g\in\mathbb{N}_0}} 
\sum_{\stackrel{\stackrel{\vec{g}\in\mathbb{N}^g}{\vec{c}\in\mathbb{N}^c}}{|\vec{c}| + |\vec{g}|=n}} 
\frac{1}{c! g!} \prod_{l=1}^c \frac{1}{c_l!} C_{c_l} \prod_{l=1}^g \frac{1}{g_l!} \mathrm\Gamma_{g_l}\\
&=\id_{\mathcal{F}}+  \sum_{\stackrel{1\le c+g }{c,g\in\mathbb{N}_0}} 
\sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{\vec{c}\in\mathbb{N}^c}} 
\frac{1}{c! g!} \prod_{l=1}^c \frac{1}{c_l!} C_{c_l} \prod_{l=1}^g \frac{1}{g_l!} \mathrm\Gamma_{g_l}\\
&=\sum_{c,g\in\mathbb{N}_0}
\sum_{\stackrel{\vec{g}\in\mathbb{N}^g}{\vec{c}\in\mathbb{N}^c}} 
\frac{1}{c! g!} \prod_{l=1}^c \frac{1}{c_l!} C_{c_l} \prod_{l=1}^g \frac{1}{g_l!} \mathrm\Gamma_{g_l}\\
&=\sum_{c\in\mathbb{N}_0} \frac{1}{c!} \sum_{\vec{c}\in\mathbb{N}^c} \prod_{l=1}^c \frac{1}{c_l!} C_{c_l}
\sum_{g\in\mathbb{N}_0} \frac{1}{g!} \sum_{\vec{g}\in\mathbb{N}^g} \prod_{l=1}^g \frac{1}{g_l!} \mathrm\Gamma_{g_l}\\
&=\sum_{c\in\mathbb{N}_0} \frac{1}{c!} \prod_{l=1}^c \sum_{k\in\mathbb{N}} \frac{1}{k!} C_{k}
\sum_{g\in\mathbb{N}_0} \frac{1}{g!}  \prod_{l=1}^g \sum_{b\in\mathbb{N}} \frac{1}{b!} \mathrm\Gamma_{b}\\
&=\sum_{c\in\mathbb{N}_0} \frac{1}{c!} \left( \sum_{k\in\mathbb{N}} \frac{1}{k!} C_{k}\right)^c
\sum_{g\in\mathbb{N}_0} \frac{1}{g!}  \left( \sum_{b\in\mathbb{N}} \frac{1}{b!} \mathrm\Gamma_{b}\right)^g\\
&=e^{\sum_{l\in\mathbb{N}} \frac{1}{l!} C_{l}} e^{\sum_{l\in\mathbb{N}} \frac{1}{l!} \mathrm\Gamma_{l}}.
\end{align}


\begin{Conj}
For \(A\) such that 
\begin{equation}
\|\id-U^A\|<1.
\end{equation}
The second quantized scattering operator fulfils
\begin{equation}\label{conj:sleek_second_quantised_scattering_operator}
S= e^{\sum_{n\in\mathbb{N}} \frac{C_n}{n!}} e^{\mathrm{d}\Gamma(\ln (U))}
\end{equation}
where \(C_n\) must be imaginary for any \(n\in\mathbb{N}\) in order to satisfy unitarity.

\end{Conj}
\textbf{Motivation:} 
First the remark about \(C_n \in i \mathbb{R}\) for any \(n\) is a direct consequence of 
the second factor of \eqref{conj:sleek_second_quantised_scattering_operator} begin unitary.
This in turn follows directly from \(\mathrm{d}\Gamma^* (K)=-\mathrm{d}\Gamma(K)\) for any \(K\) in the domain of \(\mathrm{d}\Gamma\).
That \(\ln U\) is in the domain of \(\mathrm{d}\Gamma\) follows from \( (\ln U)^*=\ln U^*=\ln U^{-1}=-\ln U\)
and \(\|U-\id\|<1\).

 We are going to change the sum in the second exponential of 
\eqref{Corollary double exp}, so let's take a closer look at that: by exchanging summation
we can step by step simplify

\begin{multline}
\sum_{l\in\mathbb{N}} \frac{\mathrm\Gamma_{l}}{l!}= 
\sum_{n \in\mathbb{N}} \frac{1}{n!} 
\mathrm{d}\Gamma\left( \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^{g+1}}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g Z_{b_l}  \right)\\
=\mathrm{d}\Gamma\left( \sum_{n \in\mathbb{N}} \frac{1}{n!} 
 \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^{g+1}}{g} 
\binom{n}{\vec{b}} \prod_{l=1}^g Z_{b_l}  \right)\\
=\mathrm{d}\Gamma\left( \sum_{n \in\mathbb{N}}
 \sum_{g=1}^n \sum_{\stackrel{\vec{b}\in\mathbb{N}^g}{|\vec{b}|=n}}\frac{(-1)^{g+1}}{g} 
 \prod_{l=1}^g \frac{Z_{b_l}}{b_l!}  \right)\\
=\mathrm{d}\Gamma\left( 
 \sum_{g\in\mathbb{N}} \sum_{\vec{b}\in\mathbb{N}^g}\frac{(-1)^{g+1}}{g} 
\prod_{l=1}^g \frac{Z_{b_l}}{b_l!}  \right)\\
=\mathrm{d}\Gamma\left( 
 \sum_{g\in\mathbb{N}} \frac{(-1)^{g+1}}{g} 
\prod_{l=1}^g \left(\sum_{b_l\in\mathbb{N}} \frac{Z_{b_l}}{b_l!} \right) \right)\\
=\mathrm{d}\Gamma\left( 
 \sum_{g\in\mathbb{N}} \frac{(-1)^{g+1}}{g} 
 \left(\sum_{b\in\mathbb{N}} \frac{Z_{b}}{b!} \right)^g \right)\\
 =\mathrm{d}\Gamma\left( 
 \sum_{g\in\mathbb{N}} \frac{(-1)^{g+1}}{g} 
 \left(U-\id \right)^g \right)
 =\mathrm{d}\Gamma\left( -
 \sum_{g\in\mathbb{N}} \frac{1}{g} 
 \left(\id-U \right)^g \right)\\
  =\mathrm{d}\Gamma\left( 
 \ln \left(\id-\left(\id-U\right) \right) \right)
 =\mathrm{d}\Gamma\left( \ln \left(U\right)\right).
\end{multline}



The last conjecture is proven directly in section \ref{sec:proof simple formula}



%\chapter{Bibliography concerning the state of the art, the research objectives, and the work program} 
%\vspace*{-0.68cm}

%\begingroup
%\renewcommand{\section}[2]{}
\bibliographystyle{amsplain}
\bibliography{ref}

%\bibliography{../../aarbeit/felix}
%\include{bib}
%\endgroup

\chapter{Cooperating Researchers} 
Prof. Dr. Franz Merkl (LMU)\\
Junior Research Group Leader Dr. Dirk Deckert (LMU)



\end{document}

